### 2022-12-28 quarto/mysite/index.qmd
quarto

# Aston Zhang

<table align="center" width="1000">
<tbody>
<tr>
<td height="200" width="200"><img src="img/aston.jpg" height="150" width="150" border="0" hspace="0" /></td>
<td>
<p align="left"><img src="img/email.png" height="30" width="225"></p>
<p align="left"><span style="font-size: large;">2795 Augustine Dr, Santa Clara, CA 95054</span></p>
<p align="left">
	<a href="https://twitter.com/astonzhangAZ" title="Twitter" target="_blank"><img src="./img/logo-twitter.svg" class="bio-icon"></a>
	<a href="https://github.com/astonzhang" title="GitHub" target="_blank"><img src="./img/logo-github.svg" class="bio-icon"></a>
</p>
</td>
</tr>
</tbody>
</table>

<b>Aston Zhang</b> is a senior scientist at Amazon Web Services AI.
His current research interests focus on efficient and robust methods for machine learning and natural language processing.
He received the <a href="https://iclr-conf.medium.com/announcing-iclr-2021-outstanding-paper-awards-9ae0514734ab" target="_blank">ICLR Outstanding Paper Award (2021)</a>,
the ACM Ubicomp Distinguished Paper Award (2018), and the ACM SenSys Best Paper Award Nomination (2017).
His <a href="https://github.com/d2l-ai" target="_blank">open-source</a> textbook,
<a href="https://d2l.ai" target="_blank">Dive into Deep Learning</a>,
has been <a href="https://d2l.ai/_images/map.png" target="_blank">adopted worldwide</a>.
He obtained his Ph.D. in Computer Science from University of Illinois at Urbana-Champaign.

Hi! I'm happy to connect and discuss. Preferred mode of contact is my email.
My team is hiring intern scientists in machine learning
(at our <a href="https://www.google.com/maps/place/2795+Augustine+Dr,+Santa+Clara,+CA+95054/@37.3835062,-121.9778599,17z/data=!3m1!4b1!4m5!3m4!1s0x808fc9f208b94da1:0xd2df9ae053c51af0!8m2!3d37.383502!4d-121.9756659" target="_blank">Santa Clara office</a> or other global offices). Just drop me a line.

## Books

* A. Zhang, Z. C. Lipton, M. Li, and A. J. Smola<br>
 	<a href="https://d2l.ai" target="_blank">Dive into Deep Learning</a><br>
	Cambridge University Press, 2023<br>
	* Adopted at 400 universities from 60 countries
	* Featured in the <a href="https://youtu.be/ue9aumC7AAk?t=6856" target="_blank">AWS re:Invent 2021 keynote</a> by Dr. Swami Sivasubramanian
	<iframe src="https://ghbtns.com/github-btn.html?user=d2l-ai&repo=d2l-en&type=star&count=true" frameborder="0" scrolling="0" width="150" height="30" title="GitHub"></iframe>

* A. Zhang, M. Li, Z. C. Lipton, and A. J. Smola<br>
	<a href="https://zh.d2l.ai" target="_blank">动手学深度学习</a><br>
	人民邮电出版社, 2nd ed., 2023, 1st ed., 2019<br>
	* <a href="https://github.com/d2l-ai/d2l-zh/raw/v1/img/frontpage/jd-190715-en.png" target="_blank">Best seller</a> of new books in "Computers and Internet" at the largest Chinese online bookstore
	<iframe src="https://ghbtns.com/github-btn.html?user=d2l-ai&repo=d2l-zh&type=star&count=true" frameborder="0" scrolling="0" width="150" height="30" title="GitHub"></iframe>

## Recent Papers

* Z. Zhang, A. Zhang, M. Li, and A. J. Smola<br>
<a href="https://arxiv.org/abs/2210.03493" target="_blank">Automatic Chain of Thought Prompting in Large Language Models</a><br>
<i>"Let's think not just step by step, but also one by one."</i>
In <i>arXiv</i>, 2022<br>
<a href="https://twitter.com/astonzhangAZ/status/1579489453789581312" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
<a href="https://github.com/amazon-research/auto-cot" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>

* J. Chen, A. Zhang, X. Shi, M. Li, A. J. Smola, and D. Yang<br>
<a href="https://d2l-webdata.s3.us-west-2.amazonaws.com/papers/PEFT-design-spaces.pdf" target="_blank">Parameter-Efficient Fine-Tuning Design Spaces</a><br>
<i>"Adapters, prefix tuning, BitFit, LoRA, ... do design patterns exist?"</i>
In <i>arXiv</i>, 2022<br>

* M. S. Bari, A. Zhang, S. Zheng, X. Shi, Y. Zhu, S. Joty, M. Li<br>
<a href="https://arxiv.org/abs/2212.10929" target="_blank">
SPT: Semi-Parametric Prompt Tuning for Multitask Prompted Learning</a><br>
<i>"If your prompt tuning can't converge easily, make it semi-parametric."</i>
In <i>arXiv</i>, 2022<br>
<a href="https://twitter.com/astonzhangAZ/status/1605959819894349824" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>

* H. Wang, A. Zhang, Y. Zhu, S. Zheng, M. Li, A. J. Smola, and Z. Wang<br>
<a href="https://arxiv.org/pdf/2207.01160.pdf" target="_blank">Partial and Asymmetric Contrastive Learning for Out-of-Distribution Detection in Long-Tailed Recognition</a><br>
In <i>Proceedings of International Conference on Machine Learning</i> (<b>ICML, Long Presentation</b>), 2022<br>
<a href="https://twitter.com/astonzhangAZ/status/1549800894840971265" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
<a href="https://github.com/amazon-research/long-tailed-ood-detection" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>

* H. Wang, A. Zhang, S. Zheng, X. Shi, M. Li, and Z. Wang<br>
<a href="https://arxiv.org/pdf/2207.01156.pdf" target="_blank">Removing Batch Normalization Boosts Adversarial Training</a><br>
In <i>Proceedings of International Conference on Machine Learning</i> (<b>ICML</b>), 2022<br>
<a href="https://twitter.com/astonzhangAZ/status/1549069378250874880" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
<a href="https://github.com/amazon-research/normalizer-free-robust-training" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>

* E. Grassucci, A. Zhang, and D. Comminiello<br>
<a href="https://arxiv.org/abs/2110.04176" target="_blank">PHNNs: Lightweight Neural Networks via Parameterized Hypercomplex Convolutions</a><br>
In <i>IEEE Transactions on Neural Networks and Learning Systems</i> (<b>TNNLS</b>), 2022<br>
<a href="https://github.com/eleGAN23/HyperNets" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>

* A. Zhang, Y. Tay, S. Zhang, A. Chan, A. T. Luu, S. C. Hui, and J. Fu<br>
<a href="https://arxiv.org/abs/2102.08597" target="_blank">Beyond Fully-Connected Layers with Quaternions: Parameterization of Hypercomplex Multiplications with 1/n Parameters</a><br>
In <i>Proceedings of the International Conference on Learning Representations</i> (<b>ICLR, <font color="red">Outstanding Paper Award</font></b>), 2021<br>
<a href="https://github.com/astonzhang/Parameterization-of-Hypercomplex-Multiplications" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>

## <a href="papers.html">All Papers</a>

## Services

* Area Chair
	* Annual Meeting of the Association for Computational Linguistics (ACL)
	* Conference on Empirical Methods in Natural Language Processing (EMNLP)

* Senior Program Committee
	* AAAI Conference on Artificial Intelligence (AAAI)

* Journal Editorial Board
	* Frontiers in Big Data

## Ph.D. Interns</a>

For prospective 2023 interns: my team is hiring research interns in NLP or ML. Just email me.

* <a href="https://sites.cc.gatech.edu/~jchen896/" target="_blank">Jiaao Chen</a> (2022)
* <a href="https://bcmi.sjtu.edu.cn/home/zhangzs/" target="_blank">Zhuosheng Zhang</a> (2022)
* <a href="https://sbmaruf.github.io/" target="_blank">M Saiful Bari</a> (2022)
* <a href="https://renshuhuai-andy.github.io/" target="_blank">Shuhuai Ren</a> (2022)
* <a href="https://htwang14.github.io/" target="_blank">Haotao Wang</a> (2021, 2022)
* <a href="https://shuaizhang.tech/" target="_blank">Shuai Zhang</a> (2019&ndash;2020)

<br>
<a href="https://twitter.com/astonzhangAZ?ref_src=twsrc%5Etfw" class="twitter-follow-button" data-size="large" data-show-count="false">Follow @astonzhangAZ</a><script async src="https://platform.twitter.com/widgets.js" charset="utf-8"></script>
<br>
<a class="twitter-timeline" data-width="350" data-height="200" href="https://twitter.com/astonzhangAZ?ref_src=twsrc%5Etfw">Tweets by astonzhangAZ</a> <script async src="https://platform.twitter.com/widgets.js" charset="utf-8"></script>

### 2022-12-28 quarto/mysite/papers.qmd
quarto

---
title: "Papers"
---

## 2022

* Z. Zhang, A. Zhang, M. Li, and A. J. Smola<br>
<a href="https://arxiv.org/abs/2210.03493" target="_blank">Automatic Chain of Thought Prompting in Large Language Models</a><br>
<i>"Let's think not just step by step, but also one by one."</i>
In <i>arXiv</i>, 2022<br>
<a href="https://twitter.com/astonzhangAZ/status/1579489453789581312" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
<a href="https://github.com/amazon-research/auto-cot" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>

* J. Chen, A. Zhang, X. Shi, M. Li, A. J. Smola, and D. Yang<br>
<a href="https://d2l-webdata.s3.us-west-2.amazonaws.com/papers/PEFT-design-spaces.pdf" target="_blank">Parameter-Efficient Fine-Tuning Design Spaces</a><br>
<i>"Adapters, prefix tuning, BitFit, LoRA, ... do design patterns exist?"</i>
In <i>arXiv</i>, 2022<br>

* M. S. Bari, A. Zhang, S. Zheng, X. Shi, Y. Zhu, S. Joty, M. Li<br>
<a href="https://arxiv.org/abs/2212.10929" target="_blank">
SPT: Semi-Parametric Prompt Tuning for Multitask Prompted Learning</a><br>
<i>"If your prompt tuning can't converge easily, make it semi-parametric."</i>
In <i>arXiv</i>, 2022<br>
<a href="https://twitter.com/astonzhangAZ/status/1605959819894349824" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>

* H. Wang, A. Zhang, Y. Zhu, S. Zheng, M. Li, A. J. Smola, and Z. Wang<br>
<a href="https://arxiv.org/pdf/2207.01160.pdf" target="_blank">Partial and Asymmetric Contrastive Learning for Out-of-Distribution Detection in Long-Tailed Recognition</a><br>
In <i>Proceedings of International Conference on Machine Learning</i> (<b>ICML, Long Presentation</b>), 2022<br>
<a href="https://twitter.com/astonzhangAZ/status/1549800894840971265" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
<a href="https://github.com/amazon-research/long-tailed-ood-detection" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>

* H. Wang, A. Zhang, S. Zheng, X. Shi, M. Li, and Z. Wang<br>
<a href="https://arxiv.org/pdf/2207.01156.pdf" target="_blank">Removing Batch Normalization Boosts Adversarial Training</a><br>
In <i>Proceedings of International Conference on Machine Learning</i> (<b>ICML</b>), 2022<br>
<a href="https://twitter.com/astonzhangAZ/status/1549069378250874880" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
<a href="https://github.com/amazon-research/normalizer-free-robust-training" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>

* H. Wang, J. Hong, A. Zhang, J. Zhou, and Z. Wang<br>
<a href="https://arxiv.org/abs/2210.06428" target="_blank">Trap and Replace: Defending Backdoor Attacks by Trapping Them into an Easy-to-Replace Subnetwork</a><br>
In <i>Proceedings of the Conference on Neural Information Processing Systems</i> (<b>NeurIPS</b>), 2022

* Z. Hu, R. K.-W, Lee, C. C. Aggarwal, and A. Zhang<br>
<a href="https://arxiv.org/pdf/2010.12742.pdf" target="_blank">Text Style Transfer: A Review and Experimental Evaluation</a><br>
In <i>ACM SIGKDD Explorations</i>, 2022<br>

* C. He, S. Zheng, A. Zhang, G. Karypis, T. Chilimbi, M. Soltanolkotabi, S. Avestimehr<br>
<a href="https://arxiv.org/abs/2212.05191" target="_blank">
SMILE: Scaling Mixture-of-Experts with Efficient Bi-level Routing</a><br>
<i>"2.5x speedup over Switch Transformers"</i>
In <i>arXiv</i>, 2022<br>

* X. Hao, Y. Zhu, S. Appalaraju, A. Zhang, W. Zhang, B. Li, and M. Li<br>
<a href="https://arxiv.org/abs/2206.08358" target="_blank">MixGen: A New Multi-Modal Data Augmentation</a><br>
<i>"Interpolate images, concatenate text."</i>
In <i>arXiv</i>, 2022<br>
<a href="https://twitter.com/astonzhangAZ/status/1537860202652786688" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
<a href="https://github.com/amazon-research/mix-generation" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>

* E. Grassucci, A. Zhang, and D. Comminiello<br>
<a href="https://arxiv.org/abs/2110.04176" target="_blank">PHNNs: Lightweight Neural Networks via Parameterized Hypercomplex Convolutions</a><br>
In <i>IEEE Transactions on Neural Networks and Learning Systems</i> (<b>TNNLS</b>), 2022<br>
<a href="https://github.com/eleGAN23/HyperNets" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>

## 2021

* A. Zhang, Y. Tay, S. Zhang, A. Chan, A. T. Luu, S. C. Hui, and J. Fu<br>
<a href="https://arxiv.org/abs/2102.08597" target="_blank">Beyond Fully-Connected Layers with Quaternions: Parameterization of Hypercomplex Multiplications with 1/n Parameters</a><br>
In <i>Proceedings of the International Conference on Learning Representations</i> (<b>ICLR, <font color="red">Outstanding Paper Award</font></b>), 2021<br>
<a href="https://github.com/astonzhang/Parameterization-of-Hypercomplex-Multiplications" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>

* A. Chan, Y. S. Ong, B. Pung, A. Zhang, and J. Fu<br>
<a href="https://arxiv.org/pdf/2006.03535.pdf" target="_blank">CoCon: A Self-Supervised Approach for Controlled Text Generation</a><br>
In <i>Proceedings of the International Conference on Learning Representations</i> (<b>ICLR</b>), 2021<br>
<a href="https://github.com/alvinchangw/COCON_ICLR2021" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>

* A. Zhang, Y. Tay, Y. Shen, A. Chan, and S. Zhang<br>
<a href="https://proceedings.neurips.cc/paper/2021/file/3341f6f048384ec73a7ba2e77d2db48b-Paper.pdf" target="_blank">Self-Instantiated Recurrent Units with Dynamic Soft Recursion</a><br>
In <i>Proceedings of the Conference on Neural Information Processing Systems</i> (<b>NeurIPS</b>), 2021<br>
<a href="https://github.com/astonzhang/Self-IRU" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>

* Y. Long, B. Wang, Z. Yang, B. Kailkhura, A. Zhang, C. A. Gunter, and B. Li<br>
<a href="https://arxiv.org/pdf/1906.09338.pdf" target="_blank">G-PATE: Scalable Differentially Private Data Generator via Private Aggregation of Teacher Discriminators</a><br>
In <i>Proceedings of the Conference on Neural Information Processing Systems</i> (<b>NeurIPS</b>), 2021<br>
<a href="https://github.com/AI-secure/G-PATE" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>

* T. Chen, Y. Sui, X. Chen, A. Zhang, and Z. Wang<br>
<a href="https://arxiv.org/abs/2102.06790" target="_blank">A Unified Lottery Ticket Hypothesis for Graph Neural Networks</a><br>
In <i>Proceedings of International Conference on Machine Learning</i> (<b>ICML</b>), 2021<br>
<a href="https://github.com/VITA-Group/Unified-LTH-GNN" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>

* H. Shao, Z. Xiao, S. Yao, D. Sun, A. Zhang, S. Liu, T. Wang, J. Li, and T. Abdelzaher<br>
<b>ControlVAE: Tuning, Analytical Properties, and Performance Analysis</b><br>
In <i>Transactions on Pattern Analysis and Machine Intelligence</i> (<b>TPAMI</b>), 2021

* A. Zhang, A. Chan, Y. Tay, J. Fu, S. Wang, S. Zhang, H. Shao, S. Yao, and R. Lee<br>
<b>On Orthogonality Constraints for Transformers</b><br>
In <i>Proceedings of the 59th Annual Meeting of the Association for Computational Linguistics</i> (<b>ACL, Oral</b>), 2021

* H. Shao, J. Wang, H. Lin, X. Zhang, A. Zhang, H. Ji, and T. Abdelzaher<br>
<b>Controllable and Diverse Text Generation in E-commerce</b><br>
In <i>Proceedings of the Web Conference</i> (<b>WWW</b>), 2021

* S. Zhang, H. Liu, A. Zhang, Y. Hu, C. Zhang, Y. Li, T. Zhu, S. He, and W. Ou<br>
<b>Learning User Representations with Hypercuboids for Recommender Systems</b><br>
In <i>Proceedings of the 14th International Conference on Web Search and Data Mining</i> (<b>WSDM</b>), 2021

## 2020

* H. Shao, S. Yao, D. Sun, A. Zhang, S. Liu, D. Liu, J. Wang, and T. Abdelzaher<br>
<b>ControlVAE: Controllable Variational Autoencoder</b><br>
In <i>Proceedings of International Conference on Machine Learning</i> (<b>ICML</b>), 2020

* J. Guo, H. He, T. He, L. Lausen, M. Li, H. Lin, X. Shi, C. Wang, J. Xie, S. Zha, A. Zhang, H. Zhang, Z. Zhang, Z. Zhang, S. Zheng, and Y. Zhu<br>
<b>GluonCV and GluonNLP: Deep Learning in Computer Vision and Natural Language Processing</b><br>
In <i>Journal of Machine Learning Research</i> (<b>JMLR</b>), Vol. 21, No. 23, 2020

* A. Chan, Y. Tay, Y. S. Ong, and A. Zhang<br>
<b>Poison Attacks against Text Datasets with Conditional Adversarially Regularized Autoencoder</b><br>
In <i>Findings of Empirical Methods in Natural Language Processing</i> (<b>EMNLP-Findings</b>), 2020

* H. Shao, D. Sun, J. Wu, Z. Zhang, A. Zhang, S. Yao, S. Liu, T. Wang, C. Zhang, and T. Abdelzaher<br>
<b>GitHub Repository Recommendation for Academic Papers</b><br>
In <i>Proceedings of the Web Conference</i> (<b>WWW</b>), 2020

## 2019

* Y. Tay, A. T. Luu, A. Zhang, S. Wang, and S. C. Hui<br>
<b>Compositional De-Attention Networks</b><br>
In <i>Proceedings of the Conference on Neural Information Processing Systems</i> (<b>NeurIPS</b>), 2019

* S. Zhang, L. Yao, L. V. Tran, A. Zhang, and Y. Tay<br>
<b>Quaternion Collaborative Filtering for Recommendation</b><br>
In <i>Proceedings of the 28th International Joint Conference on Artificial Intelligence</i> (<b>IJCAI</b>), 2019

* Y. Tay, A. Zhang, A. T. Luu, J. Rao, S. Zhang, S. Wang, J. Fu, and S. C. Hui<br>
<b>Lightweight and Efficient Neural Natural Language Processing with Quaternion Networks</b><br>
In <i>Proceedings of the 57th Annual Meeting of the Association for Computational Linguistics</i> (<b>ACL</b>), 2019

* Y. Tay, S. Wang, A. T. Luu, J. Fu, M. C. Phan, X. Yuan, J. Rao, S. C. Hui, and A. Zhang<br>
<b>Simple and Effective Curriculum Pointer-Generator Networks for Reading Comprehension over Long Narratives</b><br>
In <i>Proceedings of the 57th Annual Meeting of the Association for Computational Linguistics</i> (<b>ACL</b>), 2019

* A. El-Kishky, F. Xu, A. Zhang, and J. Han<br>
<b>Parsimonious Morpheme Segmentation with an Application to Enriching Word Embeddings</b><br>
In <i>Proceedings of the IEEE International Conference on Big Data</i> (<b>IEEE BigData</b>), 2019

## Earlier

* S. Yao, Y. Zhao, A. Zhang, S. Hu, H. Shao, C. Zhang, L. Su, and T. Abdelzaher<br>
<b>Deep Learning for the Internet of Things</b><br>
In <i>Computer</i>, 2018 (selected as May 2018 cover feature of the flagship magazine of the IEEE Computer Society)

* A. El-Kishky, F. Xu, A. Zhang, S. Macke, and J. Han<br>
<b>Entropy-Based Subword with an Application to Word Embeddings</b><br>
In <i>Proceedings of the 2nd Workshop on Subword and Character Level Models in NLP at the 16th Annual Conference of the North American Chapter of the Association for Computational Linguistics: Human Language Technologies</i> (<b>NAACL SCLeM</b>), 2018

* S. Yao, Y. Zhao, H. Shao, C. Zhang, A. Zhang, S. Hu, D. Liu, S. Liu, L. Su, and T. F. Abdelzaher<br>
<b>SenseGAN: Enabling Deep Learning for Internet of Things with a Semi-Supervised Framework</b><br>
In <i>Proceedings of the ACM on Interactive, Mobile, Wearable and Ubiquitous Technologies</i> (<b>ACM Ubicomp, <font color="red">Distinguished Paper Award</font></b>), 2018

* A. Zhang, X. Lu, C. A. Gunter, S. Yao, F. Tao, R. Zhu, H. Gui, D. Fabbri, D. Liebovitz, and B. Malin<br>
<b>De Facto Diagnosis Specialties: Recognition and Discovery</b><br>
In <i>Learning Health Systems</i> (<b>LHS</b>), 2018

* S. Yao, Y. Zhao, H. Shao, C. Zhang, A. Zhang, D. Liu, S. Liu, L. Su, and T. Abdelzaher<br>
<b>ApDeepSense: Deep Learning Uncertainty Estimation Without the Pain for IoT</b><br>
In <i>Proceedings of the 38th IEEE International Conference on Distributed Computing Systems</i> (<b>ICDCS</b>), 2018

* A. Zhang, L. Garcia-Pueyo, J. B. Wendt, M. Najork, and A. Broder<br>
<b>Email Category Prediction</b><br>
In <i>Proceedings of the 26th International World Wide Web Conference </i> (<b>WWW</b>), 2017

* S. Yao, S. Hu, Y. Zhao, A. Zhang, and T. Abdelzaher<br>
<b>DeepSense: A Unified Deep Learning Framework for Time-Series Mobile Sensing Data Processing</b><br>
In <i>Proceedings of the 26th International World Wide Web Conference</i> (<b>WWW</b>), 2017

* S. Yao, Y. Zhao, A. Zhang, S. Lu, and T. Abdelzaher<br>
<b>DeepIoT: Compressing Deep Neural Network Structures for Sensing Systems without Loss of Performance</b><br>
In <i>Proceedings of the 15th ACM Conference on Embedded Networked Sensor Systems</i> (<b>ACM Sensys, <font color="red">Best Paper Award Nomination</font></b>), 2017

* S. Yao, Y. Zhao, H. Shao, A. Zhang, C. Zhang, S. Li, and T. Abdelzaher<br>
<b>RDeepSense: Reliable Deep Mobile Computing Models with Uncertainty Estimations</b><br>
In <i>Proceedings of the ACM on Interactive, Mobile, Wearable and Ubiquitous Technologies</i> (<b>ACM Ubicomp</b>), 2017

* A. Zhang, A. Goyal, R. Baeza-Yates, Y. Chang, J. Han, C. A. Gunter, and H. Deng<br>
<b>Towards Mobile Query Auto-Completion: An Efficient Mobile Application-Aware Approach</b><br>
In <i>Proceedings of the 25th International World Wide Web Conference</i> (<b>WWW</b>), 2016

* A. Zhang and Q. Gu<br>
<b>Accelerated Stochastic Block Coordinate Descent with Optimal Sampling</b> [<a href="papers/supp_asbcd.pdf" target="_blank">Proof of Lemmas</a>]<br>
In <i>Proceedings of the 22nd ACM SIGKDD Conference on Knowledge Discovery and Data Mining</i> (<b>KDD</b>), 2016

* S. Demetriou, W. Merrill, W. Yang, A. Zhang, and C. A. Gunter<br>
<b>Free for All! Assessing User Data Exposure to Advertising Libraries on Android</b><br>
In <i>Proceedings of the Network and Distributed System Security Symposium</i> (<b>NDSS</b>), 2016

* R. Zhu, A. Zhang, J. Peng, and C. Zhai<br>
<b>Exploiting Temporal Divergence of Topic Distributions for Event Detection</b><br>
In <i>Proceedings of the IEEE International Conference on Big Data</i> (<b>IEEE BigData</b>), 2016

* A. Zhang, A. Goyal, W. Kong, H. Deng, A. Dong, Y. Chang, C. A. Gunter, and J. Han<br>
<b>adaQAC: Adaptive Query Auto-Completion via Implicit Negative Feedback</b><br>
In <i>Proceedings of the 38th International ACM SIGIR Conference on Research and Development in Information Retrieval</i> (<b>SIGIR</b>), 2015

* W. Kong, R. Li, J. Luo, A. Zhang, Y. Chang, and J. Allan<br>
<b>Predicting Search Intent Based on Pre-Search Context</b><br>
In <i>Proceedings of the 38th International ACM SIGIR Conference on Research and Development in Information Retrieval</i> (<b>SIGIR</b>), 2015

* H. Fu, A. Zhang, and X. Xie<br>
<b>Effective Social Graph De-anonymization based on Graph Structure and Descriptive Information</b><br>
In <i>ACM Transactions on Intelligent Systems and Technology</i> (<b>ACM TIST</b>), Vol. 6, No. 4, 2015

* X. Lu, A. Zhang, C. A. Gunter, D. Fabbri, D. Liebovitz, and B. Malin<br>
<b>Discovering De Facto Diagnosis Specialties</b><br>
In <i>Proceedings of the 6th ACM Conference on Bioinformatics, Computational Biology, and Health Informatics</i> (<b>ACM BCB</b>), 2015

* A. Zhang, X. Xie, K. C.-C. Chang, C. A. Gunter, J. Han, and X. Wang<br>
<b>Privacy Risk in Anonymized Heterogeneous Information Networks</b><br>
In <i>Proceedings of the 17th International Conference on Extending Database Technology</i> (<b>EDBT</b>), 2014

* H. Fu, A. Zhang, and X. Xie<br>
<b>De-anonymizing Social Graphs via Node Similarity</b><br>
In <i>Proceedings of the 23rd International World Wide Web Conference</i> (<b>WWW</b>), 2014

### 2022-12-28 quarto/index.qmd
update

--- 2022-12-28 quarto/mysite/index.qmd
@@
 
-<table align="center" width="1000">
-<tbody>
-<tr>
-<td height="200" width="200"><img src="img/aston.jpg" height="150" width="150" border="0" hspace="0" /></td>
-<td>
-<p align="left"><img src="img/email.png" height="30" width="225"></p>
-<p align="left"><span style="font-size: large;">2795 Augustine Dr, Santa Clara, CA 95054</span></p>
+<img src="img/aston.jpg"  border="0" vspace="5" hspace="0" /><br>
+<img src="img/email.png" height="30" width="200" vspace="5" ><br>
+
 <p align="left">
@@
 </p>
-</td>
-</tr>
-</tbody>
-</table>
 
@@
 
-## <a href="papers.html">All Papers</a>
+## [All Papers](papers.qmd)
 

### 2022-12-28 quarto/deploy.sh

@@ -1,0 +1,1 @@
+cp -r _site/* ..

### 2022-12-28 quarto/index.qmd
update

@@
 	* Adopted at 400 universities from 60 countries
-	* Featured in the <a href="https://youtu.be/ue9aumC7AAk?t=6856" target="_blank">AWS re:Invent 2021 keynote</a> by Dr. Swami Sivasubramanian
+	* Featured in the <a href="https://youtu.be/ue9aumC7AAk?t=6856" target="_blank">AWS re:Invent 2021 keynote</a> by Dr. Swami Sivasubramanian<br>
 	<iframe src="https://ghbtns.com/github-btn.html?user=d2l-ai&repo=d2l-en&type=star&count=true" frameborder="0" scrolling="0" width="150" height="30" title="GitHub"></iframe>
@@
 	人民邮电出版社, 2nd ed., 2023, 1st ed., 2019<br>
-	* <a href="https://github.com/d2l-ai/d2l-zh/raw/v1/img/frontpage/jd-190715-en.png" target="_blank">Best seller</a> of new books in "Computers and Internet" at the largest Chinese online bookstore
+	* <a href="https://github.com/d2l-ai/d2l-zh/raw/v1/img/frontpage/jd-190715-en.png" target="_blank">Best seller</a> of new books in "Computers and Internet" at the largest Chinese online bookstore<br>
 	<iframe src="https://ghbtns.com/github-btn.html?user=d2l-ai&repo=d2l-zh&type=star&count=true" frameborder="0" scrolling="0" width="150" height="30" title="GitHub"></iframe>

### 2022-12-28 quarto/deploy.sh

@@ -1,1 +1,2 @@
 cp -r _site/* ..
+cd ..

### 2022-12-28 quarto/index.qmd
update

@@
-# Aston Zhang
-
-<img src="img/aston.jpg"  border="0" vspace="5" hspace="0" /><br>
-<img src="img/email.png" height="30" width="200" vspace="5" ><br>
+<img src="img/aston.jpg"  border="0" vspace="10" hspace="0" /><br>
+<img src="img/email.png" height="30" width="200" vspace="0" ><br>
 
@@
 
+## Tutorials
+
+* with A. J. Smola<br>
+	<b>Attention in Deep Learning</b> [<a href="http://alex.smola.org/talks/ICML19-attention.key" target="_blank">Keynote</a>] [<a href="http://alex.smola.org/talks/ICML19-attention.pdf" target="_blank">PDF</a>] [<a href="https://www.youtube.com/watch?v=nS1Lse2B48w" target="_blank">Video</a>]<br>
+	In <i>The 36th International Conference on Machine Learning</i> (<b>ICML</b>), 2019
+
+* with H. Lin, X. Shi, L. Lausen, H. He, S. Zha, and A. J. Smola<br>
+	<b>Dive into Deep Learning for Natural Language Processing</b> <br>
+	In <i>Conference on Empirical Methods in Natural Language Processing</i> (<b>EMNLP</b>), 2019
+
+* with H. Lin, L. Lausen, S. Zha, A. J. Smola, C. Wang, and M. Li<br>
+	<b>From Shallow to Deep Language Representations: Pre-training, Fine-tuning, and Beyond</b> [<a href="https://github.com/astonzhang/KDD19-tutorial" target="_blank">Website</a>]<br>
+	In <i>The 25th ACM SIGKDD Conference on Knowledge Discovery and Data Mining</i> (<b>KDD</b>), 2019
+
+* with H. Zhang, T. He, Z. Zhang, Z. Zhang, H. Lin, and M. Li<br>
+	<b>Everything You Need to Know to Reproduce SOTA Deep Learning Models from Hands-on Tutorial</b><br>
+	In <i>International Conference on Computer Vision</i> (<b>ICCV</b>), 2019
+
 ## Services

### 2022-12-28 quarto/deploy.sh

@@ -1,2 +1,3 @@
+#!/bin/bash
 cp -r _site/* ..
 cd ..

### 2022-12-28 quarto/papers.qmd
update

--- 2022-12-28 quarto/mysite/papers.qmd
@@
 
-* Z. Zhang, A. Zhang, M. Li, and A. J. Smola<br>
+* Z. Zhang, **A. Zhang**, M. Li, and A. J. Smola<br>
 <a href="https://arxiv.org/abs/2210.03493" target="_blank">Automatic Chain of Thought Prompting in Large Language Models</a><br>
@@
 
-* J. Chen, A. Zhang, X. Shi, M. Li, A. J. Smola, and D. Yang<br>
+* J. Chen, **A. Zhang**, X. Shi, M. Li, A. J. Smola, and D. Yang<br>
 <a href="https://d2l-webdata.s3.us-west-2.amazonaws.com/papers/PEFT-design-spaces.pdf" target="_blank">Parameter-Efficient Fine-Tuning Design Spaces</a><br>
@@
 
-* M. S. Bari, A. Zhang, S. Zheng, X. Shi, Y. Zhu, S. Joty, M. Li<br>
+* M. S. Bari, **A. Zhang**, S. Zheng, X. Shi, Y. Zhu, S. Joty, M. Li<br>
 <a href="https://arxiv.org/abs/2212.10929" target="_blank">
@@
 
-* H. Wang, A. Zhang, Y. Zhu, S. Zheng, M. Li, A. J. Smola, and Z. Wang<br>
+* H. Wang, **A. Zhang**, Y. Zhu, S. Zheng, M. Li, A. J. Smola, and Z. Wang<br>
 <a href="https://arxiv.org/pdf/2207.01160.pdf" target="_blank">Partial and Asymmetric Contrastive Learning for Out-of-Distribution Detection in Long-Tailed Recognition</a><br>
@@
 
-* H. Wang, A. Zhang, S. Zheng, X. Shi, M. Li, and Z. Wang<br>
+* H. Wang, **A. Zhang**, S. Zheng, X. Shi, M. Li, and Z. Wang<br>
 <a href="https://arxiv.org/pdf/2207.01156.pdf" target="_blank">Removing Batch Normalization Boosts Adversarial Training</a><br>
@@
 
-* H. Wang, J. Hong, A. Zhang, J. Zhou, and Z. Wang<br>
+* H. Wang, J. Hong, **A. Zhang**, J. Zhou, and Z. Wang<br>
 <a href="https://arxiv.org/abs/2210.06428" target="_blank">Trap and Replace: Defending Backdoor Attacks by Trapping Them into an Easy-to-Replace Subnetwork</a><br>
@@
 
-* Z. Hu, R. K.-W, Lee, C. C. Aggarwal, and A. Zhang<br>
+* Z. Hu, R. K.-W, Lee, C. C. Aggarwal, and **A. Zhang**<br>
 <a href="https://arxiv.org/pdf/2010.12742.pdf" target="_blank">Text Style Transfer: A Review and Experimental Evaluation</a><br>
@@
 
-* C. He, S. Zheng, A. Zhang, G. Karypis, T. Chilimbi, M. Soltanolkotabi, S. Avestimehr<br>
+* C. He, S. Zheng, **A. Zhang**, G. Karypis, T. Chilimbi, M. Soltanolkotabi, S. Avestimehr<br>
 <a href="https://arxiv.org/abs/2212.05191" target="_blank">
@@
 
-* X. Hao, Y. Zhu, S. Appalaraju, A. Zhang, W. Zhang, B. Li, and M. Li<br>
+* X. Hao, Y. Zhu, S. Appalaraju, **A. Zhang**, W. Zhang, B. Li, and M. Li<br>
 <a href="https://arxiv.org/abs/2206.08358" target="_blank">MixGen: A New Multi-Modal Data Augmentation</a><br>
@@
 
-* E. Grassucci, A. Zhang, and D. Comminiello<br>
+* E. Grassucci, **A. Zhang**, and D. Comminiello<br>
 <a href="https://arxiv.org/abs/2110.04176" target="_blank">PHNNs: Lightweight Neural Networks via Parameterized Hypercomplex Convolutions</a><br>
@@
 
-* A. Zhang, Y. Tay, S. Zhang, A. Chan, A. T. Luu, S. C. Hui, and J. Fu<br>
+* **A. Zhang**, Y. Tay, S. Zhang, A. Chan, A. T. Luu, S. C. Hui, and J. Fu<br>
 <a href="https://arxiv.org/abs/2102.08597" target="_blank">Beyond Fully-Connected Layers with Quaternions: Parameterization of Hypercomplex Multiplications with 1/n Parameters</a><br>
@@
 
-* A. Chan, Y. S. Ong, B. Pung, A. Zhang, and J. Fu<br>
+* A. Chan, Y. S. Ong, B. Pung, **A. Zhang**, and J. Fu<br>
 <a href="https://arxiv.org/pdf/2006.03535.pdf" target="_blank">CoCon: A Self-Supervised Approach for Controlled Text Generation</a><br>
@@
 
-* A. Zhang, Y. Tay, Y. Shen, A. Chan, and S. Zhang<br>
+* **A. Zhang**, Y. Tay, Y. Shen, A. Chan, and S. Zhang<br>
 <a href="https://proceedings.neurips.cc/paper/2021/file/3341f6f048384ec73a7ba2e77d2db48b-Paper.pdf" target="_blank">Self-Instantiated Recurrent Units with Dynamic Soft Recursion</a><br>
@@
 
-* Y. Long, B. Wang, Z. Yang, B. Kailkhura, A. Zhang, C. A. Gunter, and B. Li<br>
+* Y. Long, B. Wang, Z. Yang, B. Kailkhura, **A. Zhang**, C. A. Gunter, and B. Li<br>
 <a href="https://arxiv.org/pdf/1906.09338.pdf" target="_blank">G-PATE: Scalable Differentially Private Data Generator via Private Aggregation of Teacher Discriminators</a><br>
@@
 
-* T. Chen, Y. Sui, X. Chen, A. Zhang, and Z. Wang<br>
+* T. Chen, Y. Sui, X. Chen, **A. Zhang**, and Z. Wang<br>
 <a href="https://arxiv.org/abs/2102.06790" target="_blank">A Unified Lottery Ticket Hypothesis for Graph Neural Networks</a><br>
@@
 
-* H. Shao, Z. Xiao, S. Yao, D. Sun, A. Zhang, S. Liu, T. Wang, J. Li, and T. Abdelzaher<br>
+* H. Shao, Z. Xiao, S. Yao, D. Sun, **A. Zhang**, S. Liu, T. Wang, J. Li, and T. Abdelzaher<br>
 <b>ControlVAE: Tuning, Analytical Properties, and Performance Analysis</b><br>
@@
 
-* A. Zhang, A. Chan, Y. Tay, J. Fu, S. Wang, S. Zhang, H. Shao, S. Yao, and R. Lee<br>
+* **A. Zhang**, A. Chan, Y. Tay, J. Fu, S. Wang, S. Zhang, H. Shao, S. Yao, and R. Lee<br>
 <b>On Orthogonality Constraints for Transformers</b><br>
@@
 
-* H. Shao, J. Wang, H. Lin, X. Zhang, A. Zhang, H. Ji, and T. Abdelzaher<br>
+* H. Shao, J. Wang, H. Lin, X. Zhang, **A. Zhang**, H. Ji, and T. Abdelzaher<br>
 <b>Controllable and Diverse Text Generation in E-commerce</b><br>
@@
 
-* S. Zhang, H. Liu, A. Zhang, Y. Hu, C. Zhang, Y. Li, T. Zhu, S. He, and W. Ou<br>
+* S. Zhang, H. Liu, **A. Zhang**, Y. Hu, C. Zhang, Y. Li, T. Zhu, S. He, and W. Ou<br>
 <b>Learning User Representations with Hypercuboids for Recommender Systems</b><br>
@@
 
-* H. Shao, S. Yao, D. Sun, A. Zhang, S. Liu, D. Liu, J. Wang, and T. Abdelzaher<br>
+* H. Shao, S. Yao, D. Sun, **A. Zhang**, S. Liu, D. Liu, J. Wang, and T. Abdelzaher<br>
 <b>ControlVAE: Controllable Variational Autoencoder</b><br>
@@
 
-* J. Guo, H. He, T. He, L. Lausen, M. Li, H. Lin, X. Shi, C. Wang, J. Xie, S. Zha, A. Zhang, H. Zhang, Z. Zhang, Z. Zhang, S. Zheng, and Y. Zhu<br>
+* J. Guo, H. He, T. He, L. Lausen, M. Li, H. Lin, X. Shi, C. Wang, J. Xie, S. Zha, **A. Zhang**, H. Zhang, Z. Zhang, Z. Zhang, S. Zheng, and Y. Zhu<br>
 <b>GluonCV and GluonNLP: Deep Learning in Computer Vision and Natural Language Processing</b><br>
@@
 
-* A. Chan, Y. Tay, Y. S. Ong, and A. Zhang<br>
+* A. Chan, Y. Tay, Y. S. Ong, and **A. Zhang**<br>
 <b>Poison Attacks against Text Datasets with Conditional Adversarially Regularized Autoencoder</b><br>
@@
 
-* H. Shao, D. Sun, J. Wu, Z. Zhang, A. Zhang, S. Yao, S. Liu, T. Wang, C. Zhang, and T. Abdelzaher<br>
+* H. Shao, D. Sun, J. Wu, Z. Zhang, **A. Zhang**, S. Yao, S. Liu, T. Wang, C. Zhang, and T. Abdelzaher<br>
 <b>GitHub Repository Recommendation for Academic Papers</b><br>
@@
 
-* Y. Tay, A. T. Luu, A. Zhang, S. Wang, and S. C. Hui<br>
+* Y. Tay, A. T. Luu, **A. Zhang**, S. Wang, and S. C. Hui<br>
 <b>Compositional De-Attention Networks</b><br>
@@
 
-* S. Zhang, L. Yao, L. V. Tran, A. Zhang, and Y. Tay<br>
+* S. Zhang, L. Yao, L. V. Tran, **A. Zhang**, and Y. Tay<br>
 <b>Quaternion Collaborative Filtering for Recommendation</b><br>
@@
 
-* Y. Tay, A. Zhang, A. T. Luu, J. Rao, S. Zhang, S. Wang, J. Fu, and S. C. Hui<br>
+* Y. Tay, **A. Zhang**, A. T. Luu, J. Rao, S. Zhang, S. Wang, J. Fu, and S. C. Hui<br>
 <b>Lightweight and Efficient Neural Natural Language Processing with Quaternion Networks</b><br>
@@
 
-* Y. Tay, S. Wang, A. T. Luu, J. Fu, M. C. Phan, X. Yuan, J. Rao, S. C. Hui, and A. Zhang<br>
+* Y. Tay, S. Wang, A. T. Luu, J. Fu, M. C. Phan, X. Yuan, J. Rao, S. C. Hui, and **A. Zhang**<br>
 <b>Simple and Effective Curriculum Pointer-Generator Networks for Reading Comprehension over Long Narratives</b><br>
@@
 
-* A. El-Kishky, F. Xu, A. Zhang, and J. Han<br>
+* A. El-Kishky, F. Xu, **A. Zhang**, and J. Han<br>
 <b>Parsimonious Morpheme Segmentation with an Application to Enriching Word Embeddings</b><br>
@@
 
-* S. Yao, Y. Zhao, A. Zhang, S. Hu, H. Shao, C. Zhang, L. Su, and T. Abdelzaher<br>
+* S. Yao, Y. Zhao, **A. Zhang**, S. Hu, H. Shao, C. Zhang, L. Su, and T. Abdelzaher<br>
 <b>Deep Learning for the Internet of Things</b><br>
@@
 
-* A. El-Kishky, F. Xu, A. Zhang, S. Macke, and J. Han<br>
+* A. El-Kishky, F. Xu, **A. Zhang**, S. Macke, and J. Han<br>
 <b>Entropy-Based Subword with an Application to Word Embeddings</b><br>
@@
 
-* S. Yao, Y. Zhao, H. Shao, C. Zhang, A. Zhang, S. Hu, D. Liu, S. Liu, L. Su, and T. F. Abdelzaher<br>
+* S. Yao, Y. Zhao, H. Shao, C. Zhang, **A. Zhang**, S. Hu, D. Liu, S. Liu, L. Su, and T. F. Abdelzaher<br>
 <b>SenseGAN: Enabling Deep Learning for Internet of Things with a Semi-Supervised Framework</b><br>
@@
 
-* A. Zhang, X. Lu, C. A. Gunter, S. Yao, F. Tao, R. Zhu, H. Gui, D. Fabbri, D. Liebovitz, and B. Malin<br>
+* **A. Zhang**, X. Lu, C. A. Gunter, S. Yao, F. Tao, R. Zhu, H. Gui, D. Fabbri, D. Liebovitz, and B. Malin<br>
 <b>De Facto Diagnosis Specialties: Recognition and Discovery</b><br>
@@
 
-* S. Yao, Y. Zhao, H. Shao, C. Zhang, A. Zhang, D. Liu, S. Liu, L. Su, and T. Abdelzaher<br>
+* S. Yao, Y. Zhao, H. Shao, C. Zhang, **A. Zhang**, D. Liu, S. Liu, L. Su, and T. Abdelzaher<br>
 <b>ApDeepSense: Deep Learning Uncertainty Estimation Without the Pain for IoT</b><br>
@@
 
-* A. Zhang, L. Garcia-Pueyo, J. B. Wendt, M. Najork, and A. Broder<br>
+* **A. Zhang**, L. Garcia-Pueyo, J. B. Wendt, M. Najork, and A. Broder<br>
 <b>Email Category Prediction</b><br>
@@
 
-* S. Yao, S. Hu, Y. Zhao, A. Zhang, and T. Abdelzaher<br>
+* S. Yao, S. Hu, Y. Zhao, **A. Zhang**, and T. Abdelzaher<br>
 <b>DeepSense: A Unified Deep Learning Framework for Time-Series Mobile Sensing Data Processing</b><br>
@@
 
-* S. Yao, Y. Zhao, A. Zhang, S. Lu, and T. Abdelzaher<br>
+* S. Yao, Y. Zhao, **A. Zhang**, S. Lu, and T. Abdelzaher<br>
 <b>DeepIoT: Compressing Deep Neural Network Structures for Sensing Systems without Loss of Performance</b><br>
@@
 
-* S. Yao, Y. Zhao, H. Shao, A. Zhang, C. Zhang, S. Li, and T. Abdelzaher<br>
+* S. Yao, Y. Zhao, H. Shao, **A. Zhang**, C. Zhang, S. Li, and T. Abdelzaher<br>
 <b>RDeepSense: Reliable Deep Mobile Computing Models with Uncertainty Estimations</b><br>
@@
 
-* A. Zhang, A. Goyal, R. Baeza-Yates, Y. Chang, J. Han, C. A. Gunter, and H. Deng<br>
+* **A. Zhang**, A. Goyal, R. Baeza-Yates, Y. Chang, J. Han, C. A. Gunter, and H. Deng<br>
 <b>Towards Mobile Query Auto-Completion: An Efficient Mobile Application-Aware Approach</b><br>
@@
 
-* A. Zhang and Q. Gu<br>
+* **A. Zhang** and Q. Gu<br>
 <b>Accelerated Stochastic Block Coordinate Descent with Optimal Sampling</b> [<a href="papers/supp_asbcd.pdf" target="_blank">Proof of Lemmas</a>]<br>
@@
 
-* S. Demetriou, W. Merrill, W. Yang, A. Zhang, and C. A. Gunter<br>
+* S. Demetriou, W. Merrill, W. Yang, **A. Zhang**, and C. A. Gunter<br>
 <b>Free for All! Assessing User Data Exposure to Advertising Libraries on Android</b><br>
@@
 
-* R. Zhu, A. Zhang, J. Peng, and C. Zhai<br>
+* R. Zhu, **A. Zhang**, J. Peng, and C. Zhai<br>
 <b>Exploiting Temporal Divergence of Topic Distributions for Event Detection</b><br>
@@
 
-* A. Zhang, A. Goyal, W. Kong, H. Deng, A. Dong, Y. Chang, C. A. Gunter, and J. Han<br>
+* **A. Zhang**, A. Goyal, W. Kong, H. Deng, A. Dong, Y. Chang, C. A. Gunter, and J. Han<br>
 <b>adaQAC: Adaptive Query Auto-Completion via Implicit Negative Feedback</b><br>
@@
 
-* W. Kong, R. Li, J. Luo, A. Zhang, Y. Chang, and J. Allan<br>
+* W. Kong, R. Li, J. Luo, **A. Zhang**, Y. Chang, and J. Allan<br>
 <b>Predicting Search Intent Based on Pre-Search Context</b><br>
@@
 
-* H. Fu, A. Zhang, and X. Xie<br>
+* H. Fu, **A. Zhang**, and X. Xie<br>
 <b>Effective Social Graph De-anonymization based on Graph Structure and Descriptive Information</b><br>
@@
 
-* X. Lu, A. Zhang, C. A. Gunter, D. Fabbri, D. Liebovitz, and B. Malin<br>
+* X. Lu, **A. Zhang**, C. A. Gunter, D. Fabbri, D. Liebovitz, and B. Malin<br>
 <b>Discovering De Facto Diagnosis Specialties</b><br>
@@
 
-* A. Zhang, X. Xie, K. C.-C. Chang, C. A. Gunter, J. Han, and X. Wang<br>
+* **A. Zhang**, X. Xie, K. C.-C. Chang, C. A. Gunter, J. Han, and X. Wang<br>
 <b>Privacy Risk in Anonymized Heterogeneous Information Networks</b><br>
@@
 
-* H. Fu, A. Zhang, and X. Xie<br>
+* H. Fu, **A. Zhang**, and X. Xie<br>
 <b>De-anonymizing Social Graphs via Node Similarity</b><br>

### 2022-12-28 quarto/index.qmd
update

--- 2022-12-28 quarto/index.qmd
@@
 
-* A. Zhang, Z. C. Lipton, M. Li, and A. J. Smola<br>
+* **A. Zhang**, Z. C. Lipton, M. Li, and A. J. Smola<br>
  	<a href="https://d2l.ai" target="_blank">Dive into Deep Learning</a><br>
@@
 
-* A. Zhang, M. Li, Z. C. Lipton, and A. J. Smola<br>
+* **A. Zhang**, M. Li, Z. C. Lipton, and A. J. Smola<br>
 	<a href="https://zh.d2l.ai" target="_blank">动手学深度学习</a><br>
@@
 
-* Z. Zhang, A. Zhang, M. Li, and A. J. Smola<br>
+* Z. Zhang, **A. Zhang**, M. Li, and A. J. Smola<br>
 	<a href="https://arxiv.org/abs/2210.03493" target="_blank">Automatic Chain of Thought Prompting in Large Language Models</a><br>
@@
 
-* J. Chen, A. Zhang, X. Shi, M. Li, A. J. Smola, and D. Yang<br>
+* J. Chen, **A. Zhang**, X. Shi, M. Li, A. J. Smola, and D. Yang<br>
 	<a href="https://d2l-webdata.s3.us-west-2.amazonaws.com/papers/PEFT-design-spaces.pdf" target="_blank">Parameter-Efficient Fine-Tuning Design Spaces</a><br>
@@
 
-* M. S. Bari, A. Zhang, S. Zheng, X. Shi, Y. Zhu, S. Joty, M. Li<br>
+* M. S. Bari, **A. Zhang**, S. Zheng, X. Shi, Y. Zhu, S. Joty, M. Li<br>
 	<a href="https://arxiv.org/abs/2212.10929" target="_blank">
@@
 
-* H. Wang, A. Zhang, Y. Zhu, S. Zheng, M. Li, A. J. Smola, and Z. Wang<br>
+* H. Wang, **A. Zhang**, Y. Zhu, S. Zheng, M. Li, A. J. Smola, and Z. Wang<br>
 	<a href="https://arxiv.org/pdf/2207.01160.pdf" target="_blank">Partial and Asymmetric Contrastive Learning for Out-of-Distribution Detection in Long-Tailed Recognition</a><br>
@@
 
-* H. Wang, A. Zhang, S. Zheng, X. Shi, M. Li, and Z. Wang<br>
+* H. Wang, **A. Zhang**, S. Zheng, X. Shi, M. Li, and Z. Wang<br>
 	<a href="https://arxiv.org/pdf/2207.01156.pdf" target="_blank">Removing Batch Normalization Boosts Adversarial Training</a><br>
@@
 
-* E. Grassucci, A. Zhang, and D. Comminiello<br>
+* E. Grassucci, **A. Zhang**, and D. Comminiello<br>
 	<a href="https://arxiv.org/abs/2110.04176" target="_blank">PHNNs: Lightweight Neural Networks via Parameterized Hypercomplex Convolutions</a><br>
@@
 
-* A. Zhang, Y. Tay, S. Zhang, A. Chan, A. T. Luu, S. C. Hui, and J. Fu<br>
+* **A. Zhang**, Y. Tay, S. Zhang, A. Chan, A. T. Luu, S. C. Hui, and J. Fu<br>
 	<a href="https://arxiv.org/abs/2102.08597" target="_blank">Beyond Fully-Connected Layers with Quaternions: Parameterization of Hypercomplex Multiplications with 1/n Parameters</a><br>
@@
 
+## Tutorials
+
+* with A. J. Smola<br>
+	<b>Attention in Deep Learning</b> [<a href="http://alex.smola.org/talks/ICML19-attention.key" target="_blank">Keynote</a>] [<a href="http://alex.smola.org/talks/ICML19-attention.pdf" target="_blank">PDF</a>] [<a href="https://www.youtube.com/watch?v=nS1Lse2B48w" target="_blank">Video</a>]<br>
+	In *The 36th International Conference on Machine Learning* (**ICML**), 2019
+
+* with H. Lin, X. Shi, L. Lausen, H. He, S. Zha, and A. J. Smola<br>
+	<b>Dive into Deep Learning for Natural Language Processing</b> <br>
+	In *Conference on Empirical Methods in Natural Language Processing* (**EMNLP**), 2019
+
+* with H. Lin, L. Lausen, S. Zha, A. J. Smola, C. Wang, and M. Li<br>
+	<b>From Shallow to Deep Language Representations: Pre-training, Fine-tuning, and Beyond</b> [<a href="https://github.com/astonzhang/KDD19-tutorial" target="_blank">Website</a>]<br>
+	In *The 25th ACM SIGKDD Conference on Knowledge Discovery and Data Mining* (**KDD**), 2019
+
+* with H. Zhang, T. He, Z. Zhang, Z. Zhang, H. Lin, and M. Li<br>
+	<b>Everything You Need to Know to Reproduce SOTA Deep Learning Models from Hands-on Tutorial</b><br>
+	In *International Conference on Computer Vision* (**ICCV**), 2019
+
 ## Services
@@
 * Area Chair
-	* Annual Meeting of the Association for Computational Linguistics (ACL)
-	* Conference on Empirical Methods in Natural Language Processing (EMNLP)
+	* Annual Meeting of the Association for Computational Linguistics (**ACL**)
+	* Conference on Empirical Methods in Natural Language Processing (**EMNLP**)
 
 * Senior Program Committee
-	* AAAI Conference on Artificial Intelligence (AAAI)
+	* AAAI Conference on Artificial Intelligence (**AAAI**)
 

### 2022-12-28 quarto/index.qmd
update

@@
 
-<b>Aston Zhang</b> is a senior scientist at Amazon Web Services AI.
+**Aston Zhang** is a senior scientist at Amazon Web Services AI.
 His current research interests focus on efficient and robust methods for machine learning and natural language processing.
@@
  	<a href="https://d2l.ai" target="_blank">Dive into Deep Learning</a><br>
-	Cambridge University Press, 2023<br>
+	*Cambridge University Press*, 2023<br>
 	* Adopted at 400 universities from 60 countries
@@
 	<a href="https://zh.d2l.ai" target="_blank">动手学深度学习</a><br>
-	人民邮电出版社, 2nd ed., 2023, 1st ed., 2019<br>
+	*人民邮电出版社*, 2nd ed., 2023, 1st ed., 2019<br>
 	* <a href="https://github.com/d2l-ai/d2l-zh/raw/v1/img/frontpage/jd-190715-en.png" target="_blank">Best seller</a> of new books in "Computers and Internet" at the largest Chinese online bookstore<br>
@@
 	<a href="https://arxiv.org/abs/2210.03493" target="_blank">Automatic Chain of Thought Prompting in Large Language Models</a><br>
-	<i>"Let's think not just step by step, but also one by one."</i>
-	In <i>arXiv</i>, 2022<br>
+	*"Let's think not just step by step, but also one by one."*
+	In *arXiv*, 2022<br>
 	<a href="https://twitter.com/astonzhangAZ/status/1579489453789581312" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
@@
 	<a href="https://d2l-webdata.s3.us-west-2.amazonaws.com/papers/PEFT-design-spaces.pdf" target="_blank">Parameter-Efficient Fine-Tuning Design Spaces</a><br>
-	<i>"Adapters, prefix tuning, BitFit, LoRA, ... do design patterns exist?"</i>
-	In <i>arXiv</i>, 2022<br>
+	*"Adapters, prefix tuning, BitFit, LoRA, ... do design patterns exist?"*
+	In *arXiv*, 2022<br>
 
@@
 	SPT: Semi-Parametric Prompt Tuning for Multitask Prompted Learning</a><br>
-	<i>"If your prompt tuning can't converge easily, make it semi-parametric."</i>
-	In <i>arXiv</i>, 2022<br>
+	*"If your prompt tuning can't converge easily, make it semi-parametric."*
+	In *arXiv*, 2022<br>
 	<a href="https://twitter.com/astonzhangAZ/status/1605959819894349824" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
@@
 	<a href="https://arxiv.org/pdf/2207.01160.pdf" target="_blank">Partial and Asymmetric Contrastive Learning for Out-of-Distribution Detection in Long-Tailed Recognition</a><br>
-	In <i>Proceedings of International Conference on Machine Learning</i> (<b>ICML, Long Presentation</b>), 2022<br>
+	In *Proceedings of International Conference on Machine Learning* (**ICML, Long Presentation**), 2022<br>
 	<a href="https://twitter.com/astonzhangAZ/status/1549800894840971265" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
@@
 	<a href="https://arxiv.org/pdf/2207.01156.pdf" target="_blank">Removing Batch Normalization Boosts Adversarial Training</a><br>
-	In <i>Proceedings of International Conference on Machine Learning</i> (<b>ICML</b>), 2022<br>
+	In *Proceedings of International Conference on Machine Learning* (**ICML**), 2022<br>
 	<a href="https://twitter.com/astonzhangAZ/status/1549069378250874880" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
@@
 	<a href="https://arxiv.org/abs/2110.04176" target="_blank">PHNNs: Lightweight Neural Networks via Parameterized Hypercomplex Convolutions</a><br>
-	In <i>IEEE Transactions on Neural Networks and Learning Systems</i> (<b>TNNLS</b>), 2022<br>
+	In *IEEE Transactions on Neural Networks and Learning Systems* (**TNNLS**), 2022<br>
 	<a href="https://github.com/eleGAN23/HyperNets" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>
@@
 	<a href="https://arxiv.org/abs/2102.08597" target="_blank">Beyond Fully-Connected Layers with Quaternions: Parameterization of Hypercomplex Multiplications with 1/n Parameters</a><br>
-	In <i>Proceedings of the International Conference on Learning Representations</i> (<b>ICLR, <font color="red">Outstanding Paper Award</font></b>), 2021<br>
+	In *Proceedings of the International Conference on Learning Representations* (**ICLR, <font color="red">Outstanding Paper Award</font>**), 2021<br>
 	<a href="https://github.com/astonzhang/Parameterization-of-Hypercomplex-Multiplications" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>
@@
 * with A. J. Smola<br>
-	<b>Attention in Deep Learning</b> [<a href="http://alex.smola.org/talks/ICML19-attention.key" target="_blank">Keynote</a>] [<a href="http://alex.smola.org/talks/ICML19-attention.pdf" target="_blank">PDF</a>] [<a href="https://www.youtube.com/watch?v=nS1Lse2B48w" target="_blank">Video</a>]<br>
+	**Attention in Deep Learning** [<a href="http://alex.smola.org/talks/ICML19-attention.key" target="_blank">Keynote</a>] [<a href="http://alex.smola.org/talks/ICML19-attention.pdf" target="_blank">PDF</a>] [<a href="https://www.youtube.com/watch?v=nS1Lse2B48w" target="_blank">Video</a>]<br>
 	In *The 36th International Conference on Machine Learning* (**ICML**), 2019
@@
 * with H. Lin, X. Shi, L. Lausen, H. He, S. Zha, and A. J. Smola<br>
-	<b>Dive into Deep Learning for Natural Language Processing</b> <br>
+	**Dive into Deep Learning for Natural Language Processing** <br>
 	In *Conference on Empirical Methods in Natural Language Processing* (**EMNLP**), 2019
@@
 * with H. Lin, L. Lausen, S. Zha, A. J. Smola, C. Wang, and M. Li<br>
-	<b>From Shallow to Deep Language Representations: Pre-training, Fine-tuning, and Beyond</b> [<a href="https://github.com/astonzhang/KDD19-tutorial" target="_blank">Website</a>]<br>
+	**From Shallow to Deep Language Representations: Pre-training, Fine-tuning, and Beyond** [<a href="https://github.com/astonzhang/KDD19-tutorial" target="_blank">Website</a>]<br>
 	In *The 25th ACM SIGKDD Conference on Knowledge Discovery and Data Mining* (**KDD**), 2019
@@
 * with H. Zhang, T. He, Z. Zhang, Z. Zhang, H. Lin, and M. Li<br>
-	<b>Everything You Need to Know to Reproduce SOTA Deep Learning Models from Hands-on Tutorial</b><br>
+	**Everything You Need to Know to Reproduce SOTA Deep Learning Models from Hands-on Tutorial**<br>
 	In *International Conference on Computer Vision* (**ICCV**), 2019

### 2022-12-28 quarto/papers.qmd
update

@@
 <a href="https://arxiv.org/abs/2210.03493" target="_blank">Automatic Chain of Thought Prompting in Large Language Models</a><br>
-<i>"Let's think not just step by step, but also one by one."</i>
-In <i>arXiv</i>, 2022<br>
+*"Let's think not just step by step, but also one by one."*
+In *arXiv*, 2022<br>
 <a href="https://twitter.com/astonzhangAZ/status/1579489453789581312" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
@@
 <a href="https://d2l-webdata.s3.us-west-2.amazonaws.com/papers/PEFT-design-spaces.pdf" target="_blank">Parameter-Efficient Fine-Tuning Design Spaces</a><br>
-<i>"Adapters, prefix tuning, BitFit, LoRA, ... do design patterns exist?"</i>
-In <i>arXiv</i>, 2022<br>
+*"Adapters, prefix tuning, BitFit, LoRA, ... do design patterns exist?"*
+In *arXiv*, 2022<br>
 
@@
 SPT: Semi-Parametric Prompt Tuning for Multitask Prompted Learning</a><br>
-<i>"If your prompt tuning can't converge easily, make it semi-parametric."</i>
-In <i>arXiv</i>, 2022<br>
+*"If your prompt tuning can't converge easily, make it semi-parametric."*
+In *arXiv*, 2022<br>
 <a href="https://twitter.com/astonzhangAZ/status/1605959819894349824" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
@@
 <a href="https://arxiv.org/pdf/2207.01160.pdf" target="_blank">Partial and Asymmetric Contrastive Learning for Out-of-Distribution Detection in Long-Tailed Recognition</a><br>
-In <i>Proceedings of International Conference on Machine Learning</i> (<b>ICML, Long Presentation</b>), 2022<br>
+In *Proceedings of International Conference on Machine Learning* (**ICML, Long Presentation**), 2022<br>
 <a href="https://twitter.com/astonzhangAZ/status/1549800894840971265" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
@@
 <a href="https://arxiv.org/pdf/2207.01156.pdf" target="_blank">Removing Batch Normalization Boosts Adversarial Training</a><br>
-In <i>Proceedings of International Conference on Machine Learning</i> (<b>ICML</b>), 2022<br>
+In *Proceedings of International Conference on Machine Learning* (**ICML**), 2022<br>
 <a href="https://twitter.com/astonzhangAZ/status/1549069378250874880" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
@@
 <a href="https://arxiv.org/abs/2210.06428" target="_blank">Trap and Replace: Defending Backdoor Attacks by Trapping Them into an Easy-to-Replace Subnetwork</a><br>
-In <i>Proceedings of the Conference on Neural Information Processing Systems</i> (<b>NeurIPS</b>), 2022
+In *Proceedings of the Conference on Neural Information Processing Systems* (**NeurIPS**), 2022
 
@@
 <a href="https://arxiv.org/pdf/2010.12742.pdf" target="_blank">Text Style Transfer: A Review and Experimental Evaluation</a><br>
-In <i>ACM SIGKDD Explorations</i>, 2022<br>
+In *ACM SIGKDD Explorations*, 2022<br>
 
@@
 SMILE: Scaling Mixture-of-Experts with Efficient Bi-level Routing</a><br>
-<i>"2.5x speedup over Switch Transformers"</i>
-In <i>arXiv</i>, 2022<br>
+*"2.5x speedup over Switch Transformers"*
+In *arXiv*, 2022<br>
 
@@
 <a href="https://arxiv.org/abs/2206.08358" target="_blank">MixGen: A New Multi-Modal Data Augmentation</a><br>
-<i>"Interpolate images, concatenate text."</i>
-In <i>arXiv</i>, 2022<br>
+*"Interpolate images, concatenate text."*
+In *arXiv*, 2022<br>
 <a href="https://twitter.com/astonzhangAZ/status/1537860202652786688" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
@@
 <a href="https://arxiv.org/abs/2110.04176" target="_blank">PHNNs: Lightweight Neural Networks via Parameterized Hypercomplex Convolutions</a><br>
-In <i>IEEE Transactions on Neural Networks and Learning Systems</i> (<b>TNNLS</b>), 2022<br>
+In *IEEE Transactions on Neural Networks and Learning Systems* (**TNNLS**), 2022<br>
 <a href="https://github.com/eleGAN23/HyperNets" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>
@@
 <a href="https://arxiv.org/abs/2102.08597" target="_blank">Beyond Fully-Connected Layers with Quaternions: Parameterization of Hypercomplex Multiplications with 1/n Parameters</a><br>
-In <i>Proceedings of the International Conference on Learning Representations</i> (<b>ICLR, <font color="red">Outstanding Paper Award</font></b>), 2021<br>
+In *Proceedings of the International Conference on Learning Representations* (**ICLR, <font color="red">Outstanding Paper Award</font>**), 2021<br>
 <a href="https://github.com/astonzhang/Parameterization-of-Hypercomplex-Multiplications" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>
@@
 <a href="https://arxiv.org/pdf/2006.03535.pdf" target="_blank">CoCon: A Self-Supervised Approach for Controlled Text Generation</a><br>
-In <i>Proceedings of the International Conference on Learning Representations</i> (<b>ICLR</b>), 2021<br>
+In *Proceedings of the International Conference on Learning Representations* (**ICLR**), 2021<br>
 <a href="https://github.com/alvinchangw/COCON_ICLR2021" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>
@@
 <a href="https://proceedings.neurips.cc/paper/2021/file/3341f6f048384ec73a7ba2e77d2db48b-Paper.pdf" target="_blank">Self-Instantiated Recurrent Units with Dynamic Soft Recursion</a><br>
-In <i>Proceedings of the Conference on Neural Information Processing Systems</i> (<b>NeurIPS</b>), 2021<br>
+In *Proceedings of the Conference on Neural Information Processing Systems* (**NeurIPS**), 2021<br>
 <a href="https://github.com/astonzhang/Self-IRU" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>
@@
 <a href="https://arxiv.org/pdf/1906.09338.pdf" target="_blank">G-PATE: Scalable Differentially Private Data Generator via Private Aggregation of Teacher Discriminators</a><br>
-In <i>Proceedings of the Conference on Neural Information Processing Systems</i> (<b>NeurIPS</b>), 2021<br>
+In *Proceedings of the Conference on Neural Information Processing Systems* (**NeurIPS**), 2021<br>
 <a href="https://github.com/AI-secure/G-PATE" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>
@@
 <a href="https://arxiv.org/abs/2102.06790" target="_blank">A Unified Lottery Ticket Hypothesis for Graph Neural Networks</a><br>
-In <i>Proceedings of International Conference on Machine Learning</i> (<b>ICML</b>), 2021<br>
+In *Proceedings of International Conference on Machine Learning* (**ICML**), 2021<br>
 <a href="https://github.com/VITA-Group/Unified-LTH-GNN" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>
@@
 * H. Shao, Z. Xiao, S. Yao, D. Sun, **A. Zhang**, S. Liu, T. Wang, J. Li, and T. Abdelzaher<br>
-<b>ControlVAE: Tuning, Analytical Properties, and Performance Analysis</b><br>
-In <i>Transactions on Pattern Analysis and Machine Intelligence</i> (<b>TPAMI</b>), 2021
+**ControlVAE: Tuning, Analytical Properties, and Performance Analysis**<br>
+In *Transactions on Pattern Analysis and Machine Intelligence* (**TPAMI**), 2021
 
 * **A. Zhang**, A. Chan, Y. Tay, J. Fu, S. Wang, S. Zhang, H. Shao, S. Yao, and R. Lee<br>
-<b>On Orthogonality Constraints for Transformers</b><br>
-In <i>Proceedings of the 59th Annual Meeting of the Association for Computational Linguistics</i> (<b>ACL, Oral</b>), 2021
+**On Orthogonality Constraints for Transformers**<br>
+In *Proceedings of the 59th Annual Meeting of the Association for Computational Linguistics* (**ACL, Oral**), 2021
 
 * H. Shao, J. Wang, H. Lin, X. Zhang, **A. Zhang**, H. Ji, and T. Abdelzaher<br>
-<b>Controllable and Diverse Text Generation in E-commerce</b><br>
-In <i>Proceedings of the Web Conference</i> (<b>WWW</b>), 2021
+**Controllable and Diverse Text Generation in E-commerce**<br>
+In *Proceedings of the Web Conference* (**WWW**), 2021
 
 * S. Zhang, H. Liu, **A. Zhang**, Y. Hu, C. Zhang, Y. Li, T. Zhu, S. He, and W. Ou<br>
-<b>Learning User Representations with Hypercuboids for Recommender Systems</b><br>
-In <i>Proceedings of the 14th International Conference on Web Search and Data Mining</i> (<b>WSDM</b>), 2021
+**Learning User Representations with Hypercuboids for Recommender Systems**<br>
+In *Proceedings of the 14th International Conference on Web Search and Data Mining* (**WSDM**), 2021
 
@@
 * H. Shao, S. Yao, D. Sun, **A. Zhang**, S. Liu, D. Liu, J. Wang, and T. Abdelzaher<br>
-<b>ControlVAE: Controllable Variational Autoencoder</b><br>
-In <i>Proceedings of International Conference on Machine Learning</i> (<b>ICML</b>), 2020
+**ControlVAE: Controllable Variational Autoencoder**<br>
+In *Proceedings of International Conference on Machine Learning* (**ICML**), 2020
 
 * J. Guo, H. He, T. He, L. Lausen, M. Li, H. Lin, X. Shi, C. Wang, J. Xie, S. Zha, **A. Zhang**, H. Zhang, Z. Zhang, Z. Zhang, S. Zheng, and Y. Zhu<br>
-<b>GluonCV and GluonNLP: Deep Learning in Computer Vision and Natural Language Processing</b><br>
-In <i>Journal of Machine Learning Research</i> (<b>JMLR</b>), Vol. 21, No. 23, 2020
+**GluonCV and GluonNLP: Deep Learning in Computer Vision and Natural Language Processing**<br>
+In *Journal of Machine Learning Research* (**JMLR**), Vol. 21, No. 23, 2020
 
 * A. Chan, Y. Tay, Y. S. Ong, and **A. Zhang**<br>
-<b>Poison Attacks against Text Datasets with Conditional Adversarially Regularized Autoencoder</b><br>
-In <i>Findings of Empirical Methods in Natural Language Processing</i> (<b>EMNLP-Findings</b>), 2020
+**Poison Attacks against Text Datasets with Conditional Adversarially Regularized Autoencoder**<br>
+In *Findings of Empirical Methods in Natural Language Processing* (**EMNLP-Findings**), 2020
 
 * H. Shao, D. Sun, J. Wu, Z. Zhang, **A. Zhang**, S. Yao, S. Liu, T. Wang, C. Zhang, and T. Abdelzaher<br>
-<b>GitHub Repository Recommendation for Academic Papers</b><br>
-In <i>Proceedings of the Web Conference</i> (<b>WWW</b>), 2020
+**GitHub Repository Recommendation for Academic Papers**<br>
+In *Proceedings of the Web Conference* (**WWW**), 2020
 
@@
 * Y. Tay, A. T. Luu, **A. Zhang**, S. Wang, and S. C. Hui<br>
-<b>Compositional De-Attention Networks</b><br>
-In <i>Proceedings of the Conference on Neural Information Processing Systems</i> (<b>NeurIPS</b>), 2019
+**Compositional De-Attention Networks**<br>
+In *Proceedings of the Conference on Neural Information Processing Systems* (**NeurIPS**), 2019
 
 * S. Zhang, L. Yao, L. V. Tran, **A. Zhang**, and Y. Tay<br>
-<b>Quaternion Collaborative Filtering for Recommendation</b><br>
-In <i>Proceedings of the 28th International Joint Conference on Artificial Intelligence</i> (<b>IJCAI</b>), 2019
+**Quaternion Collaborative Filtering for Recommendation**<br>
+In *Proceedings of the 28th International Joint Conference on Artificial Intelligence* (**IJCAI**), 2019
 
 * Y. Tay, **A. Zhang**, A. T. Luu, J. Rao, S. Zhang, S. Wang, J. Fu, and S. C. Hui<br>
-<b>Lightweight and Efficient Neural Natural Language Processing with Quaternion Networks</b><br>
-In <i>Proceedings of the 57th Annual Meeting of the Association for Computational Linguistics</i> (<b>ACL</b>), 2019
+**Lightweight and Efficient Neural Natural Language Processing with Quaternion Networks**<br>
+In *Proceedings of the 57th Annual Meeting of the Association for Computational Linguistics* (**ACL**), 2019
 
 * Y. Tay, S. Wang, A. T. Luu, J. Fu, M. C. Phan, X. Yuan, J. Rao, S. C. Hui, and **A. Zhang**<br>
-<b>Simple and Effective Curriculum Pointer-Generator Networks for Reading Comprehension over Long Narratives</b><br>
-In <i>Proceedings of the 57th Annual Meeting of the Association for Computational Linguistics</i> (<b>ACL</b>), 2019
+**Simple and Effective Curriculum Pointer-Generator Networks for Reading Comprehension over Long Narratives**<br>
+In *Proceedings of the 57th Annual Meeting of the Association for Computational Linguistics* (**ACL**), 2019
 
 * A. El-Kishky, F. Xu, **A. Zhang**, and J. Han<br>
-<b>Parsimonious Morpheme Segmentation with an Application to Enriching Word Embeddings</b><br>
-In <i>Proceedings of the IEEE International Conference on Big Data</i> (<b>IEEE BigData</b>), 2019
+**Parsimonious Morpheme Segmentation with an Application to Enriching Word Embeddings**<br>
+In *Proceedings of the IEEE International Conference on Big Data* (**IEEE BigData**), 2019
 
@@
 * S. Yao, Y. Zhao, **A. Zhang**, S. Hu, H. Shao, C. Zhang, L. Su, and T. Abdelzaher<br>
-<b>Deep Learning for the Internet of Things</b><br>
-In <i>Computer</i>, 2018 (selected as May 2018 cover feature of the flagship magazine of the IEEE Computer Society)
+**Deep Learning for the Internet of Things**<br>
+In *Computer*, 2018 (selected as May 2018 cover feature of the flagship magazine of the IEEE Computer Society)
 
 * A. El-Kishky, F. Xu, **A. Zhang**, S. Macke, and J. Han<br>
-<b>Entropy-Based Subword with an Application to Word Embeddings</b><br>
-In <i>Proceedings of the 2nd Workshop on Subword and Character Level Models in NLP at the 16th Annual Conference of the North American Chapter of the Association for Computational Linguistics: Human Language Technologies</i> (<b>NAACL SCLeM</b>), 2018
+**Entropy-Based Subword with an Application to Word Embeddings**<br>
+In *Proceedings of the 2nd Workshop on Subword and Character Level Models in NLP at the 16th Annual Conference of the North American Chapter of the Association for Computational Linguistics: Human Language Technologies* (**NAACL SCLeM**), 2018
 
 * S. Yao, Y. Zhao, H. Shao, C. Zhang, **A. Zhang**, S. Hu, D. Liu, S. Liu, L. Su, and T. F. Abdelzaher<br>
-<b>SenseGAN: Enabling Deep Learning for Internet of Things with a Semi-Supervised Framework</b><br>
-In <i>Proceedings of the ACM on Interactive, Mobile, Wearable and Ubiquitous Technologies</i> (<b>ACM Ubicomp, <font color="red">Distinguished Paper Award</font></b>), 2018
+**SenseGAN: Enabling Deep Learning for Internet of Things with a Semi-Supervised Framework**<br>
+In *Proceedings of the ACM on Interactive, Mobile, Wearable and Ubiquitous Technologies* (**ACM Ubicomp, <font color="red">Distinguished Paper Award</font>**), 2018
 
 * **A. Zhang**, X. Lu, C. A. Gunter, S. Yao, F. Tao, R. Zhu, H. Gui, D. Fabbri, D. Liebovitz, and B. Malin<br>
-<b>De Facto Diagnosis Specialties: Recognition and Discovery</b><br>
-In <i>Learning Health Systems</i> (<b>LHS</b>), 2018
+**De Facto Diagnosis Specialties: Recognition and Discovery**<br>
+In *Learning Health Systems* (**LHS**), 2018
 
 * S. Yao, Y. Zhao, H. Shao, C. Zhang, **A. Zhang**, D. Liu, S. Liu, L. Su, and T. Abdelzaher<br>
-<b>ApDeepSense: Deep Learning Uncertainty Estimation Without the Pain for IoT</b><br>
-In <i>Proceedings of the 38th IEEE International Conference on Distributed Computing Systems</i> (<b>ICDCS</b>), 2018
+**ApDeepSense: Deep Learning Uncertainty Estimation Without the Pain for IoT**<br>
+In *Proceedings of the 38th IEEE International Conference on Distributed Computing Systems* (**ICDCS**), 2018
 
 * **A. Zhang**, L. Garcia-Pueyo, J. B. Wendt, M. Najork, and A. Broder<br>
-<b>Email Category Prediction</b><br>
-In <i>Proceedings of the 26th International World Wide Web Conference </i> (<b>WWW</b>), 2017
+**Email Category Prediction**<br>
+In *Proceedings of the 26th International World Wide Web Conference * (**WWW**), 2017
 
 * S. Yao, S. Hu, Y. Zhao, **A. Zhang**, and T. Abdelzaher<br>
-<b>DeepSense: A Unified Deep Learning Framework for Time-Series Mobile Sensing Data Processing</b><br>
-In <i>Proceedings of the 26th International World Wide Web Conference</i> (<b>WWW</b>), 2017
+**DeepSense: A Unified Deep Learning Framework for Time-Series Mobile Sensing Data Processing**<br>
+In *Proceedings of the 26th International World Wide Web Conference* (**WWW**), 2017
 
 * S. Yao, Y. Zhao, **A. Zhang**, S. Lu, and T. Abdelzaher<br>
-<b>DeepIoT: Compressing Deep Neural Network Structures for Sensing Systems without Loss of Performance</b><br>
-In <i>Proceedings of the 15th ACM Conference on Embedded Networked Sensor Systems</i> (<b>ACM Sensys, <font color="red">Best Paper Award Nomination</font></b>), 2017
+**DeepIoT: Compressing Deep Neural Network Structures for Sensing Systems without Loss of Performance**<br>
+In *Proceedings of the 15th ACM Conference on Embedded Networked Sensor Systems* (**ACM Sensys, <font color="red">Best Paper Award Nomination</font>**), 2017
 
 * S. Yao, Y. Zhao, H. Shao, **A. Zhang**, C. Zhang, S. Li, and T. Abdelzaher<br>
-<b>RDeepSense: Reliable Deep Mobile Computing Models with Uncertainty Estimations</b><br>
-In <i>Proceedings of the ACM on Interactive, Mobile, Wearable and Ubiquitous Technologies</i> (<b>ACM Ubicomp</b>), 2017
+**RDeepSense: Reliable Deep Mobile Computing Models with Uncertainty Estimations**<br>
+In *Proceedings of the ACM on Interactive, Mobile, Wearable and Ubiquitous Technologies* (**ACM Ubicomp**), 2017
 
 * **A. Zhang**, A. Goyal, R. Baeza-Yates, Y. Chang, J. Han, C. A. Gunter, and H. Deng<br>
-<b>Towards Mobile Query Auto-Completion: An Efficient Mobile Application-Aware Approach</b><br>
-In <i>Proceedings of the 25th International World Wide Web Conference</i> (<b>WWW</b>), 2016
+**Towards Mobile Query Auto-Completion: An Efficient Mobile Application-Aware Approach**<br>
+In *Proceedings of the 25th International World Wide Web Conference* (**WWW**), 2016
 
 * **A. Zhang** and Q. Gu<br>
-<b>Accelerated Stochastic Block Coordinate Descent with Optimal Sampling</b> [<a href="papers/supp_asbcd.pdf" target="_blank">Proof of Lemmas</a>]<br>
-In <i>Proceedings of the 22nd ACM SIGKDD Conference on Knowledge Discovery and Data Mining</i> (<b>KDD</b>), 2016
+**Accelerated Stochastic Block Coordinate Descent with Optimal Sampling** [<a href="papers/supp_asbcd.pdf" target="_blank">Proof of Lemmas</a>]<br>
+In *Proceedings of the 22nd ACM SIGKDD Conference on Knowledge Discovery and Data Mining* (**KDD**), 2016
 
 * S. Demetriou, W. Merrill, W. Yang, **A. Zhang**, and C. A. Gunter<br>
-<b>Free for All! Assessing User Data Exposure to Advertising Libraries on Android</b><br>
-In <i>Proceedings of the Network and Distributed System Security Symposium</i> (<b>NDSS</b>), 2016
+**Free for All! Assessing User Data Exposure to Advertising Libraries on Android**<br>
+In *Proceedings of the Network and Distributed System Security Symposium* (**NDSS**), 2016
 
 * R. Zhu, **A. Zhang**, J. Peng, and C. Zhai<br>
-<b>Exploiting Temporal Divergence of Topic Distributions for Event Detection</b><br>
-In <i>Proceedings of the IEEE International Conference on Big Data</i> (<b>IEEE BigData</b>), 2016
+**Exploiting Temporal Divergence of Topic Distributions for Event Detection**<br>
+In *Proceedings of the IEEE International Conference on Big Data* (**IEEE BigData**), 2016
 
 * **A. Zhang**, A. Goyal, W. Kong, H. Deng, A. Dong, Y. Chang, C. A. Gunter, and J. Han<br>
-<b>adaQAC: Adaptive Query Auto-Completion via Implicit Negative Feedback</b><br>
-In <i>Proceedings of the 38th International ACM SIGIR Conference on Research and Development in Information Retrieval</i> (<b>SIGIR</b>), 2015
+**adaQAC: Adaptive Query Auto-Completion via Implicit Negative Feedback**<br>
+In *Proceedings of the 38th International ACM SIGIR Conference on Research and Development in Information Retrieval* (**SIGIR**), 2015
 
 * W. Kong, R. Li, J. Luo, **A. Zhang**, Y. Chang, and J. Allan<br>
-<b>Predicting Search Intent Based on Pre-Search Context</b><br>
-In <i>Proceedings of the 38th International ACM SIGIR Conference on Research and Development in Information Retrieval</i> (<b>SIGIR</b>), 2015
+**Predicting Search Intent Based on Pre-Search Context**<br>
+In *Proceedings of the 38th International ACM SIGIR Conference on Research and Development in Information Retrieval* (**SIGIR**), 2015
 
 * H. Fu, **A. Zhang**, and X. Xie<br>
-<b>Effective Social Graph De-anonymization based on Graph Structure and Descriptive Information</b><br>
-In <i>ACM Transactions on Intelligent Systems and Technology</i> (<b>ACM TIST</b>), Vol. 6, No. 4, 2015
+**Effective Social Graph De-anonymization based on Graph Structure and Descriptive Information**<br>
+In *ACM Transactions on Intelligent Systems and Technology* (**ACM TIST**), Vol. 6, No. 4, 2015
 
 * X. Lu, **A. Zhang**, C. A. Gunter, D. Fabbri, D. Liebovitz, and B. Malin<br>
-<b>Discovering De Facto Diagnosis Specialties</b><br>
-In <i>Proceedings of the 6th ACM Conference on Bioinformatics, Computational Biology, and Health Informatics</i> (<b>ACM BCB</b>), 2015
+**Discovering De Facto Diagnosis Specialties**<br>
+In *Proceedings of the 6th ACM Conference on Bioinformatics, Computational Biology, and Health Informatics* (**ACM BCB**), 2015
 
 * **A. Zhang**, X. Xie, K. C.-C. Chang, C. A. Gunter, J. Han, and X. Wang<br>
-<b>Privacy Risk in Anonymized Heterogeneous Information Networks</b><br>
-In <i>Proceedings of the 17th International Conference on Extending Database Technology</i> (<b>EDBT</b>), 2014
+**Privacy Risk in Anonymized Heterogeneous Information Networks**<br>
+In *Proceedings of the 17th International Conference on Extending Database Technology* (**EDBT**), 2014
 
 * H. Fu, **A. Zhang**, and X. Xie<br>
-<b>De-anonymizing Social Graphs via Node Similarity</b><br>
-In <i>Proceedings of the 23rd International World Wide Web Conference</i> (<b>WWW</b>), 2014
+**De-anonymizing Social Graphs via Node Similarity**<br>
+In *Proceedings of the 23rd International World Wide Web Conference* (**WWW**), 2014

### 2022-12-28 preview.sh

@@ -1,0 +1,2 @@
+cd quarto
+quarto preview

### 2022-12-28 quarto/index.qmd
update

@@
-<img src="img/aston.jpg"  border="0" vspace="10" hspace="0" /><br>
+<img src="img/aston.jpg"  border="0" vspace="10" hspace="0" class="bio-photo"><br>
 <img src="img/email.png" height="30" width="200" vspace="0" ><br>
@@
 
-## [All Papers](papers.qmd)
+## All Papers
+
+[List](papers.qmd)
 
@@
 * Area Chair
-	* Annual Meeting of the Association for Computational Linguistics (**ACL**)
-	* Conference on Empirical Methods in Natural Language Processing (**EMNLP**)
+	* *Annual Meeting of the Association for Computational Linguistics* (**ACL**)
+	* *Conference on Empirical Methods in Natural Language Processing* (**EMNLP**)
 
 * Senior Program Committee
-	* AAAI Conference on Artificial Intelligence (**AAAI**)
+	* *AAAI Conference on Artificial Intelligence* (**AAAI**)
 
 * Journal Editorial Board
-	* Frontiers in Big Data
+	* *Frontiers in Big Data*
 

### 2022-12-31 quarto/index.qmd
div

@@
-<img src="img/aston.jpg"  border="0" vspace="10" hspace="0" class="bio-photo"><br>
-<img src="img/email.png" height="30" width="200" vspace="0" ><br>
+<div class="container">
 
+<div class="fixed"><img src="img/aston.jpg" width="200" border="0" vspace="20" hspace="0" class="bio-photo"></div>
+<div class="flex-item">
+<img src="img/email.png" height="30" width="200" vspace="50" ><br>
 <p align="left">
@@
 </p>
+</div>
+
+</div>
 
@@
 
-## Recent Papers
+## Papers ([All](papers.qmd))
 
@@
 	<a href="https://github.com/astonzhang/Parameterization-of-Hypercomplex-Multiplications" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>
-
-## All Papers
-
-[List](papers.qmd)
 

### 2022-12-31 quarto/index.qmd
Revert "div"
This reverts commit 9c43e3a7a19f272910bafa2d1cec48086f5d78ff.
update

--- 2022-12-28 quarto/index.qmd
@@
-<img src="img/aston.jpg"  border="0" vspace="10" hspace="0" class="bio-photo"><br>
-<img src="img/email.png" height="30" width="200" vspace="0" ><br>
+---
+about:
+  id: az-heading
+  template: trestles
+  image: img/aston.jpg
+  image-width: 200px
+  image-shape: rounded
+  links:
+    - icon: twitter
+      text: Twitter
+      href: https://twitter.com/astonzhangAZ
+    - icon: github
+      text: GitHub
+      href: https://github.com/astonzhang
+    - icon: bi-envelope
+      text: Email
+      href: img/email.png
+---
 
-<p align="left">
-	<a href="https://twitter.com/astonzhangAZ" title="Twitter" target="_blank"><img src="./img/logo-twitter.svg" class="bio-icon"></a>
-	<a href="https://github.com/astonzhang" title="GitHub" target="_blank"><img src="./img/logo-github.svg" class="bio-icon"></a>
-</p>
+:::{#az-heading}
 
@@
 He obtained his Ph.D. in Computer Science from University of Illinois at Urbana-Champaign.
+
+:::
 

### 2023-01-05 quarto/index.qmd
update

@@
 	<a href="https://d2l-webdata.s3.us-west-2.amazonaws.com/papers/PEFT-design-spaces.pdf" target="_blank">Parameter-Efficient Fine-Tuning Design Spaces</a><br>
-	*"Adapters, prefix tuning, BitFit, LoRA, ... do design patterns exist?"*
+	*"Don't assign the SAME parameter-efficient fine-tuning strategy to DIFFERENT layers."*
 	In *arXiv*, 2022<br>
 
-* M. S. Bari, **A. Zhang**, S. Zheng, X. Shi, Y. Zhu, S. Joty, M. Li<br>
+* M. S. Bari, **A. Zhang**, S. Zheng, X. Shi, Y. Zhu, S. Joty, and M. Li<br>
 	<a href="https://arxiv.org/abs/2212.10929" target="_blank">

### 2023-01-05 quarto/papers.qmd
update

@@
 ---
-
-## 2022
 
@@
 <a href="https://d2l-webdata.s3.us-west-2.amazonaws.com/papers/PEFT-design-spaces.pdf" target="_blank">Parameter-Efficient Fine-Tuning Design Spaces</a><br>
-*"Adapters, prefix tuning, BitFit, LoRA, ... do design patterns exist?"*
+*"Don't assign the SAME parameter-efficient fine-tuning strategy to DIFFERENT layers."*
 In *arXiv*, 2022<br>
 
-* M. S. Bari, **A. Zhang**, S. Zheng, X. Shi, Y. Zhu, S. Joty, M. Li<br>
+* M. S. Bari, **A. Zhang**, S. Zheng, X. Shi, Y. Zhu, S. Joty, and M. Li<br>
 <a href="https://arxiv.org/abs/2212.10929" target="_blank">
@@
 
-* C. He, S. Zheng, **A. Zhang**, G. Karypis, T. Chilimbi, M. Soltanolkotabi, S. Avestimehr<br>
-<a href="https://arxiv.org/abs/2212.05191" target="_blank">
-SMILE: Scaling Mixture-of-Experts with Efficient Bi-level Routing</a><br>
-*"2.5x speedup over Switch Transformers"*
+* Z. Liu, Z. Tang, X. Shi, **A. Zhang**, M. Li, A. Shrivastava, and A. Wilson<br>
+<a href="https://arxiv.org/abs/2212.14453" target="_blank">Learning Multimodal Data Augmentation in Feature Space</a><br>
+*"The first augmentation method to be applied to the joint of text, image, and tabular data."*
 In *arXiv*, 2022<br>
@@
 
+* C. He, S. Zheng, **A. Zhang**, G. Karypis, T. Chilimbi, M. Soltanolkotabi, and S. Avestimehr<br>
+<a href="https://arxiv.org/abs/2212.05191" target="_blank">
+SMILE: Scaling Mixture-of-Experts with Efficient Bi-level Routing</a><br>
+*"2.5x speedup over Switch Transformers."*
+In *arXiv*, 2022<br>
+
 * E. Grassucci, **A. Zhang**, and D. Comminiello<br>
@@
 <a href="https://github.com/eleGAN23/HyperNets" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>
-
-## 2021
 
@@
 
-## 2020
-
 * H. Shao, S. Yao, D. Sun, **A. Zhang**, S. Liu, D. Liu, J. Wang, and T. Abdelzaher<br>
@@
 In *Proceedings of the Web Conference* (**WWW**), 2020
-
-## 2019
 
@@
 In *Proceedings of the IEEE International Conference on Big Data* (**IEEE BigData**), 2019
-
-## Earlier
 

### 2023-01-06 quarto/index.qmd
update

@@
 * J. Chen, **A. Zhang**, X. Shi, M. Li, A. J. Smola, and D. Yang<br>
-	<a href="https://d2l-webdata.s3.us-west-2.amazonaws.com/papers/PEFT-design-spaces.pdf" target="_blank">Parameter-Efficient Fine-Tuning Design Spaces</a><br>
-	*"Don't assign the SAME parameter-efficient fine-tuning strategy to DIFFERENT layers."*
+	<a href="https://arxiv.org/abs/2301.01821" target="_blank">Parameter-Efficient Fine-Tuning Design Spaces</a><br>
+	*"Don't assign the same parameter-efficient fine-tuning strategy to different layers."*
 	In *arXiv*, 2022<br>
+	<a href="https://github.com/amazon-science/peft-design-spaces" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>
 

### 2023-01-06 quarto/papers.qmd
update

@@
 * J. Chen, **A. Zhang**, X. Shi, M. Li, A. J. Smola, and D. Yang<br>
-<a href="https://d2l-webdata.s3.us-west-2.amazonaws.com/papers/PEFT-design-spaces.pdf" target="_blank">Parameter-Efficient Fine-Tuning Design Spaces</a><br>
-*"Don't assign the SAME parameter-efficient fine-tuning strategy to DIFFERENT layers."*
+<a href="https://arxiv.org/abs/2301.01821" target="_blank">Parameter-Efficient Fine-Tuning Design Spaces</a><br>
+*"Don't assign the same parameter-efficient fine-tuning strategy to different layers."*
 In *arXiv*, 2022<br>
+<a href="https://github.com/amazon-science/peft-design-spaces" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>
 

### 2023-01-06 quarto/deploy.sh

@@ -1,3 +1,7 @@
 #!/bin/bash
 cp -r _site/* ..
 cd ..
+git status
+git add .
+git commit -m 'update'
+git push

### 2023-01-06 quarto/index.qmd
update

--- 2023-01-05 quarto/index.qmd
@@
 * J. Chen, **A. Zhang**, X. Shi, M. Li, A. J. Smola, and D. Yang<br>
-	<a href="https://d2l-webdata.s3.us-west-2.amazonaws.com/papers/PEFT-design-spaces.pdf" target="_blank">Parameter-Efficient Fine-Tuning Design Spaces</a><br>
-	*"Don't assign the SAME parameter-efficient fine-tuning strategy to DIFFERENT layers."*
+	<a href="https://arxiv.org/abs/2301.01821" target="_blank">Parameter-Efficient Fine-Tuning Design Spaces</a><br>
+	*"Don't assign the same parameter-efficient fine-tuning strategy to different layers."*
 	In *arXiv*, 2022<br>
+	<a href="https://twitter.com/astonzhangAZ/status/1611400421255557122" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
+	<a href="https://github.com/amazon-science/peft-design-spaces" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>
 

### 2023-01-06 quarto/papers.qmd
update

--- 2023-01-05 quarto/papers.qmd
@@
 * J. Chen, **A. Zhang**, X. Shi, M. Li, A. J. Smola, and D. Yang<br>
-<a href="https://d2l-webdata.s3.us-west-2.amazonaws.com/papers/PEFT-design-spaces.pdf" target="_blank">Parameter-Efficient Fine-Tuning Design Spaces</a><br>
-*"Don't assign the SAME parameter-efficient fine-tuning strategy to DIFFERENT layers."*
+<a href="https://arxiv.org/abs/2301.01821" target="_blank">Parameter-Efficient Fine-Tuning Design Spaces</a><br>
+*"Don't assign the same parameter-efficient fine-tuning strategy to different layers."*
 In *arXiv*, 2022<br>
+<a href="https://twitter.com/astonzhangAZ/status/1611400421255557122" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
+<a href="https://github.com/amazon-science/peft-design-spaces" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>
 

### 2023-01-13 quarto/deploy.sh
update

@@ -1,7 +1,7 @@
 #!/bin/bash
 cp -r _site/* ..
 cd ..
-git status
 git add .
+git status
 git commit -m 'update'
 git push

### 2023-01-13 quarto/index.qmd
update

@@
 
-**Aston Zhang** is a senior scientist at Amazon Web Services AI.
-His current research interests focus on efficient and robust methods for machine learning and natural language processing.
+**Aston Zhang** is a senior scientist at Amazon Web Services AI Research.
+He focuses on efficient and robust methods for machine learning and natural language processing.
 He received the <a href="https://iclr-conf.medium.com/announcing-iclr-2021-outstanding-paper-awards-9ae0514734ab" target="_blank">ICLR Outstanding Paper Award (2021)</a>,

### 2023-01-17 quarto/index.qmd
update

@@
 **Aston Zhang** is a senior scientist at Amazon Web Services AI Research.
-He focuses on efficient and robust methods for machine learning and natural language processing.
+He studies efficient and robust methods for machine learning and natural language processing, currently focusing on large language models.
 He received the <a href="https://iclr-conf.medium.com/announcing-iclr-2021-outstanding-paper-awards-9ae0514734ab" target="_blank">ICLR Outstanding Paper Award (2021)</a>,
@@
 
-Hi! I'm happy to connect and discuss. Preferred mode of contact is my email.
-My team is hiring intern scientists in machine learning
-(at our <a href="https://www.google.com/maps/place/2795+Augustine+Dr,+Santa+Clara,+CA+95054/@37.3835062,-121.9778599,17z/data=!3m1!4b1!4m5!3m4!1s0x808fc9f208b94da1:0xd2df9ae053c51af0!8m2!3d37.383502!4d-121.9756659" target="_blank">Santa Clara office</a> or other global offices).
-Just drop me a line.
+Hi! I'm happy to connect and discuss.
+My team is hiring intern scientists
+at our <a href="https://www.google.com/maps/place/2795+Augustine+Dr,+Santa+Clara,+CA+95054/@37.3835062,-121.9778599,17z/data=!3m1!4b1!4m5!3m4!1s0x808fc9f208b94da1:0xd2df9ae053c51af0!8m2!3d37.383502!4d-121.9756659" target="_blank">Santa Clara office</a> or other global offices.
+Just email me.
 
@@
 
-For prospective 2023 interns: my team is hiring research interns in NLP or ML. Just email me.
-
 * <a href="https://sites.cc.gatech.edu/~jchen896/" target="_blank">Jiaao Chen</a> (2022)

### 2023-01-20 quarto/index.qmd
update

@@
 	<a href="https://arxiv.org/abs/2210.03493" target="_blank">Automatic Chain of Thought Prompting in Large Language Models</a><br>
-	*"Let's think not just step by step, but also one by one."*
-	In *arXiv*, 2022<br>
+	In *Proceedings of the International Conference on Learning Representations* (**ICLR**), 2023<br>
 	<a href="https://twitter.com/astonzhangAZ/status/1579489453789581312" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
@@
 	<a href="https://arxiv.org/abs/2301.01821" target="_blank">Parameter-Efficient Fine-Tuning Design Spaces</a><br>
-	*"Don't assign the same parameter-efficient fine-tuning strategy to different layers."*
-	In *arXiv*, 2022<br>
+	In *Proceedings of the International Conference on Learning Representations* (**ICLR**), 2023<br>
 	<a href="https://twitter.com/astonzhangAZ/status/1611400421255557122" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
 	<a href="https://github.com/amazon-science/peft-design-spaces" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>
+
+* Z. Liu, Z. Tang, X. Shi, **A. Zhang**, M. Li, A. Shrivastava, and A. Wilson<br>
+	<a href="https://arxiv.org/abs/2212.14453" target="_blank">Learning Multimodal Data Augmentation in Feature Space</a><br>
+	In *Proceedings of the International Conference on Learning Representations* (**ICLR**), 2023<br>
+
+* T. Yang, Y. Zhu, Y. Xie, **A. Zhang**, C. Chen, and M. Li<br>
+	<a href="https://openreview.net/forum?id=CIoSZ_HKHS7" target="_blank">AIM: Adapting Image Models for Efficient Video Understanding</a><br>
+	In *Proceedings of the International Conference on Learning Representations* (**ICLR**), 2023<br>
 

### 2023-01-20 quarto/papers.qmd
update

--- 2023-01-05 quarto/papers.qmd
@@
 <a href="https://arxiv.org/abs/2210.03493" target="_blank">Automatic Chain of Thought Prompting in Large Language Models</a><br>
-*"Let's think not just step by step, but also one by one."*
-In *arXiv*, 2022<br>
+In *Proceedings of the International Conference on Learning Representations* (**ICLR**), 2023<br>
 <a href="https://twitter.com/astonzhangAZ/status/1579489453789581312" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
@@
 * J. Chen, **A. Zhang**, X. Shi, M. Li, A. J. Smola, and D. Yang<br>
-<a href="https://d2l-webdata.s3.us-west-2.amazonaws.com/papers/PEFT-design-spaces.pdf" target="_blank">Parameter-Efficient Fine-Tuning Design Spaces</a><br>
-*"Don't assign the SAME parameter-efficient fine-tuning strategy to DIFFERENT layers."*
-In *arXiv*, 2022<br>
+<a href="https://arxiv.org/abs/2301.01821" target="_blank">Parameter-Efficient Fine-Tuning Design Spaces</a><br>
+In *Proceedings of the International Conference on Learning Representations* (**ICLR**), 2023<br>
+<a href="https://twitter.com/astonzhangAZ/status/1611400421255557122" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
+<a href="https://github.com/amazon-science/peft-design-spaces" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>
+
+* Z. Liu, Z. Tang, X. Shi, **A. Zhang**, M. Li, A. Shrivastava, and A. Wilson<br>
+<a href="https://arxiv.org/abs/2212.14453" target="_blank">Learning Multimodal Data Augmentation in Feature Space</a><br>
+In *Proceedings of the International Conference on Learning Representations* (**ICLR**), 2023<br>
+
+* T. Yang, Y. Zhu, Y. Xie, **A. Zhang**, C. Chen, and M. Li<br>
+<a href="https://openreview.net/forum?id=CIoSZ_HKHS7" target="_blank">AIM: Adapting Image Models for Efficient Video Understanding</a><br>
+In *Proceedings of the International Conference on Learning Representations* (**ICLR**), 2023<br>
 
@@
 In *ACM SIGKDD Explorations*, 2022<br>
-
-* Z. Liu, Z. Tang, X. Shi, **A. Zhang**, M. Li, A. Shrivastava, and A. Wilson<br>
-<a href="https://arxiv.org/abs/2212.14453" target="_blank">Learning Multimodal Data Augmentation in Feature Space</a><br>
-*"The first augmentation method to be applied to the joint of text, image, and tabular data."*
-In *arXiv*, 2022<br>
 

### 2023-02-03 quarto/index.qmd
update

@@
 
-* Z. Zhang, **A. Zhang**, M. Li, and A. J. Smola<br>
-	<a href="https://arxiv.org/abs/2210.03493" target="_blank">Automatic Chain of Thought Prompting in Large Language Models</a><br>
-	In *Proceedings of the International Conference on Learning Representations* (**ICLR**), 2023<br>
-	<a href="https://twitter.com/astonzhangAZ/status/1579489453789581312" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
-	<a href="https://github.com/amazon-research/auto-cot" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>
+* Z. Zhang, **A. Zhang**, M. Li, H. Zhao, G. Karypis, and A. J. Smola<br>
+	<a href="https://arxiv.org/abs/2302.00923" target="_blank">Multimodal Chain-of-Thought Reasoning in Language Models</a><br>
+	*"SOTA and surpassing human performance on the ScienceQA benchmark."*
+	In *arXiv*, 2023<br>
+	<a href="https://twitter.com/arankomatsuzaki/status/1621323705686134788" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
+	<a href="https://github.com/amazon-science/mm-cot" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>
 
@@
 	<a href="https://github.com/amazon-science/peft-design-spaces" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>
+
+* Z. Zhang, **A. Zhang**, M. Li, and A. J. Smola<br>
+	<a href="https://arxiv.org/abs/2210.03493" target="_blank">Automatic Chain of Thought Prompting in Large Language Models</a><br>
+	In *Proceedings of the International Conference on Learning Representations* (**ICLR**), 2023<br>
+	<a href="https://twitter.com/astonzhangAZ/status/1579489453789581312" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
+	<a href="https://github.com/amazon-research/auto-cot" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>
 
@@
 	*"If your prompt tuning can't converge easily, make it semi-parametric."*
-	In *arXiv*, 2022<br>
+	In *arXiv*, 2023<br>
 	<a href="https://twitter.com/astonzhangAZ/status/1605959819894349824" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>

### 2023-02-03 quarto/papers.qmd
update

@@
 ---
+
+* Z. Zhang, **A. Zhang**, M. Li, H. Zhao, G. Karypis, and A. J. Smola<br>
+	<a href="https://arxiv.org/abs/2302.00923" target="_blank">Multimodal Chain-of-Thought Reasoning in Language Models</a><br>
+	*"SOTA and surpassing human performance on the ScienceQA benchmark."*
+	In *arXiv*, 2023<br>
+	<a href="https://twitter.com/arankomatsuzaki/status/1621323705686134788" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
+	<a href="https://github.com/amazon-science/mm-cot" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>
+
+* J. Chen, **A. Zhang**, X. Shi, M. Li, A. J. Smola, and D. Yang<br>
+<a href="https://arxiv.org/abs/2301.01821" target="_blank">Parameter-Efficient Fine-Tuning Design Spaces</a><br>
+In *Proceedings of the International Conference on Learning Representations* (**ICLR**), 2023<br>
+<a href="https://twitter.com/astonzhangAZ/status/1611400421255557122" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
+<a href="https://github.com/amazon-science/peft-design-spaces" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>
 
@@
 <a href="https://github.com/amazon-research/auto-cot" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>
-
-* J. Chen, **A. Zhang**, X. Shi, M. Li, A. J. Smola, and D. Yang<br>
-<a href="https://arxiv.org/abs/2301.01821" target="_blank">Parameter-Efficient Fine-Tuning Design Spaces</a><br>
-In *Proceedings of the International Conference on Learning Representations* (**ICLR**), 2023<br>
-<a href="https://twitter.com/astonzhangAZ/status/1611400421255557122" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
-<a href="https://github.com/amazon-science/peft-design-spaces" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>
 

### 2023-02-03 quarto/index.qmd
update

@@
 	In *arXiv*, 2023<br>
-	<a href="https://twitter.com/arankomatsuzaki/status/1621323705686134788" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
+	<a href="." title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
 	<a href="https://github.com/amazon-science/mm-cot" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>

### 2023-02-03 quarto/papers.qmd
update

--- 2023-01-20 quarto/papers.qmd
@@
 ---
+
+* Z. Zhang, **A. Zhang**, M. Li, H. Zhao, G. Karypis, and A. J. Smola<br>
+	<a href="https://arxiv.org/abs/2302.00923" target="_blank">Multimodal Chain-of-Thought Reasoning in Language Models</a><br>
+	*"SOTA and surpassing human performance on the ScienceQA benchmark."*
+	In *arXiv*, 2023<br>
+	<a href="." title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
+	<a href="https://github.com/amazon-science/mm-cot" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>
+
+* J. Chen, **A. Zhang**, X. Shi, M. Li, A. J. Smola, and D. Yang<br>
+<a href="https://arxiv.org/abs/2301.01821" target="_blank">Parameter-Efficient Fine-Tuning Design Spaces</a><br>
+In *Proceedings of the International Conference on Learning Representations* (**ICLR**), 2023<br>
+<a href="https://twitter.com/astonzhangAZ/status/1611400421255557122" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
+<a href="https://github.com/amazon-science/peft-design-spaces" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>
 

### 2023-02-03 quarto/index.qmd
update

@@
 	In *arXiv*, 2023<br>
-	<a href="." title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
+	<a href="https://twitter.com/astonzhangAZ/status/1621545166049005568" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
 	<a href="https://github.com/amazon-science/mm-cot" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>

### 2023-02-03 quarto/papers.qmd
update

--- 2023-01-20 quarto/papers.qmd
@@
 ---
+
+* Z. Zhang, **A. Zhang**, M. Li, H. Zhao, G. Karypis, and A. J. Smola<br>
+	<a href="https://arxiv.org/abs/2302.00923" target="_blank">Multimodal Chain-of-Thought Reasoning in Language Models</a><br>
+	*"SOTA and surpassing human performance on the ScienceQA benchmark."*
+	In *arXiv*, 2023<br>
+	<a href="https://twitter.com/astonzhangAZ/status/1621545166049005568" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
+	<a href="https://github.com/amazon-science/mm-cot" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>
+
+* J. Chen, **A. Zhang**, X. Shi, M. Li, A. J. Smola, and D. Yang<br>
+<a href="https://arxiv.org/abs/2301.01821" target="_blank">Parameter-Efficient Fine-Tuning Design Spaces</a><br>
+In *Proceedings of the International Conference on Learning Representations* (**ICLR**), 2023<br>
+<a href="https://twitter.com/astonzhangAZ/status/1611400421255557122" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
+<a href="https://github.com/amazon-science/peft-design-spaces" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>
 

### 2023-02-03 quarto/index.qmd
update

--- 2023-02-03 quarto/index.qmd
@@
 	<a href="https://arxiv.org/abs/2302.00923" target="_blank">Multimodal Chain-of-Thought Reasoning in Language Models</a><br>
-	*"SOTA and surpassing human performance on the ScienceQA benchmark."*
+	*"Imagine reading a book without figures: Multimodal-CoT surpasses humans on ScienceQA."*
 	In *arXiv*, 2023<br>
-	<a href="." title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
+	<a href="https://twitter.com/astonzhangAZ/status/1621545166049005568" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
 	<a href="https://github.com/amazon-science/mm-cot" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>

### 2023-02-03 quarto/index.qmd
update

--- 2023-02-03 quarto/index.qmd
@@
 	<a href="https://arxiv.org/abs/2302.00923" target="_blank">Multimodal Chain-of-Thought Reasoning in Language Models</a><br>
-	*"SOTA and surpassing human performance on the ScienceQA benchmark."*
+	*"Imagine reading a book without figures: Multimodal-CoT surpasses humans on ScienceQA."*
 	In *arXiv*, 2023<br>
-	<a href="." title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
+	[Idea Inspiration](img/mm-cot-idea.png)
+	<a href="https://twitter.com/astonzhangAZ/status/1621545166049005568" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
 	<a href="https://github.com/amazon-science/mm-cot" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>

### 2023-02-04 quarto/index.qmd
update

@@
 
-Hi! I'm happy to connect and discuss.
-My team is hiring intern scientists
-at our <a href="https://www.google.com/maps/place/2795+Augustine+Dr,+Santa+Clara,+CA+95054/@37.3835062,-121.9778599,17z/data=!3m1!4b1!4m5!3m4!1s0x808fc9f208b94da1:0xd2df9ae053c51af0!8m2!3d37.383502!4d-121.9756659" target="_blank">Santa Clara office</a> or other global offices.
+Hi!
+I'm happy to connect and discuss.
+Our office is at <a href="https://www.google.com/maps/place/2795+Augustine+Dr,+Santa+Clara,+CA+95054/@37.3835062,-121.9778599,17z/data=!3m1!4b1!4m5!3m4!1s0x808fc9f208b94da1:0xd2df9ae053c51af0!8m2!3d37.383502!4d-121.9756659" target="_blank">Santa Clara</a> in the San Francisco Bay Area.
 Just email me.
@@
 
-## Ph.D. Interns</a>
-
-* <a href="https://sites.cc.gatech.edu/~jchen896/" target="_blank">Jiaao Chen</a> (2022)
-* <a href="https://bcmi.sjtu.edu.cn/home/zhangzs/" target="_blank">Zhuosheng Zhang</a> (2022)
-* <a href="https://sbmaruf.github.io/" target="_blank">M Saiful Bari</a> (2022)
-* <a href="https://renshuhuai-andy.github.io/" target="_blank">Shuhuai Ren</a> (2022)
-* <a href="https://htwang14.github.io/" target="_blank">Haotao Wang</a> (2021, 2022)
-* <a href="https://shuaizhang.tech/" target="_blank">Shuai Zhang</a> (2019&ndash;2020)
-
 <br>

### 2023-02-05 quarto/index.qmd
update

@@
 	In *arXiv*, 2023<br>
-	[Idea Inspiration](img/mm-cot-idea.png)
+	[[Idea Inspiration]](img/mm-cot-idea.png)
+	[[Reddit Response]](https://www.reddit.com/r/MachineLearning/comments/10svwch/comment/j79i4jj/?utm_source=share&utm_medium=web2x&context=3)
 	<a href="https://twitter.com/astonzhangAZ/status/1621545166049005568" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>

### 2023-02-05 quarto/papers.qmd
update

--- 2023-02-03 quarto/papers.qmd
@@
 	<a href="https://arxiv.org/abs/2302.00923" target="_blank">Multimodal Chain-of-Thought Reasoning in Language Models</a><br>
-	*"SOTA and surpassing human performance on the ScienceQA benchmark."*
+	*"Imagine reading a book without figures: Multimodal-CoT surpasses humans on ScienceQA."*
 	In *arXiv*, 2023<br>
+	[[Idea Inspiration]](img/mm-cot-idea.png)
+	[[Reddit Response]](https://www.reddit.com/r/MachineLearning/comments/10svwch/comment/j79i4jj/?utm_source=share&utm_medium=web2x&context=3)
 	<a href="https://twitter.com/astonzhangAZ/status/1621545166049005568" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>

### 2023-02-06 quarto/index.qmd
update

--- 2023-02-04 quarto/index.qmd
@@
 	In *arXiv*, 2023<br>
-	[Idea Inspiration](img/mm-cot-idea.png)
 	<a href="https://twitter.com/astonzhangAZ/status/1621545166049005568" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
 	<a href="https://github.com/amazon-science/mm-cot" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>
+	[[Idea Inspiration]](img/mm-cot-idea.png)
+	[[Reddit Reply]](https://www.reddit.com/r/MachineLearning/comments/10svwch/comment/j79i4jj/?utm_source=share&utm_medium=web2x&context=3)
 

### 2023-02-06 quarto/papers.qmd
update

--- 2023-02-03 quarto/papers.qmd
@@
 	<a href="https://github.com/amazon-science/mm-cot" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>
+	[[Idea Inspiration]](img/mm-cot-idea.png)
+	[[Reddit Reply]](https://www.reddit.com/r/MachineLearning/comments/10svwch/comment/j79i4jj/?utm_source=share&utm_medium=web2x&context=3)
 

### 2023-02-07 quarto/index.qmd
update

--- 2023-02-04 quarto/index.qmd
@@
 	In *arXiv*, 2023<br>
-	[Idea Inspiration](img/mm-cot-idea.png)
 	<a href="https://twitter.com/astonzhangAZ/status/1621545166049005568" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
 	<a href="https://github.com/amazon-science/mm-cot" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>
+	[[Trending on paperswithcode]](img/mm-cot-trending.png)
+	[[Idea Inspiration]](img/mm-cot-idea.png)
+	[[Reddit Reply]](https://www.reddit.com/r/MachineLearning/comments/10svwch/comment/j79i4jj/?utm_source=share&utm_medium=web2x&context=3)
 

### 2023-02-09 quarto/index.qmd
update

@@
 	*人民邮电出版社*, 2nd ed., 2023, 1st ed., 2019<br>
-	* <a href="https://github.com/d2l-ai/d2l-zh/raw/v1/img/frontpage/jd-190715-en.png" target="_blank">Best seller</a> of new books in "Computers and Internet" at the largest Chinese online bookstore<br>
+	* Best seller of new books in "Computers and Internet" at the largest Chinese online bookstore (both ed.)<br>
 	<iframe src="https://ghbtns.com/github-btn.html?user=d2l-ai&repo=d2l-zh&type=star&count=true" frameborder="0" scrolling="0" width="150" height="30" title="GitHub"></iframe>

### 2023-02-09 quarto/index.qmd
update

@@
 	*人民邮电出版社*, 2nd ed., 2023, 1st ed., 2019<br>
-	* Best seller of new books in "Computers and Internet" at the largest Chinese online bookstore (both ed.)<br>
+	* Best seller (both ed.) of new books in "Computers and Internet" at the largest Chinese online bookstore<br>
 	<iframe src="https://ghbtns.com/github-btn.html?user=d2l-ai&repo=d2l-zh&type=star&count=true" frameborder="0" scrolling="0" width="150" height="30" title="GitHub"></iframe>

### 2023-02-09 quarto/index.qmd
update

@@
 	<a href="https://github.com/amazon-science/mm-cot" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>
-	[[Trending on paperswithcode]](img/mm-cot-trending.png)
+	[[Trending on paperswithcode]](img/mm-cot-trending-social.png)
 	[[Idea Inspiration]](img/mm-cot-idea.png)

### 2023-02-09 quarto/papers.qmd
update

--- 2023-02-06 quarto/papers.qmd
@@
 	<a href="https://github.com/amazon-science/mm-cot" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>
+	[[Trending on paperswithcode]](img/mm-cot-trending-social.png)
 	[[Idea Inspiration]](img/mm-cot-idea.png)

### 2023-02-11 quarto/index.qmd
update

@@
 	* Adopted at 400 universities from 60 countries
-	* Featured in the <a href="https://youtu.be/ue9aumC7AAk?t=6856" target="_blank">AWS re:Invent 2021 keynote</a> by Dr. Swami Sivasubramanian<br>
+	* Featured in the <a href="https://youtu.be/ue9aumC7AAk?t=6856" target="_blank">AWS re:Invent keynote</a> by Swami, Head of AWS AI, Database, and Analytics<br>
 	<iframe src="https://ghbtns.com/github-btn.html?user=d2l-ai&repo=d2l-en&type=star&count=true" frameborder="0" scrolling="0" width="150" height="30" title="GitHub"></iframe>

### 2023-02-11 quarto/index.qmd
update

@@
 	[[Trending on paperswithcode]](img/mm-cot-trending-social.png)
-	[[Idea Inspiration]](img/mm-cot-idea.png)
-	[[Reddit Reply]](https://www.reddit.com/r/MachineLearning/comments/10svwch/comment/j79i4jj/?utm_source=share&utm_medium=web2x&context=3)
+	[[Idea Inspiration by Homeschooling]](img/mm-cot-idea.png)
 

### 2023-02-11 quarto/index.qmd
update

@@
       href: https://twitter.com/astonzhangAZ
+    - icon: file-earmark-person-fill
+      text: CV
+      href: https://www.dropbox.com/s/t2e33tpduom4bk9/CV_Aston_Zhang.pdf?dl=0
     - icon: github
@@
       href: https://github.com/astonzhang
-    - icon: bi-envelope
-      text: Email
-      href: img/email.png
 ---

### 2023-02-11 quarto/papers.qmd
update

--- 2023-02-06 quarto/papers.qmd
@@
 	<a href="https://github.com/amazon-science/mm-cot" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>
-	[[Idea Inspiration]](img/mm-cot-idea.png)
-	[[Reddit Reply]](https://www.reddit.com/r/MachineLearning/comments/10svwch/comment/j79i4jj/?utm_source=share&utm_medium=web2x&context=3)
+	[[Trending on paperswithcode]](img/mm-cot-trending-social.png)
+	[[Idea Inspiration by Homeschooling]](img/mm-cot-idea.png)
 

### 2023-02-13 quarto/index.qmd
update

--- 2023-02-11 quarto/index.qmd
@@
       href: https://twitter.com/astonzhangAZ
+    - icon: file-earmark-person-fill
+      text: CV
+      href: https://www.dropbox.com/s/5k809fym1pc65jp/CV_Aston_Zhang.pdf?dl=0
     - icon: github

### 2023-02-14 quarto/index.qmd
update

--- 2023-02-11 quarto/index.qmd
@@
       href: https://twitter.com/astonzhangAZ
+    - icon: file-earmark-person-fill
+      text: Email
+      href: img/email.png
     - icon: github

### 2023-02-14 quarto/index.qmd
update

@@
 
-* M. S. Bari, **A. Zhang**, S. Zheng, X. Shi, Y. Zhu, S. Joty, and M. Li<br>
-	<a href="https://arxiv.org/abs/2212.10929" target="_blank">
-	SPT: Semi-Parametric Prompt Tuning for Multitask Prompted Learning</a><br>
-	*"If your prompt tuning can't converge easily, make it semi-parametric."*
-	In *arXiv*, 2023<br>
-	<a href="https://twitter.com/astonzhangAZ/status/1605959819894349824" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
-
 * H. Wang, **A. Zhang**, Y. Zhu, S. Zheng, M. Li, A. J. Smola, and Z. Wang<br>

### 2023-02-14 quarto/papers.qmd
update

@@
 In *Proceedings of the International Conference on Learning Representations* (**ICLR**), 2023<br>
-
-* M. S. Bari, **A. Zhang**, S. Zheng, X. Shi, Y. Zhu, S. Joty, and M. Li<br>
-<a href="https://arxiv.org/abs/2212.10929" target="_blank">
-SPT: Semi-Parametric Prompt Tuning for Multitask Prompted Learning</a><br>
-*"If your prompt tuning can't converge easily, make it semi-parametric."*
-In *arXiv*, 2022<br>
-<a href="https://twitter.com/astonzhangAZ/status/1605959819894349824" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
 

### 2023-02-23 quarto/index.qmd
update

@@
 	<a href="https://github.com/amazon-science/mm-cot" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>
-	[[Trending on paperswithcode]](img/mm-cot-trending-social.png)
+	[[Trending on paperswithcode]](img/mm-cot-trending.png)
 	[[Idea Inspiration by Homeschooling]](img/mm-cot-idea.png)

### 2023-02-24 quarto/index.qmd
update

@@
 	<a href="https://github.com/amazon-science/mm-cot" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>
-	[[Trending on paperswithcode]](img/mm-cot-trending.png)
+	[[Top Trending Research on paperswithcode]](img/mm-cot-trending.png)
 	[[Idea Inspiration by Homeschooling]](img/mm-cot-idea.png)
+	[[Reddit]](https://www.reddit.com/r/MachineLearning/comments/10svwch/comment/j79i4jj/?utm_source=share&utm_medium=web2x&context=3)
 

### 2023-02-24 quarto/index.qmd
update

--- 2023-02-23 quarto/index.qmd
@@
 	<a href="https://github.com/amazon-science/mm-cot" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>
-	[[Trending on paperswithcode]](img/mm-cot-trending.png)
+	[[Top Trending Research on paperswithcode]](img/mm-cot-trending.png)
 	[[Idea Inspiration by Homeschooling]](img/mm-cot-idea.png)
+	[[Reddit]](https://www.reddit.com/r/MachineLearning/comments/10svwch/r_multimodal_chainofthought_reasoning_in_language/)
 

### 2023-02-24 quarto/index.qmd
update

--- 2023-02-23 quarto/index.qmd
@@
 	<a href="https://github.com/amazon-science/mm-cot" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>
-	[[Trending on paperswithcode]](img/mm-cot-trending.png)
+	[[Top Trending Research on paperswithcode]](img/mm-cot-trending.png)
 	[[Idea Inspiration by Homeschooling]](img/mm-cot-idea.png)

### 2023-02-24 quarto/index.qmd
update

@@
     - icon: file-earmark-person-fill
-      text: Email
-      href: img/email.png
+      text: CV
+      href: https://www.dropbox.com/s/qba065m7f2hwcjv/CV-Aston-Zhang.pdf?dl=0
     - icon: github

### 2023-02-24 quarto/index.qmd
update

--- 2023-02-24 quarto/index.qmd
@@
     - icon: file-earmark-person-fill
-      text: Email
-      href: img/email.png
+      text: CV
+      href: https://www.dropbox.com/s/ey71hf621x7duho/CV-Aston.pdf?dl=0
     - icon: github

### 2023-03-16 quarto/index.qmd
update

--- 2023-02-24 quarto/index.qmd
@@
     - icon: file-earmark-person-fill
-      text: Email
-      href: img/email.png
-    - icon: github
-      text: GitHub
-      href: https://github.com/astonzhang
+      text: CV
+      href: https://www.dropbox.com/s/ey71hf621x7duho/CV-Aston.pdf?dl=0
 ---

### 2023-03-22 quarto/index.qmd
update

@@
 	<a href="https://github.com/amazon-science/mm-cot" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>
-	[[Top Trending Research on paperswithcode]](img/mm-cot-trending.png)
-	[[Idea Inspiration by Homeschooling]](img/mm-cot-idea.png)
 

### 2023-03-30 quarto/index.qmd
update

@@
       text: CV
-      href: https://www.dropbox.com/s/ey71hf621x7duho/CV-Aston.pdf?dl=0
+      href: https://www.dropbox.com/s/ysgq94ladb5xs1i/CV_Aston.pdf?dl=0
 ---

### 2023-04-10 quarto/papers.qmd
update

@@
 
+* S. Ren, **A. Zhang**, Y. Zhu, S. Zhang, S. Zheng, M. Li, A. J. Smola, X. Sun
+<br>
+<a href="https://arxiv.org" target="_blank">Prompt Pre-Training with Twenty-Thousand Classes for Open-Vocabulary Visual Recognition</a><br>
+*"Scaling up prompt learning on ImageNet-21K achieves SOTA on 21 downstream datasets."*
+In *arXiv*, 2023<br>
+<a href="https://github.com/amazon-science/prompt-pretraining" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>
+
+* J. Chen, **A. Zhang**, M. Li, A. J. Smola, and D. Yang<br>
+<a href="https://arxiv.org" target="_blank">A Cheaper and Better Diffusion Language Model with Soft-Masked Noise</a><br>
+*"Train diffusion language models faster with masks."*
+In *arXiv*, 2023<br>
+<a href="https://github.com/amazon-science/masked-diffusion-lm" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>
+
 * H. Wang, **A. Zhang**, Y. Zhu, S. Zheng, M. Li, A. J. Smola, and Z. Wang<br>
@@
 <a href="https://github.com/amazon-research/normalizer-free-robust-training" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>
+
+* M. S. Bari, **A. Zhang**, S. Zheng, X. Shi, Y. Zhu, S. Joty, and M. Li<br>
+<a href="https://arxiv.org/abs/2212.10929" target="_blank">
+SPT: Semi-Parametric Prompt Tuning for Multitask Prompted Learning</a><br>
+*"If your prompt tuning can't converge easily, make it semi-parametric."*
+In *arXiv*, 2022<br>
+<a href="https://twitter.com/astonzhangAZ/status/1605959819894349824" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
 

### 2023-04-11 quarto/papers.qmd
update

--- 2023-03-22 quarto/papers.qmd
@@
 
+* S. Ren, **A. Zhang**, Y. Zhu, S. Zhang, S. Zheng, M. Li, A. J. Smola, X. Sun
+<br>
+<a href="https://arxiv.org/abs/2304.04704" target="_blank">Prompt Pre-Training with Twenty-Thousand Classes for Open-Vocabulary Visual Recognition</a><br>
+*"Scaling up prompt learning on ImageNet-21K achieves SOTA on 21 downstream datasets."*
+In *arXiv*, 2023<br>
+<a href="https://github.com/amazon-science/prompt-pretraining" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>
+
+* J. Chen, **A. Zhang**, M. Li, A. J. Smola, and D. Yang<br>
+<a href="https://arxiv.org/abs/2304.04746" target="_blank">A Cheaper and Better Diffusion Language Model with Soft-Masked Noise</a><br>
+*"Train diffusion language models faster with masks."*
+In *arXiv*, 2023<br>
+<a href="https://github.com/amazon-science/masked-diffusion-lm" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>
+
 * H. Wang, **A. Zhang**, Y. Zhu, S. Zheng, M. Li, A. J. Smola, and Z. Wang<br>

### 2023-04-20 quarto/index.qmd
update

@@
 	*人民邮电出版社*, 2nd ed., 2023, 1st ed., 2019<br>
-	* Best seller (both ed.) of new books in "Computers and Internet" at the largest Chinese online bookstore<br>
+	* Best seller in China 
+	(<a href="https://raw.githubusercontent.com/d2l-ai/d2l-zh/master/img/frontpage/jd-202302-all-ai-zh-6.png" target="_blank">2023/2</a>, 
+	<a href="https://raw.githubusercontent.com/d2l-ai/d2l-zh/master/img/frontpage/jd-202303-all-ai-zh-6.png" target="_blank">2023/3</a>)<br>
 	<iframe src="https://ghbtns.com/github-btn.html?user=d2l-ai&repo=d2l-zh&type=star&count=true" frameborder="0" scrolling="0" width="150" height="30" title="GitHub"></iframe>

### 2023-05-05 quarto/index.qmd
update

--- 2023-03-30 quarto/index.qmd
@@
 	*人民邮电出版社*, 2nd ed., 2023, 1st ed., 2019<br>
-	* Best seller (both ed.) of new books in "Computers and Internet" at the largest Chinese online bookstore<br>
+	* <a href="https://raw.githubusercontent.com/d2l-ai/d2l-zh/master/img/frontpage/jd-2023020304-all-ai-zh-4.png" target="_blank">Best seller</a> in China 
+	<br>
 	<iframe src="https://ghbtns.com/github-btn.html?user=d2l-ai&repo=d2l-zh&type=star&count=true" frameborder="0" scrolling="0" width="150" height="30" title="GitHub"></iframe>

### 2023-05-16 quarto/index.qmd
update

@@
 	<a href="https://github.com/amazon-science/mm-cot" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>
+	<a href="img/mm-cot-idea.png">[Idea Inspiration by Homeschooling]</a>
 

### 2023-05-16 quarto/index.qmd
update

--- 2023-05-05 quarto/index.qmd
@@
 	<a href="https://github.com/amazon-science/mm-cot" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>
+	<a href="img/mm-cot-idea.png" target="_blank">[Idea Inspiration by Homeschooling]</a>
 

### 2023-05-16 quarto/papers.qmd
update

@@
 <a href="https://github.com/amazon-science/masked-diffusion-lm" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>
+
+* Z. Zeng, C. Hawkins, M. Hong, **A. Zhang**, N. Pappas, V. Singh, and S. Zheng<br>
+<a href="https://arxiv.org/abs/2305.04241" target="_blank">Vcc: Scaling Transformers to 128K Tokens or More by Prioritizing Important Tokens</a><br>
+*"Only a small subset of tokens are relevant to the output."*
+In *arXiv*, 2023<br>
 

### 2023-05-16 quarto/papers.qmd
update

@@
 <a href="https://arxiv.org/abs/2305.04241" target="_blank">Vcc: Scaling Transformers to 128K Tokens or More by Prioritizing Important Tokens</a><br>
-*"Only a small subset of tokens are relevant to the output."*
+*"Only a small subset of tokens are important to the output."*
 In *arXiv*, 2023<br>

### 2023-05-26 quarto/index.qmd
update

@@
 
-**Aston Zhang** is a senior scientist at Amazon Web Services AI Research.
-He studies efficient and robust methods for machine learning and natural language processing, currently focusing on large language models.
+**Aston Zhang** is a scientist at Amazon Web Services AI Research.
+He studies language models and multimodality for AI.
 He received the <a href="https://iclr-conf.medium.com/announcing-iclr-2021-outstanding-paper-awards-9ae0514734ab" target="_blank">ICLR Outstanding Paper Award (2021)</a>,

### 2023-07-07 quarto/index.qmd
update

@@
       href: https://twitter.com/astonzhangAZ
-    - icon: file-earmark-person-fill
-      text: CV
-      href: https://www.dropbox.com/s/ysgq94ladb5xs1i/CV_Aston.pdf?dl=0
+    - icon: github
+      text: GitHub
+      href: https://github.com/astonzhang
 ---

### 2023-08-18 quarto/index.qmd
update

@@
 	*人民邮电出版社*, 2nd ed., 2023, 1st ed., 2019<br>
-	* <a href="https://raw.githubusercontent.com/d2l-ai/d2l-zh/master/img/frontpage/jd-2023020304-all-ai-zh-4.png" target="_blank">Best seller</a> in China 
+	* <a href="https://raw.githubusercontent.com/d2l-ai/d2l-zh/master/static/frontpage/_images/sales/jd-2023020304-all-ai-zh-4.png" target="_blank">Best seller</a> in China 
 	<br>
@@
 
-* Senior Program Committee
-	* *AAAI Conference on Artificial Intelligence* (**AAAI**)
-
-* Journal Editorial Board
-	* *Frontiers in Big Data*
-
 <br>

### 2023-08-29 quarto/index.qmd
update

@@
 
-Hi!
-I'm happy to connect and discuss.
-Our office is at <a href="https://www.google.com/maps/place/2795+Augustine+Dr,+Santa+Clara,+CA+95054/@37.3835062,-121.9778599,17z/data=!3m1!4b1!4m5!3m4!1s0x808fc9f208b94da1:0xd2df9ae053c51af0!8m2!3d37.383502!4d-121.9756659" target="_blank">Santa Clara</a> in the San Francisco Bay Area.
-Just email me.
-
 ## Books
@@
 	<a href="img/mm-cot-idea.png" target="_blank">[Idea Inspiration by Homeschooling]</a>
+
+* C. Qin, **A. Zhang**, Z. Zhang, J. Chen, M. Yasunaga, and D. Yang<br>
+<a href="https://arxiv.org/abs/2302.06476" target="_blank">Is ChatGPT a General-Purpose Natural Language Processing Task Solver?</a><br>
+*"Can ChatGPT solve, for example, sequence tagging?"*
+In *arXiv*, 2023<br>
 

### 2023-08-31 quarto/index.qmd
update

@@
 
-* Area Chair
+* Area Chairs
 	* *Annual Meeting of the Association for Computational Linguistics* (**ACL**)

### 2023-09-22 quarto/index.qmd
update

--- 2023-08-29 quarto/index.qmd
@@
 
+* Z. Zhang and **A. Zhang**<br>
+<a href="https://arxiv.org/abs/2309.11436" target="_blank">You Only Look at Screens: Multimodal Chain-of-Action Agents</a><br>
+*"From screenshots to actions. It takes first principles thinking."*
+In *arXiv*, 2023<br>
+<a href="https://github.com/cooelf/Auto-UI" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>
+
+* S. Ren, **A. Zhang**, Y. Zhu, S. Zhang, S. Zheng, M. Li, A. J. Smola, X. Sun
+<br>
+<a href="https://arxiv.org/abs/2304.04704" target="_blank">Prompt Pre-Training with Twenty-Thousand Classes for Open-Vocabulary Visual Recognition</a><br>
+In *Proceedings of the Conference on Neural Information Processing Systems* (**NeurIPS**), 2023<br>
+<a href="https://github.com/amazon-science/prompt-pretraining" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>
+
+* Z. Zeng, C. Hawkins, M. Hong, **A. Zhang**, N. Pappas, V. Singh, and S. Zheng<br>
+<a href="https://arxiv.org/abs/2305.04241" target="_blank">Scaling Transformers to 128K Tokens or More by Prioritizing Important Tokens</a><br>
+In *Proceedings of the Conference on Neural Information Processing Systems* (**NeurIPS**), 2023<br>
+
 * J. Chen, **A. Zhang**, X. Shi, M. Li, A. J. Smola, and D. Yang<br>
@@
 	<a href="https://github.com/amazon-research/normalizer-free-robust-training" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>
-
-* E. Grassucci, **A. Zhang**, and D. Comminiello<br>
-	<a href="https://arxiv.org/abs/2110.04176" target="_blank">PHNNs: Lightweight Neural Networks via Parameterized Hypercomplex Convolutions</a><br>
-	In *IEEE Transactions on Neural Networks and Learning Systems* (**TNNLS**), 2022<br>
-	<a href="https://github.com/eleGAN23/HyperNets" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>
 

### 2023-09-22 quarto/papers.qmd
update

--- 2023-05-16 quarto/papers.qmd
@@
 	<a href="img/mm-cot-idea.png" target="_blank">[Idea Inspiration by Homeschooling]</a>
+
+* C. Qin, **A. Zhang**, Z. Zhang, J. Chen, M. Yasunaga, and D. Yang<br>
+<a href="https://arxiv.org/abs/2302.06476" target="_blank">Is ChatGPT a General-Purpose Natural Language Processing Task Solver?</a><br>
+*"Can ChatGPT solve, for example, sequence tagging?"*
+In *arXiv*, 2023<br>
+
+* Z. Zhang and **A. Zhang**<br>
+<a href="https://arxiv.org/abs/2309.11436" target="_blank">You Only Look at Screens: Multimodal Chain-of-Action Agents</a><br>
+*"From screenshots to actions. It takes first principles thinking."*
+In *arXiv*, 2023<br>
+<a href="https://github.com/cooelf/Auto-UI" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>
+
+* S. Ren, **A. Zhang**, Y. Zhu, S. Zhang, S. Zheng, M. Li, A. J. Smola, X. Sun
+<br>
+<a href="https://arxiv.org/abs/2304.04704" target="_blank">Prompt Pre-Training with Twenty-Thousand Classes for Open-Vocabulary Visual Recognition</a><br>
+In *Proceedings of the Conference on Neural Information Processing Systems* (**NeurIPS**), 2023<br>
+<a href="https://github.com/amazon-science/prompt-pretraining" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>
+
+* Z. Zeng, C. Hawkins, M. Hong, **A. Zhang**, N. Pappas, V. Singh, and S. Zheng<br>
+<a href="https://arxiv.org/abs/2305.04241" target="_blank">Scaling Transformers to 128K Tokens or More by Prioritizing Important Tokens</a><br>
+In *Proceedings of the Conference on Neural Information Processing Systems* (**NeurIPS**), 2023<br>
 
@@
 
-* S. Ren, **A. Zhang**, Y. Zhu, S. Zhang, S. Zheng, M. Li, A. J. Smola, X. Sun
-<br>
-<a href="https://arxiv.org/abs/2304.04704" target="_blank">Prompt Pre-Training with Twenty-Thousand Classes for Open-Vocabulary Visual Recognition</a><br>
-*"Scaling up prompt learning on ImageNet-21K achieves SOTA on 21 downstream datasets."*
-In *arXiv*, 2023<br>
-<a href="https://github.com/amazon-science/prompt-pretraining" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>
-
 * J. Chen, **A. Zhang**, M. Li, A. J. Smola, and D. Yang<br>
@@
 <a href="https://github.com/amazon-science/masked-diffusion-lm" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>
-
-* Z. Zeng, C. Hawkins, M. Hong, **A. Zhang**, N. Pappas, V. Singh, and S. Zheng<br>
-<a href="https://arxiv.org/abs/2305.04241" target="_blank">Vcc: Scaling Transformers to 128K Tokens or More by Prioritizing Important Tokens</a><br>
-*"Only a small subset of tokens are relevant to the output."*
-In *arXiv*, 2023<br>
 

### 2023-09-22 quarto/index.qmd
update

@@
 	* *Conference on Empirical Methods in Natural Language Processing* (**EMNLP**)
+	* *International Conference on Computational Linguistics* (**COLING**)
 

### 2023-09-22 quarto/index.qmd
update

@@
 	*Cambridge University Press*, 2023<br>
-	* Adopted at 400 universities from 60 countries
+	* Adopted at 500 universities from 70 countries
 	* Featured in the <a href="https://youtu.be/ue9aumC7AAk?t=6856" target="_blank">AWS re:Invent keynote</a> by Swami, Head of AWS AI, Database, and Analytics<br>

### 2023-09-22 quarto/index.qmd
update

@@
 
-**Aston Zhang** is a scientist at Amazon Web Services AI Research.
-He studies language models and multimodality for AI.
-He received the <a href="https://iclr-conf.medium.com/announcing-iclr-2021-outstanding-paper-awards-9ae0514734ab" target="_blank">ICLR Outstanding Paper Award (2021)</a>,
-the ACM Ubicomp Distinguished Paper Award (2018), and the ACM SenSys Best Paper Award Nomination (2017).
+**Aston Zhang** is a research scientist at Meta Generative AI, desining and training large models.
+Previously, he studied language models and multimodality for AI at Amazon Web Services AI Research.
+He received an <a href="https://iclr-conf.medium.com/announcing-iclr-2021-outstanding-paper-awards-9ae0514734ab" target="_blank">ICLR Outstanding Paper Award</a>,
+an ACM Ubicomp Distinguished Paper Award, and an ACM SenSys Best Paper Award Nomination.
 His <a href="https://github.com/d2l-ai" target="_blank">open-source</a> textbook,

### 2023-09-22 quarto/index.qmd
update

@@
 
-**Aston Zhang** is a research scientist at Meta Generative AI, desining and training large models.
+**Aston Zhang** is a research scientist at Meta Generative AI, designing and training large models.
 Previously, he studied language models and multimodality for AI at Amazon Web Services AI Research.
@@
 <a href="https://arxiv.org/abs/2309.11436" target="_blank">You Only Look at Screens: Multimodal Chain-of-Action Agents</a><br>
-*"From screenshots to actions. It takes first principles thinking."*
+*"Perform a task on smart phones? Train an agent using screenshots."*
 In *arXiv*, 2023<br>

### 2023-09-23 quarto/index.qmd
update

@@
 
-**Aston Zhang** is a research scientist at Meta Generative AI, designing and training large models.
-Previously, he studied language models and multimodality for AI at Amazon Web Services AI Research.
+**Aston Zhang** is a research scientist at Meta Generative AI, building large language models.
+Previously, he was a scientist at Amazon Web Services AI Research.
 He received an <a href="https://iclr-conf.medium.com/announcing-iclr-2021-outstanding-paper-awards-9ae0514734ab" target="_blank">ICLR Outstanding Paper Award</a>,
@@
 In *arXiv*, 2023<br>
+<a href="https://twitter.com/astonzhangAZ/status/1705235421280797111" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
 <a href="https://github.com/cooelf/Auto-UI" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>

### 2023-09-23 quarto/index.qmd
update

@@
 **Aston Zhang** is a research scientist at Meta Generative AI, building large language models.
-Previously, he was a scientist at Amazon Web Services AI Research.
+Prior to this, he was a scientist/manager at Amazon Web Services AI Research,
+studying language and multimodal models.
 He received an <a href="https://iclr-conf.medium.com/announcing-iclr-2021-outstanding-paper-awards-9ae0514734ab" target="_blank">ICLR Outstanding Paper Award</a>,
 an ACM Ubicomp Distinguished Paper Award, and an ACM SenSys Best Paper Award Nomination.
-His <a href="https://github.com/d2l-ai" target="_blank">open-source</a> textbook,
-<a href="https://d2l.ai" target="_blank">Dive into Deep Learning</a>,
-has been <a href="https://d2l.ai/_images/map.png" target="_blank">adopted worldwide</a>.
-He obtained his Ph.D. in Computer Science from University of Illinois at Urbana-Champaign.
+His <a href="https://d2l.ai" target="_blank">Dive into Deep Learning</a> textbook
+is <a href="https://d2l.ai/_images/map.png" target="_blank">adopted worldwide</a>.
+He obtained a Ph.D. in Computer Scientist from University of Illinois Urbana-Champaign.
 

### 2023-09-23 quarto/index.qmd
update

@@
 is <a href="https://d2l.ai/_images/map.png" target="_blank">adopted worldwide</a>.
-He obtained a Ph.D. in Computer Scientist from University of Illinois Urbana-Champaign.
+He obtained a Ph.D. in Computer Science from University of Illinois Urbana-Champaign.
 
@@
 	*Cambridge University Press*, 2023<br>
-	* Adopted at 500 universities from 70 countries
+	* Adopted at 500 universities from 70 countries (on <a href="https://www.amazon.com/Dive-into-Learning-Aston-Zhang/dp/1009389432" target="_blank">Amazon</a>)
 	* Featured in the <a href="https://youtu.be/ue9aumC7AAk?t=6856" target="_blank">AWS re:Invent keynote</a> by Swami, Head of AWS AI, Database, and Analytics<br>

### 2023-10-07 quarto/index.qmd
update

@@
 
+* Z. Zhang and **A. Zhang**<br>
+<a href="https://arxiv.org/abs/2309.11436" target="_blank">You Only Look at Screens: Multimodal Chain-of-Action Agents</a><br>
+*"Perform a task on smart phones? Train an agent using screenshots."*
+In *arXiv*, 2023<br>
+<a href="https://twitter.com/astonzhangAZ/status/1705235421280797111" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
+<a href="https://github.com/cooelf/Auto-UI" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>
+
 * Z. Zhang, **A. Zhang**, M. Li, H. Zhao, G. Karypis, and A. J. Smola<br>
@@
 	<a href="img/mm-cot-idea.png" target="_blank">[Idea Inspiration by Homeschooling]</a>
-
-* C. Qin, **A. Zhang**, Z. Zhang, J. Chen, M. Yasunaga, and D. Yang<br>
-<a href="https://arxiv.org/abs/2302.06476" target="_blank">Is ChatGPT a General-Purpose Natural Language Processing Task Solver?</a><br>
-*"Can ChatGPT solve, for example, sequence tagging?"*
-In *arXiv*, 2023<br>
-
-* Z. Zhang and **A. Zhang**<br>
-<a href="https://arxiv.org/abs/2309.11436" target="_blank">You Only Look at Screens: Multimodal Chain-of-Action Agents</a><br>
-*"Perform a task on smart phones? Train an agent using screenshots."*
-In *arXiv*, 2023<br>
-<a href="https://twitter.com/astonzhangAZ/status/1705235421280797111" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
-<a href="https://github.com/cooelf/Auto-UI" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>
 
@@
 	In *Proceedings of the International Conference on Learning Representations* (**ICLR**), 2023<br>
+
+* C. Qin, **A. Zhang**, Z. Zhang, J. Chen, M. Yasunaga, and D. Yang<br>
+<a href="https://arxiv.org/abs/2302.06476" target="_blank">Is ChatGPT a General-Purpose Natural Language Processing Task Solver?</a><br>
+In *Empirical Methods in Natural Language Processing* (**EMNLP**), 2023<br>
+
+* J. Chen, **A. Zhang**, D. Yang, M. Li, and A. J. Smola<br>
+<a href="https://arxiv.org/abs/2304.04746" target="_blank">A Cheaper and Better Diffusion Language Model with Soft-Masked Noise</a><br>
+In *Empirical Methods in Natural Language Processing* (**EMNLP**), 2023<br>
+<a href="https://github.com/amazon-science/masked-diffusion-lm" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>
 

### 2023-10-07 quarto/papers.qmd
update

@@
 ---
+
+* Z. Zhang and **A. Zhang**<br>
+<a href="https://arxiv.org/abs/2309.11436" target="_blank">You Only Look at Screens: Multimodal Chain-of-Action Agents</a><br>
+*"Perform a task on smart phones? Train an agent using screenshots."*
+In *arXiv*, 2023<br>
+<a href="https://twitter.com/astonzhangAZ/status/1705235421280797111" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
+<a href="https://github.com/cooelf/Auto-UI" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>
 
@@
 
-* J. Chen, **A. Zhang**, M. Li, A. J. Smola, and D. Yang<br>
+* C. Qin, **A. Zhang**, Z. Zhang, J. Chen, M. Yasunaga, and D. Yang<br>
+<a href="https://arxiv.org/abs/2302.06476" target="_blank">Is ChatGPT a General-Purpose Natural Language Processing Task Solver?</a><br>
+In *Empirical Methods in Natural Language Processing* (**EMNLP**), 2023<br>
+
+* J. Chen, **A. Zhang**, D. Yang, M. Li, and A. J. Smola<br>
 <a href="https://arxiv.org/abs/2304.04746" target="_blank">A Cheaper and Better Diffusion Language Model with Soft-Masked Noise</a><br>
-*"Train diffusion language models faster with masks."*
-In *arXiv*, 2023<br>
+In *Empirical Methods in Natural Language Processing* (**EMNLP**), 2023<br>
 <a href="https://github.com/amazon-science/masked-diffusion-lm" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>
+
+* R. Aly, X. Shi, K. Lin, **A. Zhang**, and A. G. Wilson<br>
+<a href="https://arxiv.org/abs/2305.12576" target="_blank">Automated Few-Shot Learning with Instruction-Finetuned Language Models</a><br>
+In *Findings of Empirical Methods in Natural Language Processing* (**EMNLP**), 2023<br>
 
@@
 **Poison Attacks against Text Datasets with Conditional Adversarially Regularized Autoencoder**<br>
-In *Findings of Empirical Methods in Natural Language Processing* (**EMNLP-Findings**), 2020
+In *Findings of Empirical Methods in Natural Language Processing* (**EMNLP**), 2020
 

### 2023-10-17 quarto/index.qmd
update

@@
       href: https://github.com/astonzhang
+    - icon: google
+      text: Scholar
+      href: https://scholar.google.com/citations?user=WXOaxKMAAAAJ
 ---

### 2023-11-29 quarto/index.qmd
update

@@
 :::
+
+*<FONT COLOR="#ff0000">I'm hiring</FONT> one Ph.D.
+research intern at the large language model (Llama) team of Meta GenAI.
+If you are interested in LLM pre-training and fine-tuning research, just email me (you'll be working with <a href="https://scholar.google.co.uk/citations?user=SnQnQicAAAAJ&hl=en" target="_blank">Mike</a> and me).*
 

### 2023-11-29 quarto/index.qmd
update

--- 2023-10-07 quarto/index.qmd
@@
     - icon: twitter
-      text: Twitter
       href: https://twitter.com/astonzhangAZ
+    - icon: bi-envelope
+      href: img/email.png
     - icon: github
-      text: GitHub
       href: https://github.com/astonzhang
+    - icon: google
+      href: https://scholar.google.com/citations?user=WXOaxKMAAAAJ
 ---
@@
 :::
+
+*<FONT COLOR="#ff0000">I'm hiring</FONT> one Ph.D.
+research intern at the large language model (Llama) team of Meta GenAI.
+If you are interested in LLM pre-training and fine-tuning research in 2024, just <a href="img/email.png" target="_blank">email me</a>.*
 

### 2023-11-29 quarto/index.qmd
update

@@
 research intern at the large language model (Llama) team of Meta GenAI.
-If you are interested in LLM pre-training and fine-tuning research in 2024, just <a href="img/email.png" target="_blank">email me</a>.*
+If you are interested in LLM pre-training and fine-tuning research, just <a href="img/email.png" target="_blank">email me</a>.
+You'll be working with <a href="https://scholar.google.com/citations?user=SnQnQicAAAAJ" target="_blank">Mike Lewis</a> and me in 2024.*
 

### 2023-11-29 quarto/index.qmd
update

@@
       href: https://scholar.google.com/citations?user=WXOaxKMAAAAJ
+    - icon: linkedin
+      href: www.linkedin.com/in/astonzhang
+
 ---

### 2023-11-29 quarto/index.qmd
update

--- 2023-11-29 quarto/index.qmd
@@
       href: https://scholar.google.com/citations?user=WXOaxKMAAAAJ
+    - icon: linkedin
+      href: https://linkedin.com/in/astonzhang
+
 ---

### 2023-11-30 quarto/index.qmd
update

@@
 
-**Aston Zhang** is a research scientist at Meta Generative AI, building large language models.
+**Aston Zhang** is a research scientist at Meta Generative AI, building large language models (Llama).
 Prior to this, he was a scientist/manager at Amazon Web Services AI Research,
@@
 
-*<FONT COLOR="#ff0000">I'm hiring</FONT> one Ph.D.
-research intern at the large language model (Llama) team of Meta GenAI.
-If you are interested in LLM pre-training and fine-tuning research, just <a href="img/email.png" target="_blank">email me</a>.
-You'll be working with <a href="https://scholar.google.com/citations?user=SnQnQicAAAAJ" target="_blank">Mike Lewis</a> and me in 2024.*
+*If you are interested in research internship on large language models at the Llama team in 2024, just <a href="img/email.png" target="_blank">email me</a>.*
 

### 2023-11-30 quarto/index.qmd
update

@@
 
-*If you are interested in research internship on large language models at the Llama team in 2024, just <a href="img/email.png" target="_blank">email me</a>.*
+*If you are interested in <font color="#ff0000">research internship</font> on large language models at the Llama team in 2024, just <a href="img/email.png" target="_blank">email me</a>.*
 

### 2023-11-30 quarto/index.qmd
update

--- 2023-11-30 quarto/index.qmd
@@
 
-*If you are interested in research internship on large language models at the Llama team in 2024, just <a href="img/email.png" target="_blank">email me</a>.*
+*If you are interested in <font color="#ff0000">research internship</font> on large language models at the Llama team in 2024, feel free to <a href="img/email.png" target="_blank">email me</a>.*
 

### 2023-11-30 quarto/index.qmd
update

@@
       href: https://scholar.google.com/citations?user=WXOaxKMAAAAJ
-    - icon: linkedin
-      href: https://linkedin.com/in/astonzhang
 

### 2023-11-30 quarto/index.qmd
update

@@
 
-*If you are interested in <font color="#ff0000">research internship</font> on large language models at the Llama team in 2024, feel free to <a href="img/email.png" target="_blank">email me</a>.*
+*If you are interested in <font color="#ff0000">research internship</font> on large language models with our team in 2024, feel free to <a href="img/email.png" target="_blank">email me</a>.*
 

### 2023-12-05 quarto/index.qmd
update

@@
 
-*If you are interested in <font color="#ff0000">research internship</font> on large language models with our team in 2024, feel free to <a href="img/email.png" target="_blank">email me</a>.*
+*If you are interested in <a href="https://twitter.com/astonzhangAZ/status/1731698624902402281" target="_blank">research internship</a> on large language models with our team in 2024, feel free to <a href="img/email.png" target="_blank">email me</a>.*
 

### 2023-12-15 quarto/index.qmd
update

@@
 	*Cambridge University Press*, 2023<br>
-	* Adopted at 500 universities from 70 countries (on <a href="https://www.amazon.com/Dive-into-Learning-Aston-Zhang/dp/1009389432" target="_blank">Amazon</a>)
+	* Adopted at 500 universities from 70 countries
 	* Featured in the <a href="https://youtu.be/ue9aumC7AAk?t=6856" target="_blank">AWS re:Invent keynote</a> by Swami, Head of AWS AI, Database, and Analytics<br>

### 2024-01-18 quarto/index.qmd
update

@@
 
-*If you are interested in <a href="https://twitter.com/astonzhangAZ/status/1731698624902402281" target="_blank">research internship</a> on large language models with our team in 2024, feel free to <a href="img/email.png" target="_blank">email me</a>.*
+[Filled, see you next year] *If you are interested in <a href="https://twitter.com/astonzhangAZ/status/1731698624902402281" target="_blank">research internship</a> on LLMs with our team in 2024, just <a href="img/email.png" target="_blank">email me</a>.*
 

### 2024-02-16 quarto/index.qmd
update

@@
       href: https://scholar.google.com/citations?user=WXOaxKMAAAAJ
-
+    - icon: linkedin
+      href: https://www.linkedin.com/in/astonzhang/
 ---

### 2024-04-14 quarto/index.qmd
update

@@
 
-**Aston Zhang** is a research scientist at Meta Generative AI, building large language models (Llama).
-Prior to this, he was a scientist/manager at Amazon Web Services AI Research,
-studying language and multimodal models.
+**Aston Zhang** is a research scientist at the <a href="https://llama.meta.com/" target="_blank">Llama</a> team of Meta Generative AI, building large language models.
+Prior to this, he was a scientist/manager at Amazon Web Services AI Research.
 He received an <a href="https://iclr-conf.medium.com/announcing-iclr-2021-outstanding-paper-awards-9ae0514734ab" target="_blank">ICLR Outstanding Paper Award</a>,
@@
 
-[Filled, see you next year] *If you are interested in <a href="https://twitter.com/astonzhangAZ/status/1731698624902402281" target="_blank">research internship</a> on LLMs with our team in 2024, just <a href="img/email.png" target="_blank">email me</a>.*
+##### News
+
+* *If you're interested in <a href="https://twitter.com/astonzhangAZ/status/1731698624902402281" target="_blank">research internship</a> with our team in 2024, just <a href="img/email.png" target="_blank">email me</a>.* [Filled, see you next year]
 

### 2024-04-20 quarto/index.qmd
update

--- 2024-02-16 quarto/index.qmd
@@
 
-**Aston Zhang** is a research scientist at Meta Generative AI, building large language models (Llama).
-Prior to this, he was a scientist/manager at Amazon Web Services AI Research,
-studying language and multimodal models.
+**Aston Zhang** is a research scientist at the <a href="https://llama.meta.com/" target="_blank">Llama</a> team of Meta Generative AI, building <a href="https://ai.meta.com/blog/meta-llama-3/" target="_blank">Llama 3</a>.
+Prior to this, he was a scientist/manager at AWS AI Research.
 He received an <a href="https://iclr-conf.medium.com/announcing-iclr-2021-outstanding-paper-awards-9ae0514734ab" target="_blank">ICLR Outstanding Paper Award</a>,
@@
 
-[Filled, see you next year] *If you are interested in <a href="https://twitter.com/astonzhangAZ/status/1731698624902402281" target="_blank">research internship</a> on LLMs with our team in 2024, just <a href="img/email.png" target="_blank">email me</a>.*
+##### News
+
+* Meet <a href="https://ai.meta.com/blog/meta-llama-3/" target="_blank">Llama 3</a>, our state-of-the-art open source large language model.
+<a href="https://x.com/astonzhangAZ/status/1780990210576441844" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
+* *If you're interested in <a href="https://twitter.com/astonzhangAZ/status/1731698624902402281" target="_blank">research internship</a> with our team in 2024, just <a href="img/email.png" target="_blank">email me</a>.* [Filled, see you next year]
 

### 2024-04-20 quarto/index.qmd
update

@@
 <a href="https://x.com/astonzhangAZ/status/1780990210576441844" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
-* *If you're interested in <a href="https://twitter.com/astonzhangAZ/status/1731698624902402281" target="_blank">research internship</a> with our team in 2024, just <a href="img/email.png" target="_blank">email me</a>.* [Filled, see you next year]
+* If you're interested in <a href="https://twitter.com/astonzhangAZ/status/1731698624902402281" target="_blank">research internship</a> with our team in 2024, just <a href="img/email.png" target="_blank">email me</a>.
+[Filled, see you next year]
 

### 2024-04-20 quarto/index.qmd
update

@@
 
-##### News
+## News
 
@@
 <a href="https://x.com/astonzhangAZ/status/1780990210576441844" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
-* If you're interested in <a href="https://twitter.com/astonzhangAZ/status/1731698624902402281" target="_blank">research internship</a> with our team in 2024, just <a href="img/email.png" target="_blank">email me</a>.
-[Filled, see you next year]
+* Join us for a 2024 research internship (filled, see you next time).
+<a href="https://twitter.com/astonzhangAZ/status/1731698624902402281" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
 

### 2024-05-10 quarto/index.qmd
update

@@
 	<a href="https://arxiv.org/abs/2302.00923" target="_blank">Multimodal Chain-of-Thought Reasoning in Language Models</a><br>
-	*"Imagine reading a book without figures: Multimodal-CoT surpasses humans on ScienceQA."*
-	In *arXiv*, 2023<br>
+	In *Transactions on Machine Learning Research*, 2023<br>
 	<a href="https://twitter.com/astonzhangAZ/status/1621545166049005568" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>

### 2024-06-29 quarto/index.qmd
update

@@
 * Meet <a href="https://ai.meta.com/blog/meta-llama-3/" target="_blank">Llama 3</a>, our state-of-the-art open source large language model.
-<a href="https://x.com/astonzhangAZ/status/1780990210576441844" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
+<a href="https://x.com/astonzhangAZ/status/1780990210576441844" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a> (my *Llama for Developers* <a href="https://www.youtube.com/watch?v=Tmdk_H2WDj4&ab_channel=AIatMeta" target="_blank">podcast</a>)
 * Join us for a 2024 research internship (filled, see you next time).

### 2024-06-29 quarto/index.qmd
update

--- 2024-05-10 quarto/index.qmd
@@
 * Meet <a href="https://ai.meta.com/blog/meta-llama-3/" target="_blank">Llama 3</a>, our state-of-the-art open source large language model.
-<a href="https://x.com/astonzhangAZ/status/1780990210576441844" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
+<a href="https://x.com/astonzhangAZ/status/1780990210576441844" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a> (my *Llama for Developers* <a href="https://x.com/AIatMeta/status/1806757387677897206" target="_blank">podcast</a>)
 * Join us for a 2024 research internship (filled, see you next time).

### 2024-07-18 quarto/index.qmd
update

@@
 
-**Aston Zhang** is a research scientist at the <a href="https://llama.meta.com/" target="_blank">Llama</a> team of Meta Generative AI, building <a href="https://ai.meta.com/blog/meta-llama-3/" target="_blank">Llama 3</a>.
-Prior to this, he was a scientist/manager at AWS AI Research.
-He received an <a href="https://iclr-conf.medium.com/announcing-iclr-2021-outstanding-paper-awards-9ae0514734ab" target="_blank">ICLR Outstanding Paper Award</a>,
-an ACM Ubicomp Distinguished Paper Award, and an ACM SenSys Best Paper Award Nomination.
-His <a href="https://d2l.ai" target="_blank">Dive into Deep Learning</a> textbook
+**Aston Zhang** is a research scientist on the <a href="https://llama.meta.com/" target="_blank">Llama</a> team at Meta Generative AI and a core contributor to <a href="https://ai.meta.com/blog/meta-llama-3/" target="_blank">Llama 3</a>.
+Previously, he served as a scientist and manager at AWS AI Research.
+His accolades include the <a href="https://iclr-conf.medium.com/announcing-iclr-2021-outstanding-paper-awards-9ae0514734ab" target="_blank">ICLR Outstanding Paper Award</a>,
+the ACM Ubicomp Distinguished Paper Award,
+and an ACM SenSys Best Paper Award nomination.
+His textbook, "<a href="https://d2l.ai" target="_blank">Dive into Deep Learning</a>," 
 is <a href="https://d2l.ai/_images/map.png" target="_blank">adopted worldwide</a>.
-He obtained a Ph.D. in Computer Science from University of Illinois Urbana-Champaign.
+He holds a Ph.D. in Computer Science from the University of Illinois Urbana-Champaign.
 

### 2024-07-23 quarto/index.qmd
update

@@
 
+* <a href="https://ai.meta.com/blog/meta-llama-3-1/" target="_blank">Llama 3.1 405B</a> is now openly available.
+<a href="https://x.com/astonzhangAZ/status/1815763885380747422" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
 * Meet <a href="https://ai.meta.com/blog/meta-llama-3/" target="_blank">Llama 3</a>, our state-of-the-art open source large language model.
@@
 ## Papers ([All](papers.qmd))
+
+* Llama Team, AI@Meta (**Core Contributor**)<br>
+<a href="https://scontent-sjc3-1.xx.fbcdn.net/v/t39.2365-6/452256780_3788187148167392_9020150332553839453_n.pdf?_nc_cat=103&ccb=1-7&_nc_sid=3c67a6&_nc_ohc=XG3_BvYG0wwQ7kNvgGBgyGR&_nc_ht=scontent-sjc3-1.xx&oh=00_AYDGOU8907donbx_n2EYOzFU-h4VJxtA_EjJbiFVm7qnaA&oe=66A5A0DC" target="_blank">The Llama 3 Herd of Models</a><br>
+2024<br>
+<a href="https://x.com/astonzhangAZ/status/1815763885380747422" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
+<a href="https://github.com/meta-llama/llama-models" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>
 

### 2024-07-23 quarto/index.qmd
update

@@
 * <a href="https://ai.meta.com/blog/meta-llama-3-1/" target="_blank">Llama 3.1 405B</a> is now openly available.
-<a href="https://x.com/astonzhangAZ/status/1815763885380747422" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
+<a href="https://x.com/astonzhangAZ/status/1815763885380747422" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a> (Mark Zuckerberg on <a href="https://x.com/rowancheung/status/1815763595197616155" target="_blank">Llama 3 and beyond</a>)
 * Meet <a href="https://ai.meta.com/blog/meta-llama-3/" target="_blank">Llama 3</a>, our state-of-the-art open source large language model.

### 2024-07-24 quarto/index.qmd
update

--- 2024-07-23 quarto/index.qmd
@@
 * <a href="https://ai.meta.com/blog/meta-llama-3-1/" target="_blank">Llama 3.1 405B</a> is now openly available.
+See Mark's thoughts on <a href="https://x.com/rowancheung/status/1815763595197616155" target="_blank">Llama 3 and beyond</a>.
 <a href="https://x.com/astonzhangAZ/status/1815763885380747422" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
 * Meet <a href="https://ai.meta.com/blog/meta-llama-3/" target="_blank">Llama 3</a>, our state-of-the-art open source large language model.
-<a href="https://x.com/astonzhangAZ/status/1780990210576441844" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a> (my *Llama for Developers* <a href="https://x.com/AIatMeta/status/1806757387677897206" target="_blank">podcast</a>)
+See my <a href="https://x.com/AIatMeta/status/1806757387677897206" target="_blank">podcast</a> for developers.
+<a href="https://x.com/astonzhangAZ/status/1780990210576441844" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
 * Join us for a 2024 research internship (filled, see you next time).

### 2024-07-24 quarto/papers.qmd
update

@@
 ---
+
+* Llama Team, AI@Meta (**Core Contributor**)<br>
+<a href="https://scontent-sjc3-1.xx.fbcdn.net/v/t39.2365-6/452256780_3788187148167392_9020150332553839453_n.pdf?_nc_cat=103&ccb=1-7&_nc_sid=3c67a6&_nc_ohc=XG3_BvYG0wwQ7kNvgGBgyGR&_nc_ht=scontent-sjc3-1.xx&oh=00_AYDGOU8907donbx_n2EYOzFU-h4VJxtA_EjJbiFVm7qnaA&oe=66A5A0DC" target="_blank">The Llama 3 Herd of Models</a><br>
+2024<br>
+<a href="https://x.com/astonzhangAZ/status/1815763885380747422" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
+<a href="https://github.com/meta-llama/llama-models" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>
 

### 2024-07-24 quarto/index.qmd
update

@@
 * <a href="https://ai.meta.com/blog/meta-llama-3-1/" target="_blank">Llama 3.1 405B</a> is now openly available.
-See Mark's thoughts on <a href="https://x.com/rowancheung/status/1815763595197616155" target="_blank">Llama 3 and beyond</a>.
+Check out <a href="https://x.com/rowancheung/status/1815763595197616155" target="_blank">Mark's insights</a> on Llama 3 and beyond.
 <a href="https://x.com/astonzhangAZ/status/1815763885380747422" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
 * Meet <a href="https://ai.meta.com/blog/meta-llama-3/" target="_blank">Llama 3</a>, our state-of-the-art open source large language model.
-See my <a href="https://x.com/AIatMeta/status/1806757387677897206" target="_blank">podcast</a> for developers.
+Check out <a href="https://x.com/AIatMeta/status/1806757387677897206" target="_blank">my developer podcast</a>.
 <a href="https://x.com/astonzhangAZ/status/1780990210576441844" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>

### 2024-07-27 quarto/index.qmd
update

@@
 * <a href="https://ai.meta.com/blog/meta-llama-3-1/" target="_blank">Llama 3.1 405B</a> is now openly available.
-Check out <a href="https://x.com/rowancheung/status/1815763595197616155" target="_blank">Mark's insights</a> on Llama 3 and beyond.
+Explore <a href="https://x.com/rowancheung/status/1815763595197616155" target="_blank">Mark's insights</a> on Llama 3 and beyond.
 <a href="https://x.com/astonzhangAZ/status/1815763885380747422" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
@@
 * Llama Team, AI@Meta (**Core Contributor**)<br>
-<a href="https://scontent-sjc3-1.xx.fbcdn.net/v/t39.2365-6/452256780_3788187148167392_9020150332553839453_n.pdf?_nc_cat=103&ccb=1-7&_nc_sid=3c67a6&_nc_ohc=XG3_BvYG0wwQ7kNvgGBgyGR&_nc_ht=scontent-sjc3-1.xx&oh=00_AYDGOU8907donbx_n2EYOzFU-h4VJxtA_EjJbiFVm7qnaA&oe=66A5A0DC" target="_blank">The Llama 3 Herd of Models</a><br>
+<a href="https://ai.meta.com/research/publications/the-llama-3-herd-of-models/" target="_blank">The Llama 3 Herd of Models</a><br>
 2024<br>

### 2024-09-30 quarto/index.qmd
update

@@
 
+* Join us for a 2025 research internship! I'm hiring early this year so just email me.
 * <a href="https://ai.meta.com/blog/meta-llama-3-1/" target="_blank">Llama 3.1 405B</a> is now openly available.
-Explore <a href="https://x.com/rowancheung/status/1815763595197616155" target="_blank">Mark's insights</a> on Llama 3 and beyond.
 <a href="https://x.com/astonzhangAZ/status/1815763885380747422" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
@@
 <a href="https://x.com/astonzhangAZ/status/1780990210576441844" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
-* Join us for a 2024 research internship (filled, see you next time).
-<a href="https://twitter.com/astonzhangAZ/status/1731698624902402281" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
 

### 2024-10-01 quarto/index.qmd
update

@@
 ## Papers ([All](papers.qmd))
+
+* M.
+Zhong\*, **A.
+Zhang**\*, X.
+Wang, R.
+Hou, W.
+Xiong, C.
+Zhu, Z.
+Chen, L.
+Tan, C.
+Bi, M.
+Lewis, S.
+Popuri, S.
+Narang, M.
+Kambadur, D.
+Mahajan, S.
+Edunov, J.
+Han, and L.
+van der Maaten (\*Equal contribution)<br>
+<a href="https://arxiv.org/abs/2409.19951" target="_blank">Law of the Weakest Link: Cross Capabilities of Large Language Models</a><br>
+*"Cross-capability performance is limited by the weakest underlying capability."*
+In *arXiv*, 2024<br>
+<a href="https://twitter.com/astonzhangAZ/" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
+<a href="https://github.com/facebookresearch/llm-cross-capabilities" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>
+<a href="https://www.llm-cross-capabilities.org" target="_blank">llm-cross-capabilities.org</a>
 

### 2024-10-01 quarto/papers.qmd
update

@@
 ---
+
+* M.
+Zhong\*, **A.
+Zhang**\*, X.
+Wang, R.
+Hou, W.
+Xiong, C.
+Zhu, Z.
+Chen, L.
+Tan, C.
+Bi, M.
+Lewis, S.
+Popuri, S.
+Narang, M.
+Kambadur, D.
+Mahajan, S.
+Edunov, J.
+Han, and L.
+van der Maaten (\*Equal contribution)<br>
+<a href="https://arxiv.org/abs/2409.19951" target="_blank">Law of the Weakest Link: Cross Capabilities of Large Language Models</a><br>
+*"Cross-capability performance is limited by the weakest underlying capability."*
+In *arXiv*, 2024<br>
+<a href="https://twitter.com/astonzhangAZ/" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
+<a href="https://github.com/facebookresearch/llm-cross-capabilities" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>
+<a href="https://www.llm-cross-capabilities.org" target="_blank">llm-cross-capabilities.org</a>
 

### 2024-10-01 quarto/index.qmd
update

--- 2024-09-30 quarto/index.qmd
@@
 ## Papers ([All](papers.qmd))
+
+* M.
+Zhong\*, **A.
+Zhang**\*, X.
+Wang, R.
+Hou, W.
+Xiong, C.
+Zhu, Z.
+Chen, L.
+Tan, C.
+Bi, M.
+Lewis, S.
+Popuri, S.
+Narang, M.
+Kambadur, D.
+Mahajan, S.
+Edunov, J.
+Han, and L.
+van der Maaten (\*Equal contribution)<br>
+<a href="https://arxiv.org/abs/2409.19951" target="_blank">Law of the Weakest Link: Cross Capabilities of Large Language Models</a><br>
+*"Cross-capability performance is limited by the weakest underlying capability."*
+In *arXiv*, 2024<br>
+<a href="https://x.com/astonzhangAZ/status/1841131443420008918" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
+<a href="https://github.com/facebookresearch/llm-cross-capabilities" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>
+<a href="https://www.llm-cross-capabilities.org" target="_blank">llm-cross-capabilities.org</a>
 

### 2024-10-01 quarto/papers.qmd
update

--- 2024-07-27 quarto/papers.qmd
@@
 ---
+
+* M.
+Zhong\*, **A.
+Zhang**\*, X.
+Wang, R.
+Hou, W.
+Xiong, C.
+Zhu, Z.
+Chen, L.
+Tan, C.
+Bi, M.
+Lewis, S.
+Popuri, S.
+Narang, M.
+Kambadur, D.
+Mahajan, S.
+Edunov, J.
+Han, and L.
+van der Maaten (\*Equal contribution)<br>
+<a href="https://arxiv.org/abs/2409.19951" target="_blank">Law of the Weakest Link: Cross Capabilities of Large Language Models</a><br>
+*"Cross-capability performance is limited by the weakest underlying capability."*
+In *arXiv*, 2024<br>
+<a href="https://x.com/astonzhangAZ/status/1841131443420008918" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
+<a href="https://github.com/facebookresearch/llm-cross-capabilities" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>
+<a href="https://www.llm-cross-capabilities.org" target="_blank">llm-cross-capabilities.org</a>
 

### 2024-10-05 quarto/index.qmd
update

--- 2024-09-30 quarto/index.qmd
@@
 
+Current research interests: pre-training architectures & scaling, long context (Llama 4).
+
 :::
@@
 
-* Join us for a 2025 research internship! I'm hiring early this year so just email me.
+* Join us for a 2025 research internship! Just email me if you are interested in improving Llama with our team.
 * <a href="https://ai.meta.com/blog/meta-llama-3-1/" target="_blank">Llama 3.1 405B</a> is now openly available.
@@
 ## Papers ([All](papers.qmd))
+
+* M.
+Zhong\*, **A.
+Zhang**\*, X.
+Wang, R.
+Hou, W.
+Xiong, C.
+Zhu, Z.
+Chen, L.
+Tan, C.
+Bi, M.
+Lewis, S.
+Popuri, S.
+Narang, M.
+Kambadur, D.
+Mahajan, S.
+Edunov, J.
+Han, and L.
+van der Maaten (\*equal contribution)<br>
+<a href="https://arxiv.org/abs/2409.19951" target="_blank">Law of the Weakest Link: Cross Capabilities of Large Language Models</a><br>
+*"Cross-capability performance is limited by the weakest underlying capability."*
+In *arXiv*, 2024<br>
+<a href="https://x.com/astonzhangAZ/status/1841131443420008918" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
+<a href="https://github.com/facebookresearch/llm-cross-capabilities" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>
+<a href="https://www.llm-cross-capabilities.org" target="_blank">llm-cross-capabilities.org</a>
 

### 2024-10-05 quarto/papers.qmd
update

--- 2024-07-27 quarto/papers.qmd
@@
 ---
+
+* M.
+Zhong\*, **A.
+Zhang**\*, X.
+Wang, R.
+Hou, W.
+Xiong, C.
+Zhu, Z.
+Chen, L.
+Tan, C.
+Bi, M.
+Lewis, S.
+Popuri, S.
+Narang, M.
+Kambadur, D.
+Mahajan, S.
+Edunov, J.
+Han, and L.
+van der Maaten (\*equal contribution)<br>
+<a href="https://arxiv.org/abs/2409.19951" target="_blank">Law of the Weakest Link: Cross Capabilities of Large Language Models</a><br>
+*"Cross-capability performance is limited by the weakest underlying capability."*
+In *arXiv*, 2024<br>
+<a href="https://x.com/astonzhangAZ/status/1841131443420008918" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
+<a href="https://github.com/facebookresearch/llm-cross-capabilities" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>
+<a href="https://www.llm-cross-capabilities.org" target="_blank">llm-cross-capabilities.org</a>
 

### 2024-10-07 quarto/index.qmd
update

@@
 
-Current research interests: pre-training architectures & scaling, long context (Llama 4).
+Current research: pre-training architectures & scaling, long context (Llama 4).
 
@@
 
-* Join us for a 2025 research internship! Just email me if you are interested in improving Llama with our team.
+* Join our Llama team for a 2025 research internship!
+Just email me if you are interested.
+<a href="https://x.com/astonzhangAZ/status/1843327816055795745" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
 * <a href="https://ai.meta.com/blog/meta-llama-3-1/" target="_blank">Llama 3.1 405B</a> is now openly available.

### 2024-10-16 quarto/index.qmd
update

@@
 <a href="https://github.com/meta-llama/llama-models" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>
+
+* J. Kim, A. Goyal, **A. Zhang**, B. Xiong, R. Hou, M. Kambadur, D. Mahajan, H. Hajishirzi, and L. Tan<br>
+<a href="#">A Systematic Examination of Preference Learning through the Lens of Instruction-Following</a><br>
+*"Understand preference learning with rejection sampling and Monte Carlo Tree Search."*
+In *arXiv*, 2024<br>
+
+* Y. Yu, Z. Chen, **A. Zhang**, L. Tan, C. Zhu, R. Y. Pang, Y. Qian, X. Wang, S. Gururangan, C. Zhang, M. Kambadur, D. Mahajan, and R. Hou<br>
+<a href="#">Self-critiquing Improves Reward Modeling for Large Language Models</a><br>
+*"Predicting both critiques and the scalar reward improves reward modeling."*
+In *arXiv*, 2024<br>
 

### 2024-10-16 quarto/papers.qmd
update

@@
 * H. Shao, Z. Xiao, S. Yao, D. Sun, **A. Zhang**, S. Liu, T. Wang, J. Li, and T. Abdelzaher<br>
-**ControlVAE: Tuning, Analytical Properties, and Performance Analysis**<br>
+<a href="#">ControlVAE: Tuning, Analytical Properties, and Performance Analysis</a><br>
 In *Transactions on Pattern Analysis and Machine Intelligence* (**TPAMI**), 2021
@@
 * **A. Zhang**, A. Chan, Y. Tay, J. Fu, S. Wang, S. Zhang, H. Shao, S. Yao, and R. Lee<br>
-**On Orthogonality Constraints for Transformers**<br>
+<a href="#">On Orthogonality Constraints for Transformers</a><br>
 In *Proceedings of the 59th Annual Meeting of the Association for Computational Linguistics* (**ACL, Oral**), 2021
@@
 * H. Shao, J. Wang, H. Lin, X. Zhang, **A. Zhang**, H. Ji, and T. Abdelzaher<br>
-**Controllable and Diverse Text Generation in E-commerce**<br>
+<a href="#">Controllable and Diverse Text Generation in E-commerce</a><br>
 In *Proceedings of the Web Conference* (**WWW**), 2021
@@
 * S. Zhang, H. Liu, **A. Zhang**, Y. Hu, C. Zhang, Y. Li, T. Zhu, S. He, and W. Ou<br>
-**Learning User Representations with Hypercuboids for Recommender Systems**<br>
+<a href="#">Learning User Representations with Hypercuboids for Recommender Systems</a><br>
 In *Proceedings of the 14th International Conference on Web Search and Data Mining* (**WSDM**), 2021
@@
 * H. Shao, S. Yao, D. Sun, **A. Zhang**, S. Liu, D. Liu, J. Wang, and T. Abdelzaher<br>
-**ControlVAE: Controllable Variational Autoencoder**<br>
+<a href="#">ControlVAE: Controllable Variational Autoencoder</a><br>
 In *Proceedings of International Conference on Machine Learning* (**ICML**), 2020
@@
 * J. Guo, H. He, T. He, L. Lausen, M. Li, H. Lin, X. Shi, C. Wang, J. Xie, S. Zha, **A. Zhang**, H. Zhang, Z. Zhang, Z. Zhang, S. Zheng, and Y. Zhu<br>
-**GluonCV and GluonNLP: Deep Learning in Computer Vision and Natural Language Processing**<br>
+<a href="#">GluonCV and GluonNLP: Deep Learning in Computer Vision and Natural Language Processing</a><br>
 In *Journal of Machine Learning Research* (**JMLR**), Vol. 21, No. 23, 2020
@@
 * A. Chan, Y. Tay, Y. S. Ong, and **A. Zhang**<br>
-**Poison Attacks against Text Datasets with Conditional Adversarially Regularized Autoencoder**<br>
+<a href="#">Poison Attacks against Text Datasets with Conditional Adversarially Regularized Autoencoder</a><br>
 In *Findings of Empirical Methods in Natural Language Processing* (**EMNLP**), 2020
@@
 * H. Shao, D. Sun, J. Wu, Z. Zhang, **A. Zhang**, S. Yao, S. Liu, T. Wang, C. Zhang, and T. Abdelzaher<br>
-**GitHub Repository Recommendation for Academic Papers**<br>
+<a href="#">GitHub Repository Recommendation for Academic Papers</a><br>
 In *Proceedings of the Web Conference* (**WWW**), 2020
@@
 * Y. Tay, A. T. Luu, **A. Zhang**, S. Wang, and S. C. Hui<br>
-**Compositional De-Attention Networks**<br>
+<a href="#">Compositional De-Attention Networks</a><br>
 In *Proceedings of the Conference on Neural Information Processing Systems* (**NeurIPS**), 2019
@@
 * S. Zhang, L. Yao, L. V. Tran, **A. Zhang**, and Y. Tay<br>
-**Quaternion Collaborative Filtering for Recommendation**<br>
+<a href="#">Quaternion Collaborative Filtering for Recommendation</a><br>
 In *Proceedings of the 28th International Joint Conference on Artificial Intelligence* (**IJCAI**), 2019
@@
 * Y. Tay, **A. Zhang**, A. T. Luu, J. Rao, S. Zhang, S. Wang, J. Fu, and S. C. Hui<br>
-**Lightweight and Efficient Neural Natural Language Processing with Quaternion Networks**<br>
+<a href="#">Lightweight and Efficient Neural Natural Language Processing with Quaternion Networks</a><br>
 In *Proceedings of the 57th Annual Meeting of the Association for Computational Linguistics* (**ACL**), 2019
@@
 * Y. Tay, S. Wang, A. T. Luu, J. Fu, M. C. Phan, X. Yuan, J. Rao, S. C. Hui, and **A. Zhang**<br>
-**Simple and Effective Curriculum Pointer-Generator Networks for Reading Comprehension over Long Narratives**<br>
+<a href="#">Simple and Effective Curriculum Pointer-Generator Networks for Reading Comprehension over Long Narratives</a><br>
 In *Proceedings of the 57th Annual Meeting of the Association for Computational Linguistics* (**ACL**), 2019
@@
 * A. El-Kishky, F. Xu, **A. Zhang**, and J. Han<br>
-**Parsimonious Morpheme Segmentation with an Application to Enriching Word Embeddings**<br>
+<a href="#">Parsimonious Morpheme Segmentation with an Application to Enriching Word Embeddings</a><br>
 In *Proceedings of the IEEE International Conference on Big Data* (**IEEE BigData**), 2019
@@
 * S. Yao, Y. Zhao, **A. Zhang**, S. Hu, H. Shao, C. Zhang, L. Su, and T. Abdelzaher<br>
-**Deep Learning for the Internet of Things**<br>
+<a href="#">Deep Learning for the Internet of Things</a><br>
 In *Computer*, 2018 (selected as May 2018 cover feature of the flagship magazine of the IEEE Computer Society)
@@
 * A. El-Kishky, F. Xu, **A. Zhang**, S. Macke, and J. Han<br>
-**Entropy-Based Subword with an Application to Word Embeddings**<br>
+<a href="#">Entropy-Based Subword with an Application to Word Embeddings</a><br>
 In *Proceedings of the 2nd Workshop on Subword and Character Level Models in NLP at the 16th Annual Conference of the North American Chapter of the Association for Computational Linguistics: Human Language Technologies* (**NAACL SCLeM**), 2018
@@
 * S. Yao, Y. Zhao, H. Shao, C. Zhang, **A. Zhang**, S. Hu, D. Liu, S. Liu, L. Su, and T. F. Abdelzaher<br>
-**SenseGAN: Enabling Deep Learning for Internet of Things with a Semi-Supervised Framework**<br>
+<a href="#">SenseGAN: Enabling Deep Learning for Internet of Things with a Semi-Supervised Framework</a><br>
 In *Proceedings of the ACM on Interactive, Mobile, Wearable and Ubiquitous Technologies* (**ACM Ubicomp, <font color="red">Distinguished Paper Award</font>**), 2018
@@
 * **A. Zhang**, X. Lu, C. A. Gunter, S. Yao, F. Tao, R. Zhu, H. Gui, D. Fabbri, D. Liebovitz, and B. Malin<br>
-**De Facto Diagnosis Specialties: Recognition and Discovery**<br>
+<a href="#">De Facto Diagnosis Specialties: Recognition and Discovery</a><br>
 In *Learning Health Systems* (**LHS**), 2018
@@
 * S. Yao, Y. Zhao, H. Shao, C. Zhang, **A. Zhang**, D. Liu, S. Liu, L. Su, and T. Abdelzaher<br>
-**ApDeepSense: Deep Learning Uncertainty Estimation Without the Pain for IoT**<br>
+<a href="#">ApDeepSense: Deep Learning Uncertainty Estimation Without the Pain for IoT</a><br>
 In *Proceedings of the 38th IEEE International Conference on Distributed Computing Systems* (**ICDCS**), 2018
@@
 * **A. Zhang**, L. Garcia-Pueyo, J. B. Wendt, M. Najork, and A. Broder<br>
-**Email Category Prediction**<br>
+<a href="#">Email Category Prediction</a><br>
 In *Proceedings of the 26th International World Wide Web Conference * (**WWW**), 2017
@@
 * S. Yao, S. Hu, Y. Zhao, **A. Zhang**, and T. Abdelzaher<br>
-**DeepSense: A Unified Deep Learning Framework for Time-Series Mobile Sensing Data Processing**<br>
+<a href="#">DeepSense: A Unified Deep Learning Framework for Time-Series Mobile Sensing Data Processing</a><br>
 In *Proceedings of the 26th International World Wide Web Conference* (**WWW**), 2017
@@
 * S. Yao, Y. Zhao, **A. Zhang**, S. Lu, and T. Abdelzaher<br>
-**DeepIoT: Compressing Deep Neural Network Structures for Sensing Systems without Loss of Performance**<br>
+<a href="#">DeepIoT: Compressing Deep Neural Network Structures for Sensing Systems without Loss of Performance</a><br>
 In *Proceedings of the 15th ACM Conference on Embedded Networked Sensor Systems* (**ACM Sensys, <font color="red">Best Paper Award Nomination</font>**), 2017
@@
 * S. Yao, Y. Zhao, H. Shao, **A. Zhang**, C. Zhang, S. Li, and T. Abdelzaher<br>
-**RDeepSense: Reliable Deep Mobile Computing Models with Uncertainty Estimations**<br>
+<a href="#">RDeepSense: Reliable Deep Mobile Computing Models with Uncertainty Estimations</a><br>
 In *Proceedings of the ACM on Interactive, Mobile, Wearable and Ubiquitous Technologies* (**ACM Ubicomp**), 2017
@@
 * **A. Zhang**, A. Goyal, R. Baeza-Yates, Y. Chang, J. Han, C. A. Gunter, and H. Deng<br>
-**Towards Mobile Query Auto-Completion: An Efficient Mobile Application-Aware Approach**<br>
+<a href="#">Towards Mobile Query Auto-Completion: An Efficient Mobile Application-Aware Approach</a><br>
 In *Proceedings of the 25th International World Wide Web Conference* (**WWW**), 2016
@@
 * **A. Zhang** and Q. Gu<br>
-**Accelerated Stochastic Block Coordinate Descent with Optimal Sampling** [<a href="papers/supp_asbcd.pdf" target="_blank">Proof of Lemmas</a>]<br>
+<a href="#">Accelerated Stochastic Block Coordinate Descent with Optimal Sampling</a> [<a href="papers/supp_asbcd.pdf" target="_blank">Proof of Lemmas</a>]<br>
 In *Proceedings of the 22nd ACM SIGKDD Conference on Knowledge Discovery and Data Mining* (**KDD**), 2016
@@
 * S. Demetriou, W. Merrill, W. Yang, **A. Zhang**, and C. A. Gunter<br>
-**Free for All! Assessing User Data Exposure to Advertising Libraries on Android**<br>
+<a href="#">Free for All! Assessing User Data Exposure to Advertising Libraries on Android</a><br>
 In *Proceedings of the Network and Distributed System Security Symposium* (**NDSS**), 2016
@@
 * R. Zhu, **A. Zhang**, J. Peng, and C. Zhai<br>
-**Exploiting Temporal Divergence of Topic Distributions for Event Detection**<br>
+<a href="#">Exploiting Temporal Divergence of Topic Distributions for Event Detection</a><br>
 In *Proceedings of the IEEE International Conference on Big Data* (**IEEE BigData**), 2016
@@
 * **A. Zhang**, A. Goyal, W. Kong, H. Deng, A. Dong, Y. Chang, C. A. Gunter, and J. Han<br>
-**adaQAC: Adaptive Query Auto-Completion via Implicit Negative Feedback**<br>
+<a href="#">adaQAC: Adaptive Query Auto-Completion via Implicit Negative Feedback</a><br>
 In *Proceedings of the 38th International ACM SIGIR Conference on Research and Development in Information Retrieval* (**SIGIR**), 2015
@@
 * W. Kong, R. Li, J. Luo, **A. Zhang**, Y. Chang, and J. Allan<br>
-**Predicting Search Intent Based on Pre-Search Context**<br>
+<a href="#">Predicting Search Intent Based on Pre-Search Context</a><br>
 In *Proceedings of the 38th International ACM SIGIR Conference on Research and Development in Information Retrieval* (**SIGIR**), 2015
@@
 * H. Fu, **A. Zhang**, and X. Xie<br>
-**Effective Social Graph De-anonymization based on Graph Structure and Descriptive Information**<br>
+<a href="#">Effective Social Graph De-anonymization based on Graph Structure and Descriptive Information</a><br>
 In *ACM Transactions on Intelligent Systems and Technology* (**ACM TIST**), Vol. 6, No. 4, 2015
@@
 * X. Lu, **A. Zhang**, C. A. Gunter, D. Fabbri, D. Liebovitz, and B. Malin<br>
-**Discovering De Facto Diagnosis Specialties**<br>
+<a href="#">Discovering De Facto Diagnosis Specialties</a><br>
 In *Proceedings of the 6th ACM Conference on Bioinformatics, Computational Biology, and Health Informatics* (**ACM BCB**), 2015
@@
 * **A. Zhang**, X. Xie, K. C.-C. Chang, C. A. Gunter, J. Han, and X. Wang<br>
-**Privacy Risk in Anonymized Heterogeneous Information Networks**<br>
+<a href="#">Privacy Risk in Anonymized Heterogeneous Information Networks</a><br>
 In *Proceedings of the 17th International Conference on Extending Database Technology* (**EDBT**), 2014
@@
 * H. Fu, **A. Zhang**, and X. Xie<br>
-**De-anonymizing Social Graphs via Node Similarity**<br>
+<a href="#">De-anonymizing Social Graphs via Node Similarity</a><br>
 In *Proceedings of the 23rd International World Wide Web Conference* (**WWW**), 2014

### 2024-11-15 quarto/index.qmd
update

@@
 
-* Join our Llama team for a 2025 research internship!
+* [<span style="color:red;">Hiring</span>] Join our Llama team for a 2025 research internship!
 Just email me if you are interested.
@@
 <a href="https://github.com/meta-llama/llama-models" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>
+
+* J. Ji, **A. Zhang**, C. Zhu, S. Wang, M. Kambadur, S. Chang, and W. Xiong<br>
+<a href="#">Pruning Computations in Transformer Prefilling for Large Language Models</a><br>
+*"Speed up Transfomer prefilling for generation via a learnable router."*
+In *arXiv*, 2024<br>
 

### 2024-12-07 quarto/index.qmd
update

@@
 
-* [<span style="color:red;">Hiring</span>] Join our Llama team for a 2025 research internship!
-Just email me if you are interested.
+* Join our Llama team for a 2025 research internship!
+Just email me (position filled, see you next year).
 <a href="https://x.com/astonzhangAZ/status/1843327816055795745" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
@@
 * Y. Yu, Z. Chen, **A. Zhang**, L. Tan, C. Zhu, R. Y. Pang, Y. Qian, X. Wang, S. Gururangan, C. Zhang, M. Kambadur, D. Mahajan, and R. Hou<br>
-<a href="#">Self-critiquing Improves Reward Modeling for Large Language Models</a><br>
+<a href="https://arxiv.org/abs/2411.16646">Self-Generated Critiques Boost Reward Modeling for Language Models</a><br>
 *"Predicting both critiques and the scalar reward improves reward modeling."*

### 2024-12-07 quarto/papers.qmd
update

@@
 
+* J. Ji, **A. Zhang**, C. Zhu, S. Wang, M. Kambadur, S. Chang, and W. Xiong<br>
+<a href="#">Pruning Computations in Transformer Prefilling for Large Language Models</a><br>
+*"Speed up Transfomer prefilling for generation via a learnable router."*
+In *arXiv*, 2024<br>
+
 * J. Kim, A. Goyal, **A. Zhang**, B. Xiong, R. Hou, M. Kambadur, D. Mahajan, H. Hajishirzi, and L. Tan<br>

### 2025-01-22 quarto/index.qmd
update

@@
 <a href="https://arxiv.org/abs/2409.19951" target="_blank">Law of the Weakest Link: Cross Capabilities of Large Language Models</a><br>
-*"Cross-capability performance is limited by the weakest underlying capability."*
-In *arXiv*, 2024<br>
+*"Cross-capability performance is limited by the weakest underlying capability."*<br>
+In *Proceedings of the International Conference on Learning Representations* (**ICLR**), 2025<br>
 <a href="https://x.com/astonzhangAZ/status/1841131443420008918" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>

### 2025-01-25 quarto/index.qmd
update

--- 2024-12-07 quarto/index.qmd
@@
 <a href="https://arxiv.org/abs/2409.19951" target="_blank">Law of the Weakest Link: Cross Capabilities of Large Language Models</a><br>
-*"Cross-capability performance is limited by the weakest underlying capability."*
-In *arXiv*, 2024<br>
+In *Proceedings of the International Conference on Learning Representations* (**ICLR**), 2025<br>
 <a href="https://x.com/astonzhangAZ/status/1841131443420008918" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
@@
 <a href="https://www.llm-cross-capabilities.org" target="_blank">llm-cross-capabilities.org</a>
+
+* J. Ji, **A. Zhang**, C. Zhu, S. Wang, M. Kambadur, S. Chang, and W. Xiong<br>
+<a href="#">Pruning Computations in Transformer Prefilling for Large Language Models</a><br>
+*"Speed up Transfomer prefilling for generation via a learnable router."*
+In *arXiv*, 2025<br>
+
+* J. Kim, A. Goyal, **A. Zhang**, B. Xiong, R. Hou, M. Kambadur, D. Mahajan, H. Hajishirzi, and L. Tan<br>
+<a href="https://arxiv.org/abs/2412.15282">A Systematic Examination of Preference Learning through the Lens of Instruction-Following</a><br>
+In *Annual Conference of the Nations of the Americas Chapter of the Association for Computational Linguistics* (**NAACL**), 2025<br>
+
+* Y. Yu, Z. Chen, **A. Zhang**, L. Tan, C. Zhu, R. Y. Pang, Y. Qian, X. Wang, S. Gururangan, C. Zhang, M. Kambadur, D. Mahajan, and R. Hou<br>
+<a href="https://arxiv.org/abs/2411.16646">Self-Generated Critiques Boost Reward Modeling for Language Models</a><br>
+In *Annual Conference of the Nations of the Americas Chapter of the Association for Computational Linguistics* (**NAACL**), 2025<br>
 
@@
 <a href="https://github.com/meta-llama/llama-models" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>
-
-* J. Ji, **A. Zhang**, C. Zhu, S. Wang, M. Kambadur, S. Chang, and W. Xiong<br>
-<a href="#">Pruning Computations in Transformer Prefilling for Large Language Models</a><br>
-*"Speed up Transfomer prefilling for generation via a learnable router."*
-In *arXiv*, 2024<br>
-
-* J. Kim, A. Goyal, **A. Zhang**, B. Xiong, R. Hou, M. Kambadur, D. Mahajan, H. Hajishirzi, and L. Tan<br>
-<a href="#">A Systematic Examination of Preference Learning through the Lens of Instruction-Following</a><br>
-*"Understand preference learning with rejection sampling and Monte Carlo Tree Search."*
-In *arXiv*, 2024<br>
-
-* Y. Yu, Z. Chen, **A. Zhang**, L. Tan, C. Zhu, R. Y. Pang, Y. Qian, X. Wang, S. Gururangan, C. Zhang, M. Kambadur, D. Mahajan, and R. Hou<br>
-<a href="https://arxiv.org/abs/2411.16646">Self-Generated Critiques Boost Reward Modeling for Language Models</a><br>
-*"Predicting both critiques and the scalar reward improves reward modeling."*
-In *arXiv*, 2024<br>
 

### 2025-01-25 quarto/papers.qmd
update

--- 2024-10-16 quarto/papers.qmd
@@
 <a href="https://github.com/meta-llama/llama-models" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>
-
-* J. Kim, A. Goyal, **A. Zhang**, B. Xiong, R. Hou, M. Kambadur, D. Mahajan, H. Hajishirzi, and L. Tan<br>
-<a href="#">A Systematic Examination of Preference Learning through the Lens of Instruction-Following</a><br>
-*"Understand preference learning with rejection sampling and Monte Carlo Tree Search."*
-In *arXiv*, 2024<br>
-
-* Y. Yu, Z. Chen, **A. Zhang**, L. Tan, C. Zhu, R. Y. Pang, Y. Qian, X. Wang, S. Gururangan, C. Zhang, M. Kambadur, D. Mahajan, and R. Hou<br>
-<a href="#">Self-critiquing Improves Reward Modeling for Large Language Models</a><br>
-*"Predicting both critiques and the scalar reward improves reward modeling."*
-In *arXiv*, 2024<br>
 

### 2025-02-11 quarto/index.qmd
update

@@
 
-**Aston Zhang** is a research scientist on the <a href="https://llama.meta.com/" target="_blank">Llama</a> team at Meta Generative AI and a core contributor to <a href="https://ai.meta.com/blog/meta-llama-3/" target="_blank">Llama 3</a>.
+**Aston Zhang** is a research scientist on the <a href="https://llama.meta.com/" target="_blank">Llama</a> team at Meta Generative AI, where he leads long context of Llama 4 and is a core contributor to <a href="https://ai.meta.com/blog/meta-llama-3/" target="_blank">Llama 3</a>.
 Previously, he served as a scientist and manager at AWS AI Research.

### 2025-02-16 quarto/index.qmd
update

--- 2025-01-25 quarto/index.qmd
@@
 
-**Aston Zhang** is a research scientist on the <a href="https://llama.meta.com/" target="_blank">Llama</a> team at Meta Generative AI and a core contributor to <a href="https://ai.meta.com/blog/meta-llama-3/" target="_blank">Llama 3</a>.
+**Aston Zhang** is a research scientist at Meta, where he leads long context of Llama 4 and is a core contributor to <a href="https://ai.meta.com/blog/meta-llama-3/" target="_blank">Llama 3</a>.
 Previously, he served as a scientist and manager at AWS AI Research.
@@
 is <a href="https://d2l.ai/_images/map.png" target="_blank">adopted worldwide</a>.
-He holds a Ph.D. in Computer Science from the University of Illinois Urbana-Champaign.
+He holds a Ph.D. in Computer Science from UIUC.
 
-Current research: pre-training architectures & scaling, long context (Llama 4).
+Research: long context, pre-training architectures & scaling
 

### 2025-02-16 quarto/index.qmd
update

@@
 
-**Aston Zhang** is a research scientist at Meta, where he leads long context of Llama 4 and is a core contributor to <a href="https://ai.meta.com/blog/meta-llama-3/" target="_blank">Llama 3</a>.
+**Aston Zhang** is a research scientist at Meta, where he leads long context of <a href="https://www.llama.com/" target="_blank">Llama</a> and is a core contributor to <a href="https://ai.meta.com/blog/meta-llama-3/" target="_blank">Llama 3</a>.
 Previously, he served as a scientist and manager at AWS AI Research.

### 2025-04-05 quarto/index.qmd
update

--- 2025-02-16 quarto/index.qmd
@@
   image: img/aston.jpg
-  image-width: 200px
+  image-width: 160px
   image-shape: rounded
   links:
-    - icon: twitter
-      href: https://twitter.com/astonzhangAZ
     - icon: bi-envelope
       href: img/email.png
-    - icon: github
-      href: https://github.com/astonzhang
-    - icon: google
-      href: https://scholar.google.com/citations?user=WXOaxKMAAAAJ
-    - icon: linkedin
-      href: https://www.linkedin.com/in/astonzhang/
+
 ---
@@
 
-**Aston Zhang** is a research scientist at Meta, where he leads long context of Llama 4 and is a core contributor to <a href="https://ai.meta.com/blog/meta-llama-3/" target="_blank">Llama 3</a>.
-Previously, he served as a scientist and manager at AWS AI Research.
-His accolades include the <a href="https://iclr-conf.medium.com/announcing-iclr-2021-outstanding-paper-awards-9ae0514734ab" target="_blank">ICLR Outstanding Paper Award</a>,
+**Aston Zhang** is a member of technical staff at <a href="https://openai.com" target="_blank">OpenAI</a>. 
+His work has been recognized with the <a href="https://iclr-conf.medium.com/announcing-iclr-2021-outstanding-paper-awards-9ae0514734ab" target="_blank">ICLR Outstanding Paper Award</a>,
 the ACM Ubicomp Distinguished Paper Award,
@@
 is <a href="https://d2l.ai/_images/map.png" target="_blank">adopted worldwide</a>.
-He holds a Ph.D. in Computer Science from UIUC.
-
-Research: long context, pre-training architectures & scaling
+He earned his Ph.D. from UIUC.
 
 :::
-
-## News
-
-* Join our Llama team for a 2025 research internship!
-Just email me (position filled, see you next year).
-<a href="https://x.com/astonzhangAZ/status/1843327816055795745" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
-* <a href="https://ai.meta.com/blog/meta-llama-3-1/" target="_blank">Llama 3.1 405B</a> is now openly available.
-<a href="https://x.com/astonzhangAZ/status/1815763885380747422" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
-* Meet <a href="https://ai.meta.com/blog/meta-llama-3/" target="_blank">Llama 3</a>, our state-of-the-art open source large language model.
-Check out <a href="https://x.com/AIatMeta/status/1806757387677897206" target="_blank">my developer podcast</a>.
-<a href="https://x.com/astonzhangAZ/status/1780990210576441844" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
 
@@
 	* Adopted at 500 universities from 70 countries
-	* Featured in the <a href="https://youtu.be/ue9aumC7AAk?t=6856" target="_blank">AWS re:Invent keynote</a> by Swami, Head of AWS AI, Database, and Analytics<br>
-	<iframe src="https://ghbtns.com/github-btn.html?user=d2l-ai&repo=d2l-en&type=star&count=true" frameborder="0" scrolling="0" width="150" height="30" title="GitHub"></iframe>
-
-* **A. Zhang**, M. Li, Z. C. Lipton, and A. J. Smola<br>
-	<a href="https://zh.d2l.ai" target="_blank">动手学深度学习</a><br>
-	*人民邮电出版社*, 2nd ed., 2023, 1st ed., 2019<br>
 	* <a href="https://raw.githubusercontent.com/d2l-ai/d2l-zh/master/static/frontpage/_images/sales/jd-2023020304-all-ai-zh-4.png" target="_blank">Best seller</a> in China 
 	<br>
-	<iframe src="https://ghbtns.com/github-btn.html?user=d2l-ai&repo=d2l-zh&type=star&count=true" frameborder="0" scrolling="0" width="150" height="30" title="GitHub"></iframe>
+	<iframe src="https://ghbtns.com/github-btn.html?user=d2l-ai&repo=d2l-en&type=star&count=true" frameborder="0" scrolling="0" width="120" height="30" title="GitHub"></iframe> <iframe src="https://ghbtns.com/github-btn.html?user=d2l-ai&repo=d2l-zh&type=star&count=true" frameborder="0" scrolling="0" width="120" height="30" title="GitHub"></iframe>
 
@@
 
-* M.
-Zhong\*, **A.
-Zhang**\*, X.
-Wang, R.
-Hou, W.
-Xiong, C.
-Zhu, Z.
-Chen, L.
-Tan, C.
-Bi, M.
-Lewis, S.
-Popuri, S.
-Narang, M.
-Kambadur, D.
-Mahajan, S.
-Edunov, J.
-Han, and L.
-van der Maaten (\*equal contribution)<br>
+* M. Zhong\*, **A. Zhang**\*, X. Wang, R. Hou, W. Xiong, C. Zhu, Z. Chen, L. Tan, C. Bi, M. Lewis, S. Popuri, S. Narang, M. Kambadur, D. Mahajan, S. Edunov, J. Han, and L. van der Maaten<br>
 <a href="https://arxiv.org/abs/2409.19951" target="_blank">Law of the Weakest Link: Cross Capabilities of Large Language Models</a><br>
@@
 <a href="https://www.llm-cross-capabilities.org" target="_blank">llm-cross-capabilities.org</a>
-
-* J. Ji, **A. Zhang**, C. Zhu, S. Wang, M. Kambadur, S. Chang, and W. Xiong<br>
-<a href="#">Pruning Computations in Transformer Prefilling for Large Language Models</a><br>
-*"Speed up Transfomer prefilling for generation via a learnable router."*
-In *arXiv*, 2025<br>
-
-* J. Kim, A. Goyal, **A. Zhang**, B. Xiong, R. Hou, M. Kambadur, D. Mahajan, H. Hajishirzi, and L. Tan<br>
-<a href="https://arxiv.org/abs/2412.15282">A Systematic Examination of Preference Learning through the Lens of Instruction-Following</a><br>
-In *Annual Conference of the Nations of the Americas Chapter of the Association for Computational Linguistics* (**NAACL**), 2025<br>
-
-* Y. Yu, Z. Chen, **A. Zhang**, L. Tan, C. Zhu, R. Y. Pang, Y. Qian, X. Wang, S. Gururangan, C. Zhang, M. Kambadur, D. Mahajan, and R. Hou<br>
-<a href="https://arxiv.org/abs/2411.16646">Self-Generated Critiques Boost Reward Modeling for Language Models</a><br>
-In *Annual Conference of the Nations of the Americas Chapter of the Association for Computational Linguistics* (**NAACL**), 2025<br>
 
@@
 <a href="https://arxiv.org/abs/2309.11436" target="_blank">You Only Look at Screens: Multimodal Chain-of-Action Agents</a><br>
-*"Perform a task on smart phones? Train an agent using screenshots."*
-In *arXiv*, 2023<br>
+In *Findings of the Association for Computational Linguistics* (**ACL**), 2024<br>
 <a href="https://twitter.com/astonzhangAZ/status/1705235421280797111" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
@@
 	<a href="https://arxiv.org/abs/2302.00923" target="_blank">Multimodal Chain-of-Thought Reasoning in Language Models</a><br>
-	In *Transactions on Machine Learning Research*, 2023<br>
+	In *Transactions on Machine Learning Research*  (**TMLR**), 2024<br>
 	<a href="https://twitter.com/astonzhangAZ/status/1621545166049005568" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
@@
 	<a href="img/mm-cot-idea.png" target="_blank">[Idea Inspiration by Homeschooling]</a>
-
-* S. Ren, **A. Zhang**, Y. Zhu, S. Zhang, S. Zheng, M. Li, A. J. Smola, X. Sun
-<br>
-<a href="https://arxiv.org/abs/2304.04704" target="_blank">Prompt Pre-Training with Twenty-Thousand Classes for Open-Vocabulary Visual Recognition</a><br>
-In *Proceedings of the Conference on Neural Information Processing Systems* (**NeurIPS**), 2023<br>
-<a href="https://github.com/amazon-science/prompt-pretraining" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>
-
-* Z. Zeng, C. Hawkins, M. Hong, **A. Zhang**, N. Pappas, V. Singh, and S. Zheng<br>
-<a href="https://arxiv.org/abs/2305.04241" target="_blank">Scaling Transformers to 128K Tokens or More by Prioritizing Important Tokens</a><br>
-In *Proceedings of the Conference on Neural Information Processing Systems* (**NeurIPS**), 2023<br>
 
@@
 
-* Z. Liu, Z. Tang, X. Shi, **A. Zhang**, M. Li, A. Shrivastava, and A. Wilson<br>
-	<a href="https://arxiv.org/abs/2212.14453" target="_blank">Learning Multimodal Data Augmentation in Feature Space</a><br>
-	In *Proceedings of the International Conference on Learning Representations* (**ICLR**), 2023<br>
-
 * T. Yang, Y. Zhu, Y. Xie, **A. Zhang**, C. Chen, and M. Li<br>
@@
 	In *Proceedings of the International Conference on Learning Representations* (**ICLR**), 2023<br>
-
-* C. Qin, **A. Zhang**, Z. Zhang, J. Chen, M. Yasunaga, and D. Yang<br>
-<a href="https://arxiv.org/abs/2302.06476" target="_blank">Is ChatGPT a General-Purpose Natural Language Processing Task Solver?</a><br>
-In *Empirical Methods in Natural Language Processing* (**EMNLP**), 2023<br>
-
-* J. Chen, **A. Zhang**, D. Yang, M. Li, and A. J. Smola<br>
-<a href="https://arxiv.org/abs/2304.04746" target="_blank">A Cheaper and Better Diffusion Language Model with Soft-Masked Noise</a><br>
-In *Empirical Methods in Natural Language Processing* (**EMNLP**), 2023<br>
-<a href="https://github.com/amazon-science/masked-diffusion-lm" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>
-
-* H. Wang, **A. Zhang**, Y. Zhu, S. Zheng, M. Li, A. J. Smola, and Z. Wang<br>
-	<a href="https://arxiv.org/pdf/2207.01160.pdf" target="_blank">Partial and Asymmetric Contrastive Learning for Out-of-Distribution Detection in Long-Tailed Recognition</a><br>
-	In *Proceedings of International Conference on Machine Learning* (**ICML, Long Presentation**), 2022<br>
-	<a href="https://twitter.com/astonzhangAZ/status/1549800894840971265" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
-	<a href="https://github.com/amazon-research/long-tailed-ood-detection" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>
-
-* H. Wang, **A. Zhang**, S. Zheng, X. Shi, M. Li, and Z. Wang<br>
-	<a href="https://arxiv.org/pdf/2207.01156.pdf" target="_blank">Removing Batch Normalization Boosts Adversarial Training</a><br>
-	In *Proceedings of International Conference on Machine Learning* (**ICML**), 2022<br>
-	<a href="https://twitter.com/astonzhangAZ/status/1549069378250874880" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
-	<a href="https://github.com/amazon-research/normalizer-free-robust-training" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>
 
@@
 
-* with H. Lin, X. Shi, L. Lausen, H. He, S. Zha, and A. J. Smola<br>
-	**Dive into Deep Learning for Natural Language Processing** <br>
-	In *Conference on Empirical Methods in Natural Language Processing* (**EMNLP**), 2019
-
-* with H. Lin, L. Lausen, S. Zha, A. J. Smola, C. Wang, and M. Li<br>
-	**From Shallow to Deep Language Representations: Pre-training, Fine-tuning, and Beyond** [<a href="https://github.com/astonzhang/KDD19-tutorial" target="_blank">Website</a>]<br>
-	In *The 25th ACM SIGKDD Conference on Knowledge Discovery and Data Mining* (**KDD**), 2019
-
-* with H. Zhang, T. He, Z. Zhang, Z. Zhang, H. Lin, and M. Li<br>
-	**Everything You Need to Know to Reproduce SOTA Deep Learning Models from Hands-on Tutorial**<br>
-	In *International Conference on Computer Vision* (**ICCV**), 2019
-
 ## Services
@@
 	* *International Conference on Computational Linguistics* (**COLING**)
-
-<br>
-<a href="https://twitter.com/astonzhangAZ?ref_src=twsrc%5Etfw" class="twitter-follow-button" data-size="large" data-show-count="false">Follow @astonzhangAZ</a><script async src="https://platform.twitter.com/widgets.js" charset="utf-8"></script>
-<br>
-<a class="twitter-timeline" data-width="350" data-height="200" href="https://twitter.com/astonzhangAZ?ref_src=twsrc%5Etfw">Tweets by astonzhangAZ</a> <script async src="https://platform.twitter.com/widgets.js" charset="utf-8"></script>

### 2025-04-05 quarto/papers.qmd
update

@@
 
+* X. Ma, Y. Wang, Y. Yao, T. Yuan, **A. Zhang**, Z. Zhang, and H. Zhao<br>
+<a href="https://arxiv.org/abs/2408.02544">Caution for the Environment: LLM Agents Are Susceptible to Environmental Distractions</a><br>
+In *Association for Computational Linguisticss* (**ACL**), 2025<br>
+
+* P. Cheng, Z. Wu, Z. Wu, T. Ju, **A. Zhang**, Z. Zhang, and G. Liu<br>
+<a href="https://arxiv.org/abs/2503.16465">OS-Kairos: Adaptive Interaction for MLLM-Powered GUI Agents</a><br>
+In *Findings of the Association for Computational Linguisticss* (**ACL**), 2025<br>
+
+* Z. Zhang, Y. Yao, **A. Zhang**, X. Tang, X. Ma, Z. He, Y. Wang, M. Gerstein, R. Wang, G. Liu, and H. Zhao<br>
+<a href="https://arxiv.org/abs/2311.11797">Igniting Language Intelligence: The Hitchhiker's Guide From Chain-of-Thought Reasoning to Language Agents</a><br>
+In *ACM Computing Surveys* (**CSUR**), 2024<br>
+
 * Llama Team, AI@Meta (**Core Contributor**)<br>

### 2025-12-23 quarto/index.qmd
update

@@
 is <a href="https://d2l.ai/_images/map.png" target="_blank">adopted worldwide</a>.
-He earned his Ph.D. from UIUC.
+He earned his Ph.D. from the University of Illinois Urbana-Champaign.
 
@@
 ## Papers ([All](papers.qmd))
+
+* R. Bansal, **A. Zhang**, R. Tiwari, L. Madaan, S. Duvvuri, D. Khatri, D. Brandfonbrener, D. Alvarez-Melis, P. Bhargava, M. Kale, and S. Jelassi<br>
+<a href="https://arxiv.org/abs/2512.13898" target="_blank">Let's (NoT) Just Put Things in Context: Test-Time Training for Long-Context LLMs</a><br>
+*Lightweight context-specific training is a better use of inference compute for long context.* In *arXiv*, 2026<br>
 
@@
 
+* T. Yang, Y. Zhu, Y. Xie, **A. Zhang**, C. Chen, and M. Li<br>
+	<a href="https://openreview.net/forum?id=CIoSZ_HKHS7" target="_blank">AIM: Adapting Image Models for Efficient Video Understanding</a><br>
+	In *Proceedings of the International Conference on Learning Representations* (**ICLR**), 2023<br>
+
 * Z. Zhang, **A. Zhang**, M. Li, and A. J. Smola<br>
@@
 
-* T. Yang, Y. Zhu, Y. Xie, **A. Zhang**, C. Chen, and M. Li<br>
-	<a href="https://openreview.net/forum?id=CIoSZ_HKHS7" target="_blank">AIM: Adapting Image Models for Efficient Video Understanding</a><br>
-	In *Proceedings of the International Conference on Learning Representations* (**ICLR**), 2023<br>
+* C. Qin, **A. Zhang**, Z. Zhang, J. Chen, M. Yasunaga, and D. Yang<br>
+	<a href="https://arxiv.org/abs/2302.06476" target="_blank">Is ChatGPT a General-Purpose Natural Language Processing Task Solver?</a><br>
+	In *Empirical Methods in Natural Language Processing* (**EMNLP**), 2023<br>
 

### 2025-12-23 quarto/index.qmd
update

@@
       href: img/email.png
+    - icon: twitter
+      href: https://twitter.com/astonzhangAZ
+    - icon: google
+      href: https://scholar.google.com/citations?user=WXOaxKMAAAAJ
+    - icon: linkedin
+      href: https://www.linkedin.com/in/astonzhang/
 

### 2025-12-23 quarto/index.qmd
update

--- 2025-12-23 quarto/index.qmd
@@
       href: img/email.png
+    - icon: twitter-x
+      href: https://twitter.com/astonzhangAZ
+    - icon: google
+      href: https://scholar.google.com/citations?user=WXOaxKMAAAAJ
+    - icon: linkedin
+      href: https://www.linkedin.com/in/astonzhang/
 
@@
 	<br>
-	<iframe src="https://ghbtns.com/github-btn.html?user=d2l-ai&repo=d2l-en&type=star&count=true" frameborder="0" scrolling="0" width="120" height="30" title="GitHub"></iframe> <iframe src="https://ghbtns.com/github-btn.html?user=d2l-ai&repo=d2l-zh&type=star&count=true" frameborder="0" scrolling="0" width="120" height="30" title="GitHub"></iframe>
+	<iframe src="https://ghbtns.com/github-btn.html?user=d2l-ai&repo=d2l-en&type=star&count=true" frameborder="0" scrolling="0" width="120" height="25" title="GitHub"></iframe>
+	<iframe src="https://ghbtns.com/github-btn.html?user=d2l-ai&repo=d2l-zh&type=star&count=true" frameborder="0" scrolling="0" width="120" height="25" title="GitHub"></iframe>
 

### 2025-12-23 quarto/index.qmd
update

@@
 	<br>
-	<iframe src="https://ghbtns.com/github-btn.html?user=d2l-ai&repo=d2l-en&type=star&count=true" frameborder="0" scrolling="0" width="120" height="25" title="GitHub"></iframe>
-	<iframe src="https://ghbtns.com/github-btn.html?user=d2l-ai&repo=d2l-zh&type=star&count=true" frameborder="0" scrolling="0" width="120" height="25" title="GitHub"></iframe>
+	<iframe src="https://ghbtns.com/github-btn.html?user=d2l-ai&repo=d2l-en&type=star&count=true" frameborder="0" scrolling="0" width="120" height="20" title="GitHub"></iframe>
+	<iframe src="https://ghbtns.com/github-btn.html?user=d2l-ai&repo=d2l-zh&type=star&count=true" frameborder="0" scrolling="0" width="120" height="20" title="GitHub"></iframe>
 

### 2025-12-23 quarto/index.qmd
update

@@
       href: https://twitter.com/astonzhangAZ
-    - icon: google
-      href: https://scholar.google.com/citations?user=WXOaxKMAAAAJ
-    - icon: linkedin
-      href: https://www.linkedin.com/in/astonzhang/
 
